### 2020-10-21 proposal/proposal.tex
initial commit

\documentclass[11pt]{article}
\title{Refining the Millisecond Pulsar Model for the Galactic Center Excess}
\author{\Large{UROP Proposal with Tracy Slatyer}\vspace{12pt}\\Jack Dinsmore}

\usepackage{csquotes}
\usepackage[english]{babel}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

\begin{document}
\maketitle

\begin{displayquote}
    I am a Junior in the MIT Physics department, applying for a direct-funding astrophysics UROP with Professor Tracy Slatyer of MIT in the fall of 2020. I will be working remotely from Leverett, MA.
\end{displayquote}

\section{Project Description}
The Galactic Center GeV Excess (GCE) is an unexpected source of gamma radiation originating from the center of the Milky Way, detected  recently by the \textit{Fermi} Gamma-ray Space Telescope \cite{fermilab, tracy3}. Its origin is debated; the GCE holds potential to be the first evidence observed for dark matter annihilation, yet several studies have also shown that point sources such as millisecond pulsars may be responsible for the excess \cite{bartels, tracy1}.

The recently collected 4FGL point source catalog promises to shed light on this conflict. By it, Ref. \cite{fermilab} argues that the millisecond pulsar model outlined in Ref. \cite{bartels} may not contribute to the GCE, and that if the GCE were entirely explained by pulsars, a large number of faint pulsars would be required. However, Ref. \cite{fermilab} uses an approximate luminosity function to describe pulsar brightness, and it is not known to what degree this approximation influences the results.

We intend to expand on Refs. \cite{bartels} and \cite{fermilab} in their investigations into a pulsar-based explanation for the GCE. In particular, we will test luminosity functions  more complicated than those used in \cite{fermilab}, taken from observed pulsars in other contexts, and measure how the number of pulsars required to recreate the GCE changes based on the luminosity functions used. We can then predict how many pulsars should have already been observed by other means for each luminosity function.

\section{Personal Role}
As the only student working on this project currently, I will be involved in all of the steps listed above. I will start by continuing to read literature on the GCE and on millisecond pulsars, identifying luminosity functions that have been observed for non-GCE scenarios. Then I will calculate the number of pulsars required to reproduce the GCE for each luminosity function, and compute how many should have been observed already.

For this first term of the project, I will probably spend most of my time gathering the luminosity functions and starting to reproduce the GCE, saving simulations and data analysis for a later term.

\section{Personal Statement}
I have been interested in astrophysics for most of my life, but the actual process of research is still new to me. I have learned from previous research projects---ranging from theoretical studies of Schwarzschild de Sitter black holes, to creating data analysis algorithms for use in the Large Hadron Collider, to analyses of time-indexed images of stellar clusters---that I am most drawn to projects with a foot in both worlds: theoretically-motivated, but backed up by observation. This UROP fits this category well.

It is also rare to find an undergraduate research opportunity so closely related to the most fundamental laws of physics. Some develop a new data analysis tool; some compile data points to add to an astrophysical catalog. But this UROP is a step in the long walk to understanding dark matter, one of the most mysterious substances remaining in the universe. I have never been involved in a project like this before, and I am excited to get started.

\section{Personal Goals}
Aside from the experience of working on a half-theoretical, half-observational research project, and aiding the effort to understand dark matter, I am looking forward to better understanding what professional research is like. I intend to apply to grad school, and I would like to be as sure as possible that research is what I want to do for a living before I graduate MIT.

I would also like to do a senior thesis next year. This project may or may not become that thesis project, but if not, it would certainly develop experience that I would use for my thesis.

\begin{thebibliography}{99}
    \bibitem{fermilab}Y. Zhong, S. McDermott, I. Cholis, P. Fox. ``A New Mask for An Old Suspect: Testing the Sensitivity of the Galactic Center Excess to the Point Source Mask.'' arXiv:1911.12369v (2019).

    \bibitem{tracy3}R. Leane, T. Slatyer. ``Spurious Point Source Signals in the Galactic Center Excess.'' arXiv:2002.12370v1 (2020).

    \bibitem{bartels}R. Bartels, S. Krishnamurthy, G. Weniger. ``Strong Support for the Millisecond Pulsar Origin of the Galactic Center GeV Excess.'' \textit{Phys. Rev. Lett} (2016).

    \bibitem{tracy1}S. Lee, M. Lisanti, B Safdi, T. Slatyer, W. Xue. ``Evidence for Unresolved $\gamma$-Ray Point Sources in the Inner Galaxy.'' \textit{Phys. Rev. Lett} (2016).

    \bibitem{tracy2}R. Leane, T. Slatyer. ``Dark Matter Strikes Back at the Galactic Center.'' arXiv:1904.08430v1 (2019).

\end{thebibliography}

\end{document}

### 2020-10-21 summaries/oct-2020/oct-2020.tex
initial commit

\documentclass{C://Aliases//Dropbox-MIT//Latex_Templates//personal}

\author{Jack Dinsmore}
\title{GCE UROP Summary}

\begin{document}
\maketitle

\begin{abstract}
This month, I experimented with two luminosity functions: a power-law distribution, and a log-normal distribution. Each luminosity function has two free parameters which can be refined to match two recently-published observations made by the \textit{Fermi} space telescope.
\end{abstract}

\section{Introduction}
\subsection{The GCE}
The Galactic Center GeV Excess (GCE) is an unexpected source of gamma radiation originating from the center of the Milky Way, detected  recently by the \textit{Fermi} Gamma-ray Space Telescope \cite{fermilab}. Its origin is debated; the GCE holds potential to be the first evidence observed for dark matter annihilation, yet several studies have also shown that point sources such as millisecond pulsars (MSPs) may be responsible for the excess.

This UROP seeks to better understand the MSP model to the GCE by proposing different luminosity functions and counting the number of MSPs required to reproduce the GCE for each model, restricting the range of possibilities via \textit{Fermi}'s observations.

For the purposes of this summary, we will take the luminosity of the GCE to be \SI{6.37}{\erg \per\second}, which is consistent with the luminosity used in ref. \cite{fermilab}.

\subsection{Observations}
The \textit{Fermi} Space Telescope has observed two features which we explore in this summary. We model the sensitivity of the telescope as a step function, with the telescope detecting no pulsars of luminosity below $L_{t} = \SI{e34}{\erg\per\second}$ and all the pulsars above it.

As documented in ref. \cite{fermilab}, \textit{Fermi} has observed 47 point sources that could be part of the GCE. It is therefore likely that $N_t$, the number of MSPs in the GCE that have luminosity greater than \textit{Fermi}'s sensitivity is less than or equal to $N_t$. For any luminosity function, this observation will therefore limit the parameter space of distributions.

The same team discovered that the amount of flux visible from the GCE above the threshold of \textit{Fermi} is about one quarter of that below the threshold. We denote this ratio $R$. Similarly, it is likely that the true value of this ratio is less than or equal to one quarter, which further limits the parameter space of luminosity functions.

\subsection{Luminosity functions}
A luminosity function is the distribution of the MSP population's luminosity, $\frac{dN}{dL}$. We explore two basic luminosity functions. The first is a power law with a hard cutoff, parameterized by the minimum and maximum luminosities of the population $L_{min}$ and $L_{max}$ respectively: 
$$\frac{dN}{dL} = L^{-\alpha}, \indent L\in [L_{min}, L_{max}]$$
which was used by ref. \cite{fermilab}. Here, $\alpha$ is a fixed value which was taken at about $1.95$ by ref. \cite{fermilab} to match their observations, but could be 1.2 to 1.5 for a more physically realistic luminosity function. We also used a variant of this luminosity function, which is called a power law with an exponential cutoff:
$$\frac{dN}{dL} = L^{-\alpha}\expp{\frac{L}{L_{max}}}, \indent L\in [L_{min}, \infty]$$

The second luminosity function is log-normal parameterized by the mode luminosity $L_0$ and the standard deviation in log-space around that peak $\sigma$: 
$$\frac{dN}{dL} = \frac{\log_{10}e}{\sigma \sqrt{2\pi} L}\expp{-\frac{\parens{\log_{10} L - \log_{10}L_0}^2}{2\sigma^2}}, \indent L\in [0, \infty]$$
which was used by ref. \cite{log-normal}.

Of these, the log-normal luminosity function is more physically relevant, but the power law is simpler. Both have been studied in detail by the papers cited, but the observations from \textit{Fermi} have not yet been applied to a log-normal luminosity function, so it is useful to compare the two in this light.

We will mostly use an exponential cutoff for the power law luminosity function in this summary. The two models differ in projected number of MSPs in the GCE by only about 10 percent for values of $L_{min}$ and $L_{max}$ not to close to $L_t$, and increases to as much as 40 percent when $L_{min}, L_{max} \rightarrow L_t$.

\section{Power law luminosity function data}
Assuming that the luminosity function of the GCE is well modeled as a power law, a good first approach is to simply plot the number of pulsars necessary to produce the entire GCE as a function of the two parameters $L_{min}$ and $L_{max}$ of the power law. We can express the number of pulsars $N_t$ above \textit{Fermi}'s threshold and the ratio of luminosity $R$ above and below the threshold as a function of the parameters of the luminosity function also, which gives us a one-parameter family of configurations that matches each observation. See figure \ref{contour-overlay-power-law}.

\begin{figure}[h]
    \label{contour-overlay-power-law}
    \centering
    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-overlay.png}
    \caption{Above is plotted the number of MSPs needed to reproduce the GCE under a power law luminosity with an exponential cutoff. In red is plotted the configurations required to match \textit{Fermi}'s observation of $R=1/4$, and in green their observation that $N_f = 47$. }
\end{figure}

The intersection point between these two families represents the only power law configuration that simultaneously realizes both of \textit{Fermi}'s observations, and it corresponds to $\si{3.3e6}$ MSPs in the GCE which is unrealistic. The region for $R < 1/4$ and $N_f < 47$, which is allowed by observation, appears beneath both curves.

To better understand this result, we show the same plot, but with contours representing other values of $R$ and $N_f$ superimposed on the number of pulsars (figure \ref{contour-overlay-extra-power-law}). One sees the limit imposed by the number of observed pulsars is more restrictive than that imposed by the luminosity observed above the threshold in this range of $L_{max}$.

\begin{figure}[h]
    \label{contour-overlay-extra-power-law}
    \centering
    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-overlay-extra.png}
    \caption{Above is plotted the number of MSPs needed to reproduce the GCE under a power law luminosity with an exponential cutoff. In red curves are plotted different values of $R$, with yellow representing higher values, while different values of $N_f$ are plotted in green, with brighter green representing higher $N_f$. The Fermilab results $R=1/4$ and $N_f=47$ are bolded.}
\end{figure}

To better understand the role of $\alpha$ in determining the intersection points of $R=1/4$ and $N_f = 47$, we can plot the curves representing these two families for many $\alpha$ (see figure \ref{contour-vary-alpha}). One can see that to satisfy both observational requirements, a high $L_{min}$ is required, quite close to $L_t$.

\begin{figure}[h]
    \label{contour-vary-alpha}
    \centering
    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-vary-alpha-exp.png}
    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-vary-alpha-hard.png}
    \caption{Above is plotted the curves representing $R=1/4$ and $N_f=47$ for various $\alpha$ from 1.22 to 2.5. Higher $\alpha$ correspond to brighter colors. The blue curve represents the intersection points of these families for each $\alpha$. An exponential cutoff is used in the top plot, and a hard cutoff for the bottom.}
\end{figure}

\section{Log-normal luminosity function data}
For the sake of comparing a log-normal luminosity function to a power law, we can reproduce the same graphs for a log-normal luminosity function (figure \ref{contour-overlay-log-normal}). The region of $N_f \leq 47$ lies below the lower green line and above the upper, while $R \leq 1/4$ lies below the red line. Thus, the configurations allowed by \textit{Fermi}'s observations lies in the triangle below the lower green line. For these values of $R$ and $N_f$, the corresponding families are roughly parallel, but this is not true in general. From the lower plot in this figure, it can be seen that the curves in the upper plot do not vary greatly with changes in $R$ and $N_f$.

\begin{figure}[h]
    \label{contour-overlay-log-normal}
    \centering
    \includegraphics[width=0.6\textwidth]{../../luminosity-models/log-normal/contour-overlay.png}
    \includegraphics[width=0.6\textwidth]{../../luminosity-models/log-normal/contour-overlay-extra.png}
    \caption{The number of MSPs needed to reproduce the GCE under a log-normal luminosity. On the top plot, the configurations required to match \textit{Fermi}'s observation of $R=1/4$ are shown in red, and in green their observation that $N_f = 47$. The plot is expanded for the lower plot to different values of $R$ and $N_f$, with higher $R$ and $N_f$ represented by brighter colors.}
\end{figure}

The minimum number of MSPs inside this ``allowed triangle'' is 650, but that occurs for vanishingly low $\sigma$. Ref. \cite{log-normal} predicted values of $\sigma = 0.62^{+0.15}_{-0.5}$ and $L_0 = \brackets{0.88^{+0.79}_{-0.41}}\times\SI{e34}{\erg\per\second}$. Allowing $\sigma$ to range within one standard deviation of this assessment, the minimum number of pulsars required to reproduce the entire GCE and meet the $N_f=47$ requirement is $3920$, a reasonable number. This point occurs at $\sigma = 0.46$ and $L_0 = \SI{9.26e32}{\erg\per\second}$ and is shown as a blue dot in figure \ref{contour-overlay-log-normal}. However, the exact $(\sigma, L_0)$ components of the paper predict $N_f=121$ and $R=10$, which disagrees thoroughly with experiment.

\begin{thebibliography}{99}
    \bibitem{fermilab}Y. Zhong, S. McDermott, I. Cholis, P. Fox. ``A New Mask for An Old Suspect: Testing the Sensitivity of the Galactic Center Excess to the Point Source Mask.'' arXiv:1911.12369v (2019).

    \bibitem{log-normal}D. Hooper and T. Linden. ``The Gamma-Ray Pulsar Population of
    Globular Clusters: Implications for the
    GeV Excess.'' \textit{JCAP} (2016).

\end{thebibliography}

\end{document}

### 2020-10-21 luminosity-models/log-normal/contour-overlay.py

@@ -1,0 +1,168 @@
+from matplotlib import pyplot as plt
+from math import log, exp, sqrt
+from scipy.special import erfc, erf
+import matplotlib.colors as colors
+
+DIM_TRIALS=100
+
+L_EXCESS = 6.37e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_0_RANGE=[1.0e32, 2.0e34]
+SIGMA_L_RANGE=[0.001, 1]
+powerStep =(L_0_RANGE[1] / L_0_RANGE[0])**(1/DIM_TRIALS)
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/4.0
+
+DRAW_EXTRA_CONTOURS = True
+
+def getNumPulsars(L, sigma):
+    totalLum = exp(0.5 * sigma**2 * log(10)**2) * L
+    A = L_EXCESS / totalLum
+    return A * 1 # A times number of pulsars per unit
+
+def getNumPulsarsAboveThreshold(L, sigma):
+    totalLum = exp(0.5 * sigma**2 * log(10)**2) * L
+    A = L_EXCESS / totalLum
+    return A * 0.5 * erfc((log(L_THRESH) - log(L)) / (sqrt(2) * sigma * log(10)))# A times number of pulsars above threshold per unit
+
+def getFracLumAboveThreshold(L, sigma):
+    # return (lum above thresh) / (lum below thresh)
+    erfArgument = (sqrt(2) * (sigma**2 * log(10)**2 - log(L_THRESH) + log(L))) / (sigma * log(100))
+    amountAbove = 1 + erf(erfArgument)
+    amountBelow = 1 - erf(erfArgument)
+    return amountAbove / amountBelow
+
+
+def getMinNumPulsarsInTriangle():
+    EXTRA_DENSITY = 2
+    minSoFar = -1
+    powerStepNew =(L_0_RANGE[1] / L_0_RANGE[0])**(1/(DIM_TRIALS * EXTRA_DENSITY))
+    for j in range(DIM_TRIALS * EXTRA_DENSITY):
+        sigma= SIGMA_L_RANGE[0]  + (SIGMA_L_RANGE[1]-SIGMA_L_RANGE[0]) / (DIM_TRIALS * EXTRA_DENSITY) * j
+        for i in range(DIM_TRIALS * EXTRA_DENSITY):
[…]

### 2020-10-21 luminosity-models/power-law/contour-overlay.py

@@ -1,0 +1,134 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+from scipy.special import gammainc, gamma
+import matplotlib.colors as colors
+
+POWER_STEP = 1.1 # 1 is the minimum
+
+ALPHA_L = 1.94
+L_EXCESS = 6.37e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN_RANGE=[1.0e28, 1.0e34]
+L_MAX_RANGE=[1.0e34, 1.0e36]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/4.0
+
+DRAW_EXTRA_CONTOURS = True
+
+dimMin= int(log(L_MIN_RANGE[1]/L_MIN_RANGE[0]) / log(POWER_STEP))
+dimMax= int(log(L_MAX_RANGE[1]/L_MAX_RANGE[0]) / log(POWER_STEP))
+
+def Gamma(s, x):
+    if(s < 0):
+        return (Gamma(s+1, x) - x**s * exp(-x))/s
+    return gamma(s) * (1-gammainc(s, x))
+
+def getNumPulsars(lMin, lMax):
+    lumExp = lMax**(2-ALPHA_L) * Gamma(2-ALPHA_L, lMin / lMax)
+    Aexp = L_EXCESS / lumExp
+    Nexp = Aexp *  lMax**(1-ALPHA_L) * Gamma(1-ALPHA_L, lMin / lMax)
+
+    return Nexp
+
+def getNumPulsarsAboveThreshold(lMin, lMax):
+    lumExp = lMax**(2-ALPHA_L) * Gamma(2-ALPHA_L, lMin / lMax)
+    Aexp = L_EXCESS / lumExp
+    nAbove = Aexp *  lMax**(1-ALPHA_L) * Gamma(1-ALPHA_L, L_THRESH / lMax)
+    return nAbove
+
+def getFracLumAboveThreshold(lMin, lMax):
+    # return (lum above thresh) / (lum below thresh)
+    fracAbove = Gamma(2-ALPHA_L, L_THRESH / lMax) / (Gamma(2-ALPHA_L, lMin / lMax) - Gamma(2-ALPHA_L, L_THRESH / lMax))
+    return fracAbove
+
+
+print("Paper values:", getNumPulsars(1e29, 1e35))
[…]

### 2020-10-21 luminosity-models/power-law/contour-vary-alpha-exp.py

@@ -1,0 +1,106 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+from scipy.special import gammainc, gamma
+import matplotlib.colors as colors
+
+POWER_STEP = 1.1 #1.05# 1 is the minimum
+
+
+ALPHA_L_MIN = 1.21
+ALPHA_L_MAX = 2.5
+PLOT_EVERY = 2
+ALPHA_L_INCREMENT = 0.02
+
+ALPHA_L = ALPHA_L_MIN
+L_EXCESS = 6.37e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN_RANGE=[1.0e28, 1.0e34]
+L_MAX_RANGE=[1.0e33, 1.0e37]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/4.0
+
+dimMin= int(log(L_MIN_RANGE[1]/L_MIN_RANGE[0]) / log(POWER_STEP))
+dimMax= int(log(L_MAX_RANGE[1]/L_MAX_RANGE[0]) / log(POWER_STEP))
+
+def Gamma(s, x):
+    if(s < 0):
+        return (Gamma(s+1, x) - x**s * exp(-x))/s
+    return gamma(s) * (1-gammainc(s, x))
+    
+def getNumPulsars(lMin, lMax):
+    lumExp = lMax**(2-ALPHA_L) * Gamma(2-ALPHA_L, lMin / lMax)
+    Aexp = L_EXCESS / lumExp
+    Nexp = Aexp *  lMax**(1-ALPHA_L) * Gamma(1-ALPHA_L, lMin / lMax)
+
+    return Nexp
+
+def getNumPulsarsAboveThreshold(lMin, lMax):
+    lumExp = lMax**(2-ALPHA_L) * Gamma(2-ALPHA_L, lMin / lMax)
+    Aexp = L_EXCESS / lumExp
+    nAbove = Aexp *  lMax**(1-ALPHA_L) * Gamma(1-ALPHA_L, L_THRESH / lMax)
+    return nAbove
+
+def getFracLumAboveThreshold(lMin, lMax):
+    fracAbove = Gamma(2-ALPHA_L, L_THRESH / lMax) / (Gamma(2-ALPHA_L, lMin / lMax) - Gamma(2-ALPHA_L, L_THRESH / lMax))
+    return fracAbove
+
+fig, ax = plt.subplots(figsize=(6,4))
[…]

### 2020-10-21 luminosity-models/power-law/contour-vary-alpha-hard.py

@@ -1,0 +1,100 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+import matplotlib.colors as colors
+
+POWER_STEP = 1.1#1.05 # 1 is the minimum
+
+
+ALPHA_L_MIN = 1.21
+ALPHA_L_MAX = 2.5
+PLOT_EVERY = 2#4
+ALPHA_L_INCREMENT = 0.02
+
+ALPHA_L = ALPHA_L_MIN
+L_EXCESS = 6.37e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN_RANGE=[1.0e28, 1.0e34]
+L_MAX_RANGE=[1.0e33, 1.0e37]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/4.0
+
+dimMin= int(log(L_MIN_RANGE[1]/L_MIN_RANGE[0]) / log(POWER_STEP))
+dimMax= int(log(L_MAX_RANGE[1]/L_MAX_RANGE[0]) / log(POWER_STEP))
+    
+def getNumPulsars(lMin, lMax):
+    lum = 1/(ALPHA_L - 2) * (lMin **(2 - ALPHA_L) - lMax**(2 - ALPHA_L))
+    A = L_EXCESS / lum
+    N = A *  1/(ALPHA_L - 1) * (lMin **(1 - ALPHA_L) - lMax**(1 - ALPHA_L))
+    return N
+
+def getNumPulsarsAboveThreshold(lMin, lMax):
+    lum = 1/(ALPHA_L - 2) * (lMin **(2 - ALPHA_L) - lMax**(2 - ALPHA_L))
+    A = L_EXCESS / lum
+    nAbove = A *  1/(ALPHA_L - 1) * (L_THRESH **(1 - ALPHA_L) - lMax**(1 - ALPHA_L))
+    return nAbove
+
+def getFracLumAboveThreshold(lMin, lMax):
+    # return (lum above thresh) / (lum below thresh)
+    fracAbove = (1/(ALPHA_L - 2) * (L_THRESH **(2 - ALPHA_L) - lMax**(2 - ALPHA_L))) / (1/(ALPHA_L - 2) * (lMin **(2 - ALPHA_L) - L_THRESH**(2 - ALPHA_L)))
+    return fracAbove
+
+fig, ax = plt.subplots(figsize=(6,4))
[…]

### 2021-06-08 compare-spectra/lum-to-flux.py
First commit in a long time

@@ -7,7 +7,7 @@ from math import pi, cos, sqrt
 DELTA_ANGLE = 0.01
 DELTA_S = 0.01
 R_C=8.5
-R_S=20
+R_S=300
 GAMMA = 1.2
 KPC_SQUARED_PER_CM_SQUARED = 3.24078e-22**2
 

### 2021-06-08 compare-spectra/numerical-integration.py

@@ -1,0 +1,111 @@
+import numpy as np
+import parse_spectrum as ps
+from matplotlib import pyplot as plt
+import matplotlib.lines as mlines
+import matplotlib.transforms as mtrans
+
+plt.style.use("latex")
+
+SPECTRUM_RANGE = [0.5, 10]# GeV
+NUM_PLOTS = 7
+
+fig, axes = plt.subplots(nrows=3, ncols=3, figsize=(10, 6), sharex='col', sharey='row')
+
+allfig, allax = plt.subplots()
+
+def sciNot(i):
+    if i == None:
+        return "None"
+    if i == np.nan:
+        return "NaN"
+    if i == 0:
+        return "0"
+    negative = False
+    if i < 0:
+        negative = True
+        i *= -1
+    d = int(np.log10(i))
+    if np.log10(i) < 0: d -= 1
+    if not negative:
+        return str(round(i / 10**d, 3)) + "e"+str(d)
+    return "-"+str(round(i / 10**d, 3)) + "e"+str(d)
+
+num_fluxes = []
+calore_fluxes = []
+fit_fluxes = []
+names = []
+
+for i in range(0, NUM_PLOTS):
+    ax = axes[i%3][i//3]
+    f = ps.Spectrum(i)
+    names.append(f.get_name())
+    f.display_data(allax, color="C"+str(i))
+    f.display_data(ax)
+    f.display_calore(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+    f.display_power_law(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+    numerical_flux = f.get_numerical_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+    calore_flux = f.get_calore_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+    fit_flux = f.get_power_law_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+    num_fluxes.append(numerical_flux)
+    calore_fluxes.append(calore_flux)
+    fit_fluxes.append(fit_flux)
+    if i//3 == 0:
+        ax.set_ylabel(f.get_y_label())
+    if i % 3 == 1:
+        ax.set_xlabel(f.get_x_label())
+
+    f.label_axes(allax)
+
+    print(f.get_name(), numerical_flux)
+    
[…]

### 2021-06-08 compare-spectra/photon-energy.py

@@ -1,0 +1,46 @@
+OLD = 0
+FERMILAB = 1
+CALORE = 2
+ERG_PER_GEV = 0.00160218
+SIZE_OF_ROI = 0.42882 # steradians
+L_BREAK = 2.06 * ERG_PER_GEV
+ALPHA_ABOVE = 2.63
+ALPHA_BELOW = 1.42
+
+TYPE = FERMILAB
+
+# The type doesn't actually matter; it doesn't come into the calcualtion
+
+SCALE = 0 # Units in erg / cm^2 / s
+if TYPE == OLD:
+    raise Exception("Old values unimplemented")
+if TYPE == FERMILAB:
+    SCALE = 25.87693692 * ERG_PER_GEV * SIZE_OF_ROI
+if TYPE == CALORE:
+    SCALE = 44.78745446 * ERG_PER_GEV * SIZE_OF_ROI
+
+def integrate(start, stop):
+    topAlpha = ALPHA_ABOVE if stop > L_BREAK else ALPHA_BELOW
+    bottomAlpha = ALPHA_BELOW if start < L_BREAK else ALPHA_ABOVE
+    return L_BREAK / (1 - bottomAlpha) * (1 - (start / L_BREAK)**(1 - bottomAlpha)) + \
+        L_BREAK / (1 - topAlpha) * ((stop / L_BREAK)**(1 - topAlpha) - 1)
+    
+
+def lintegrate(start, stop):
+    topAlpha = ALPHA_ABOVE if stop > L_BREAK else ALPHA_BELOW
+    bottomAlpha = ALPHA_BELOW if start < L_BREAK else ALPHA_ABOVE
+    return L_BREAK**2 / (2 - bottomAlpha) * (1 - (start / L_BREAK)**(2 - bottomAlpha)) + \
+        L_BREAK**2 / (2 - topAlpha) * ((stop / L_BREAK)**(2 - topAlpha) - 1)
+
+def getPhotonEnergy(start, stop):
+    return lintegrate(start, stop) / integrate(start, stop) # Units of ergs
+
+spectrumName = "old"
+if TYPE == FERMILAB:
+    spectrumName = "Fermilab"
+if TYPE == CALORE:
+    spectrumName = "Calore"
+print("Using {} spectrum".format(spectrumName))
+
[…]

### 2021-06-08 flux-histograms/total-hist/4fgl-display.py

@@ -1,0 +1,70 @@
+from astropy.io import fits
+import numpy as np
+from matplotlib import pyplot as plt
+from math import log10
+
+plt.style.use('latex')
+
+hdul = fits.open('gll_psc_v27.fit')
+hdul.info()
+print('\n'.join(str(hdul[1].header).split("/")))
+data = hdul[1].data
+hdul.close()
+
+DIST_FROM_GALACTIC_CENTER_KILOPARSEC = 8.5
+CM_PER_KILOPARSEC = 3.086e21
+PI = 3.1415926535
+
+
+
+excludeMask = np.ones(data.shape[0], dtype=bool)
+
+
+# Functions to filter point sources I don't want to include in my analysis
+def excludeLatLong(excludeMask):
+    thisMask = np.ones(data.shape[0], dtype=bool)
+    thisMask = thisMask & ((data["GLON"] < 20) | (data["GLON"] > 340))
+    thisMask = thisMask & (((-20 < data["GLAT"]) & (data["GLAT"] < -2))
+        | ((2 < data["GLAT"]) & (data["GLAT"] < 20)))
+    return excludeMask & thisMask
+
+def convertFluxToLuminosity(flux):
+    return flux * (4 * PI * (DIST_FROM_GALACTIC_CENTER_KILOPARSEC * CM_PER_KILOPARSEC)**2)
+
+
+# Apply filters
+excludeMask = excludeLatLong(excludeMask)
+
+print(data.shape)
+data = data[excludeMask]
+print(data.shape)
+
+
+# Generate flux histogram
+fluxData = data["Energy_Flux100"]
+bins = 10**np.linspace(start=log10(np.min(fluxData)), stop=log10(np.max(fluxData)), num=50)
+
+plt.figure()
+plt.hist(fluxData, bins=bins)
+plt.xlabel("Flux received (ergs / cm^2 / s)")
+plt.ylabel("Point source count")
+plt.xscale('log')
+plt.title("Histogram of point source fluxes (0.1-100 GeV range)")
+plt.savefig("flux.png")
+
+
+# Generate luminosity histogram
+lumData = convertFluxToLuminosity(fluxData)
+bins = 10**np.linspace(start=log10(np.min(lumData)), stop=log10(np.max(lumData)), num=50)
+
+plt.figure()
+fluxData = data["Energy_Flux100"]
+plt.hist(lumData, bins=bins)
+plt.xlabel("Luminosity (ergs / s)")
[…]

### 2021-06-08 luminosity-models-position/graph-log-normal.py

@@ -13,7 +13,7 @@ PLOT_SIZE = 50
 L_0_RANGE=[1.0e30, 2.0e36]#[1.0e32, 2.0e34]
 SIGMA_L_RANGE=[0.001, 1]
 
-MULTIPLIER = 5
+MULTIPLIER = 1
 
 lOPowerStep = (L_0_RANGE[1] / L_0_RANGE[0]) ** (1.0 / PLOT_SIZE)
 
@@ -28,7 +28,7 @@ DRAW_PLOEG_POINT = True
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
 
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-"+str(MULTIPLIER)+"x/log-normal/"
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/log-normal/"
 SHADE_SCALE=25
 
 def shade(field, threshold, xs, ys, off=False):

### 2021-06-08 luminosity-models-position/graph-power-law-alpha.py

@@ -5,7 +5,7 @@ import matplotlib.colors as colors
 from matplotlib.lines import Line2D
 import numpy as np
 
-plt.style.use('latex')
+plt.style.use('revtex')
 
 
 PLOT_SIZE = 50
@@ -87,9 +87,9 @@ for line in f.read().split('\n')[:-1]:
         enterLine.append(float(item) / TOTAL_FLUX)
     lumSeen.append(np.asarray(enterLine))
 
-totalNum = np.stack(totalNum, axis=0)
-numSeen = np.stack(numSeen, axis=0)
-lumSeen = np.stack(lumSeen, axis=0)
+totalNum = np.transpose(np.stack(totalNum, axis=0))
+numSeen = np.transpose(np.stack(numSeen, axis=0))
+lumSeen = np.transpose(np.stack(lumSeen, axis=0))
 
 # ========================= Display data =========================
 
@@ -101,10 +101,10 @@ lMaxVals = [L_MAX_RANGE[0] * maxPowerStep**j for j in range(PLOT_SIZE)]
 
 fig, ax = plt.subplots(figsize=(6, 4))
 
-plt.xscale("log")
+#plt.xscale("log")
 plt.yscale("log")
-plt.xlabel("$L_{max}$")
-plt.ylabel("$L_{min}$")
+plt.xlabel("$\\alpha$")
+plt.ylabel("$L_\mathrm{max}$")
 plt.title("Power-law, position-dependent{}".format("" if MULTIPLIER is None else (", sensitivity x"+str(MULTIPLIER))))
 
 c1 = plt.pcolor(alphaVals, lMaxVals, totalNum, 

### 2021-06-08 luminosity-models-step/log-normal/compare-flux/contour-overlay.py

@@ -1,0 +1,227 @@
+from matplotlib import pyplot as plt
+from math import log, exp, sqrt
+from scipy.special import erfc, erf
+import matplotlib.colors as colors
+from matplotlib.lines import Line2D
+import numpy as np
+
+plt.style.use('latex')
+
+DIM_TRIALS=100
+
+L_EXCESS = 2*1.6924845e+37# 6.756e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_0_RANGE=[1.0e30, 2.0e36]#[1.0e32, 2.0e34]
+SIGMA_L_RANGE=[0.001, 1]
+powerStep =(L_0_RANGE[1] / L_0_RANGE[0])**(1/DIM_TRIALS)
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/5.0
+LINE_COLOR = (0.8, 0.3, 0.1)
+
+DRAW_EXTRA_CONTOURS = False
+DRAW_PLOEG_POINT = True
+SHADE_SCALE=25
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
+
+def getTotalLum(L0, sigma):
+    return exp(0.5 * sigma**2 * log(10)**2) * L0
+
+def getNumPulsars(L0, sigma):
+    scale = L_EXCESS / getTotalLum(L0, sigma)
+    return scale * 1 # scale times number of pulsars per unit
+
+def getNumPulsarsAboveThreshold(L0, sigma):
+    scale = L_EXCESS / getTotalLum(L0, sigma)
[…]

### 2021-06-08 luminosity-models-step/log-normal/contour-overlay.py

@@ -9,7 +9,7 @@ plt.style.use('latex')
 
 DIM_TRIALS=100
 
-L_EXCESS = 6.756e36  # All units are in ergs per second
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47# 6.756e36  # All units are in ergs per second
 L_THRESH = 1.0e34
 L_0_RANGE=[1.0e30, 2.0e36]#[1.0e32, 2.0e34]
 SIGMA_L_RANGE=[0.001, 1]
@@ -222,6 +222,6 @@ plt.tight_layout()
 if(DRAW_EXTRA_CONTOURS):
     plt.savefig("contour-overlay-extra.png")
 if(not DRAW_EXTRA_CONTOURS):
-    plt.savefig("contour-overlay.png")
+    plt.savefig("overlay.png")
 
 plt.show()

### 2021-06-08 luminosity-models-step/power-law-alpha/contour-overlay.py

@@ -9,11 +9,11 @@ plt.style.use('latex')
 
 POWER_STEP = 1.1 # 1 is the minimum
 
-L_EXCESS = 6.756e36# 6.37e36  # All units are in ergs per second
+L_EXCESS = 9.7787012e+36# 6.756e36# 6.37e36  # All units are in ergs per second
 L_THRESH = 1.0e34
 L_MIN = 1e29
 ALPHA_RANGE = [1.1, 2.5]
-L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+L_MAX_RANGE = [1.0e33, 1.0e38]#[1.0e34, 1.0e36]
 
 NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=1/5.0

### 2021-06-08 luminosity-models-step/power-law/contour-overlay.py

@@ -10,7 +10,7 @@ plt.style.use('latex')
 POWER_STEP = 1.1 # 1 is the minimum
 
 ALPHA_L = 1.94
-L_EXCESS = 6.756e36# 6.37e36  # All units are in ergs per second
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47#6.756e36# 6.37e36  # All units are in ergs per second
 L_THRESH = 1.0e34
 L_MIN_RANGE = [1.0e28, 1.0e34]
 L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
@@ -176,10 +176,12 @@ plt.xlim(lMaxVals[0], lMaxVals[-1])
 plt.ylim(lMinVals[0], lMinVals[-1])
 plt.tight_layout()
 
+print([np.percentile(numPulsars, i) for i in range(0, 100, 10)])
+
 
 if(DRAW_EXTRA_CONTOURS):
-    plt.savefig("contour-overlay-extra.png")
+    plt.savefig("overlay-extra.png")
 if(not DRAW_EXTRA_CONTOURS):
-    plt.savefig("contour-overlay.png")
+    plt.savefig("overlay.png")
 
 plt.show()

### 2021-06-08 multiple-flux-values/luminosity-models-position/graph-power-law-alpha.py

@@ -1,0 +1,149 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+from scipy.special import gammainc, gamma
+import matplotlib.colors as colors
+from matplotlib.lines import Line2D
+import numpy as np
+
+plt.style.use('revtex')
+
+
+FERMILAB_GNFW_FLUX = 5.716826056794996e-10
+CALORE_FLUX = 1.3592975571782718e-09
+DI_MAURO_FLUX = 1.2953417255755896e-09
+AJELLO_FLUX = 1.8268259089431682e-09
+FERMILAB_NFW_FLUX = 7.770902203635269e-10
+ABAZAJIAN_FLUX = 4.887121798902831e-10
+
+PLOT_SIZE = 50
+
+L_MIN = 1e29
+ALPHA_RANGE = [1.1, 2.5]
+L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+maxPowerStep = (L_MAX_RANGE[1] / L_MAX_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+MULTIPLIER = 1
+
+paperPoint = [1e35, 1e29]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=0.2
+TOTAL_FLUX =1.2953417255755896e-09
+
+DRAW_EXTRA_CONTOURS = True
+SHOW_NUMBERS = False
+LINE_COLOR = (0.8, 0.3, 0.1)
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/power-law-alpha/"
+SHADE_SCALE=25
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
[…]

### 2021-06-08 multiple-flux-values/luminosity-models-position/graph-power-law.py

@@ -1,0 +1,152 @@
+''' Things to check:
+    Is the NFW profile a number density?
+    What is r_s from the Fermilab paper?
+    I should integrate the square of the NFW profile, not square the integral, right?
+    Am I using the number position distribution and luminosity position distribution in the correct places?
+'''
+
+from matplotlib import pyplot as plt
+import matplotlib.colors as colors
+from math import log
+import numpy as np
+from matplotlib.lines import Line2D
+
+plt.style.use('revtex-presentation')
+
+
+PLOT_SIZE = 50
+
+FERMILAB_GNFW_FLUX = 5.716826056794996e-10
+CALORE_FLUX = 1.3592975571782718e-09
+DI_MAURO_FLUX = 1.2953417255755896e-09
+AJELLO_FLUX = 1.8268259089431682e-09
+FERMILAB_NFW_FLUX = 7.770902203635269e-10
+ABAZAJIAN_FLUX = 4.887121798902831e-10
+
+ALPHA = 1.94
+L_MIN_RANGE = [1.0e28, 1.0e34]
+L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+minPowerStep = (L_MIN_RANGE[1] / L_MIN_RANGE[0]) ** (1.0 / PLOT_SIZE)
+maxPowerStep = (L_MAX_RANGE[1] / L_MAX_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+MULTIPLIER = 1
+
+paperPoint = [1e35, 1e29]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=0.2
+TOTAL_FLUX = 7.494712733226778e-10
+
+DRAW_EXTRA_CONTOURS = True
+SHOW_NUMBERS = False
+LINE_COLOR = (0.8, 0.3, 0.1)
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/power-law/"
+SHADE_SCALE=25
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
[…]

### 2021-06-08 multiple-flux-values/luminosity-models-step/NPTF/get-estimates.py

@@ -1,0 +1,115 @@
+'''
+The purpose of this file is to take the NPTF luminosity function 
+and generate predictions of how many pulsars Fermi should have seen,
+and how much flux above the threshold it should have seen. We expect
+the luminosity to have a short and strong peak below the threshold,
+leading to very few visible pulsars and small visible luminosity. 
+The paper is found here https://arxiv.org/pdf/1506.05124.pdf,
+with a luminosity function described in table 1.
+'''
+
+from matplotlib import pyplot as plt
+import numpy as np
+from math import log10
+
+plt.style.use('latex')
+
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47 # 3.3440751340173124e+36  # 1.893 to 11.943 GeV
+DIST_FROM_GALACTIC_CENTER_KILOPARSEC = 8.5
+CM_PER_KILOPARSEC = 3.086e21
+L_THRESH = 1.0e34
+PI = 3.1415926535
+
+L_MIN = None
+L_MAX = None
+
+CUTOFF_MINIMUM = 1e29
+
+global outStr
+outStr = ""
+
+class LuminosityFunction:
+    def __init__(self, name, nBelow, nAbove, lBreak):
+        self.name = name
+        self.nBelow = nBelow
+        self.nAbove = nAbove
+        self.lBreak = lBreak
+    
+    def integrate(self, minL):
+        if minL is None: minL = CUTOFF_MINIMUM
+        nptfPremul = (self.nBelow - self.nAbove) / (self.nBelow - self.nAbove - (1 - self.nAbove) * pow(CUTOFF_MINIMUM / self.lBreak, 1 - self.nBelow))
+        if (minL < self.lBreak):
+            return nptfPremul * (1 - (self.lBreak / minL) ** (self.nBelow - 1) * (self.nAbove - 1) / (self.nAbove - self.nBelow))
+        else:
+            return nptfPremul * (self.lBreak / minL) ** (self.nAbove - 1) * (1 - self.nBelow) / (self.nAbove - self.nBelow)
+
+    def lintegrate(self, minL):
+        if minL is None: minL = CUTOFF_MINIMUM
+        nptfPremul = (self.nBelow - self.nAbove) / (self.nBelow - self.nAbove - (1 - self.nAbove) * pow(CUTOFF_MINIMUM / self.lBreak, 1 - self.nBelow))
+        if minL < self.lBreak:
[…]

### 2021-06-08 multiple-flux-values/luminosity-models-step/ploeg/get-estimates.py

@@ -1,0 +1,50 @@
+'''
+The purpose of this file is to take the Ploeg luminosity function 
+and generate predictions of how many pulsars Fermi should have seen,
+and how much flux above the threshold it should have seen.
+'''
+
+import ploegload as pl
+from matplotlib import pyplot as plt
+
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN = 1e29
+L_MAX = 1.0e35
+
+outStr = ""
+
+for i in [pl.DISK, pl.LOG_NORMAL_FIT]:
+    f = pl.LuminosityFunction(i)
+    unscaledNumber = f.integrate(L_MIN)
+    unscaledLum = f.lintegrate(L_MIN)
+    unscaledNumberAbove = f.integrate(L_THRESH)
+    unscaledFluxAbove = f.lintegrate(L_THRESH)
+    print(unscaledNumber, unscaledLum, unscaledNumberAbove, unscaledFluxAbove)
+
+    scale = L_EXCESS / unscaledLum
+
+    totalNumber = unscaledNumber * scale
+    totalLum = unscaledLum * scale # Should be L_EXCESS
+    numberAbove = unscaledNumberAbove * scale
+    R = unscaledFluxAbove / unscaledLum
+
+    addStr = """{0} luminosity function:
+    Total number of pulsars:\t\t{1}
+    Total luminosity:\t\t\t{2}
+    Number of pulsars above threshold:\t{3}\t(Fermi: 47)
+    Fraction of lum above threshold:\t{4}\t(Fermi: 0.2)
+""".format(f.getName(), totalNumber, totalLum, numberAbove, R)
+    print(addStr)
+    outStr+=addStr
+    f.display()
+
+f = open("get-estimates-output.txt", 'w')
+f.write(outStr)
+f.close()
+plt.xlim(left=L_MIN, right=L_MAX)
+plt.axvline(x=L_THRESH, label="Threshold", color='black')
+plt.title("Ploeg luminosity functions")
+plt.legend()
+plt.savefig("get-estimates.png")
+plt.show()

### 2021-06-08 multiple-flux-values/luminosity-models-step/ploeg/old-integral-method/get-estimates.py

@@ -1,0 +1,50 @@
+'''
+The purpose of this file is to take the Ploeg luminosity function 
+and generate predictions of how many pulsars Fermi should have seen,
+and how much flux above the threshold it should have seen.
+'''
+
+import ploegload
+from matplotlib import pyplot as plt
+
+L_EXCESS = 6.756e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN = 1e29
+L_MAX = 1.0e35
+
+outStr = ""
+
+for i in range(4):
+    f = ploegload.LuminosityFunction(i)
+    unscaledNumber = f.integrate(minL=L_MIN, maxL=L_MAX)
+    unscaledLum = f.lintegrate(minL=L_MIN, maxL=L_MAX)
+    unscaledNumberAbove = f.integrate(minL=L_THRESH, maxL=L_MAX)
+    unscaledFluxAbove = f.lintegrate(minL=L_THRESH, maxL=L_MAX)
+    print(unscaledNumber, unscaledLum, unscaledNumberAbove, unscaledFluxAbove)
+
+    scale = L_EXCESS / unscaledLum
+
+    totalNumber = unscaledNumber * scale
+    totalLum = unscaledLum * scale # Should be L_EXCESS
+    numberAbove = unscaledNumberAbove * scale
+    R = unscaledFluxAbove / unscaledLum
+
+    addStr = """{0} luminosity function:
+    Total number of pulsars:\t\t{1}
+    Total luminosity:\t\t\t{2}
+    Number of pulsars above threshold:\t{3}\t(Fermi: 47)
+    Fraction of lum above threshold:\t{4}\t(Fermi: 0.2)
+""".format(f.getName(), totalNumber, totalLum, numberAbove, R)
+    print(addStr)
+    outStr+=addStr
+    f.display()
+
+f = open("get-estimates-output.txt", 'w')
+f.write(outStr)
+f.close()
+plt.xlim(left=L_MIN, right=L_MAX)
+plt.axvline(x=L_THRESH, label="Threshold", color='black')
+plt.title("Ploeg luminosity functions")
+plt.legend()
+plt.savefig("get-estimates.png")
+plt.show()

### 2021-06-08 multiple-flux-values/luminosity-models-step/power-law-alpha/contour-overlay.py

@@ -1,0 +1,171 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+from scipy.special import gammainc, gamma
+import matplotlib.colors as colors
+from matplotlib.lines import Line2D
+import numpy as np
+
+plt.style.use('latex')
+
+POWER_STEP = 1.1 # 1 is the minimum
+
+FERMILAB_GNFW_FLUX = 5.716826056794996e-10
+CALORE_FLUX = 1.3592975571782718e-09
+DI_MAURO_FLUX = 1.2953417255755896e-09
+AJELLO_FLUX = 1.8268259089431682e-09
+FERMILAB_NFW_FLUX = 7.770902203635269e-10
+ABAZAJIAN_FLUX = 4.887121798902831e-10
+
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47#6.756e36# 6.37e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN = 1e29
+ALPHA_RANGE = [1.1, 2.5]
+L_MAX_RANGE = [1.0e33, 1.0e38]#[1.0e34, 1.0e36]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/5.0
+
+DRAW_EXTRA_CONTOURS = True
+SHOW_NUMBERS = False
+LINE_COLOR = (0.8, 0.3, 0.1)
+SHADE_SCALE=25
+
+dimAlpha= 50
+dimMax= int(log(L_MAX_RANGE[1]/L_MAX_RANGE[0]) / log(POWER_STEP))
+
+paperPoint = [1e35, 1.94]
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
[…]

### 2021-06-08 multiple-flux-values/luminosity-models-step/power-law/contour-overlay.py

@@ -1,0 +1,200 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+from scipy.special import gammainc, gamma
+import matplotlib.colors as colors
+from matplotlib.lines import Line2D
+import numpy as np
+
+plt.style.use('latex')
+
+POWER_STEP = 1.1 # 1 is the minimum
+
+FERMILAB_GNFW_FLUX = 5.716826056794996e-10
+CALORE_FLUX = 1.3592975571782718e-09
+DI_MAURO_FLUX = 1.2953417255755896e-09
+AJELLO_FLUX = 1.8268259089431682e-09
+FERMILAB_NFW_FLUX = 7.770902203635269e-10
+ABAZAJIAN_FLUX = 4.887121798902831e-10
+
+ALPHA_L = 1.94
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47#6.756e36# 6.37e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN_RANGE = [1.0e28, 1.0e34]
+L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/5.0
+
+DRAW_EXTRA_CONTOURS = True
+SHOW_NUMBERS = False
+LINE_COLOR = (0.8, 0.3, 0.1)
+SHADE_SCALE=25
+
+dimMin= int(log(L_MIN_RANGE[1]/L_MIN_RANGE[0]) / log(POWER_STEP))
+dimMax= int(log(L_MAX_RANGE[1]/L_MAX_RANGE[0]) / log(POWER_STEP))
+
+paperPoint = [1e35, 1e29]
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
[…]

### 2021-06-09 luminosity-models-position/overlay-calculator/overlay-calculator/overlay-calculator.cpp
Changed tabs to spaces

@@ -16,7 +16,7 @@ typedef std::vector<std::vector<double>> DoubleVector;
 /* When LOTS_OF_THREADS is defined, a target of 80-90 threads are made and run concurrently.
    Otherwise, four threads are made and run concurrently. */
 
-#define SENSITIVITY_DIVISOR 1.0
+#define SENSITIVITY_DIVISOR 10.0
 
 #define pi 3.14159265358979323
 #define ONE_PLUS_EPSILON 1.0000000001
@@ -28,7 +28,7 @@ typedef std::vector<std::vector<double>> DoubleVector;
 #define CM_PER_KPC_SQUARED 9.523396e+42
 #define FLUX_EXCESS 1.2953417255755896e-09  // All flux units are in ergs per second per square centimeter
 
-#define FLUX_HIST_BINS 100
+#define FLUX_HIST_BINS 40
 #define FLUX_HIST_LOW 1.0731612e-12
 #define FLUX_HIST_HIGH 1.3719972e-09
 #define ALPHA_HIST 1.94
@@ -75,234 +75,234 @@ double nptfPremul = 0;
 double nptfLMin = 0;
 
 enum class VALUE {
-	TOTAL_NUM,
-	TOTAL_FLUX,
-	SEEN_NUM,
-	SEEN_FLUX,
+    TOTAL_NUM,
+    TOTAL_FLUX,
+    SEEN_NUM,
+    SEEN_FLUX,
 };
 
 enum class LUMINOSITY_FUNCTION {
-	POWER_LAW,
-	LOG_NORMAL,
-	PLOEG,
-	NPTF,
-	POWER_LAW_ALPHA,
-	ERROR,
+    POWER_LAW,
+    LOG_NORMAL,
+    PLOEG,
+    NPTF,
+    POWER_LAW_ALPHA,
+    ERROR,
 };
 
 enum class METHOD {
-	COUNT,
-	HIST,
-	ERROR,
+    COUNT,
+    HIST,
+    ERROR,
 };
 
 LUMINOSITY_FUNCTION luminosityFunction = LUMINOSITY_FUNCTION::POWER_LAW;
 
 std::string sciNot(double value) {
-	int power = log10(value);
-	if (log10(value) < 0 && value != pow(10, power)) {
-		power--;
-	}
-	if (myAbs(power) > 6) {
-		return std::to_string(value / pow(10.0, power)) + "e" + std::to_string(power);
-	}
-	return std::to_string(value);
+    int power = log10(value);
[…]

### 2021-06-10 luminosity-models-position/graph-log-normal.py
Made graphs prettier

@@ -6,7 +6,7 @@ import numpy as np
 
 from matplotlib.lines import Line2D
 
-plt.style.use('latex')
+plt.style.use('revtex-presentation')
 
 
 PLOT_SIZE = 50
@@ -22,13 +22,13 @@ FRAC_ABOVE_THRESHOLD=1/5.0
 TOTAL_FLUX = 7.494712733226778e-10
 
 DRAW_EXTRA_CONTOURS = False
-LINE_COLOR = (0.8, 0.3, 0.1)
+LINE_COLOR = "C1"
 DRAW_PLOEG_POINT = True
 
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
 
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/log-normal/"
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/log-normal/"
 SHADE_SCALE=25
 
 def shade(field, threshold, xs, ys, off=False):
@@ -43,7 +43,7 @@ def shade(field, threshold, xs, ys, off=False):
                 fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
 
 # ========================== Load data ===========================
 
@@ -85,20 +85,20 @@ xVals = [L_0_RANGE[0] * lOPowerStep**i for i in range(PLOT_SIZE)]
 yVals = [SIGMA_L_RANGE[0] + (SIGMA_L_RANGE[1]-SIGMA_L_RANGE[0]) / PLOT_SIZE * j for j in range(PLOT_SIZE)]
 
 
-fig, ax = plt.subplots(figsize=(6, 4))
+fig, ax = plt.subplots()
 plt.xlim(left=L_0_RANGE[0], right=L_0_RANGE[1])
[…]

### 2021-06-10 luminosity-models-position/graph-power-law.py

@@ -11,7 +11,7 @@ from math import log
 import numpy as np
 from matplotlib.lines import Line2D
 
-plt.style.use('latex')
+plt.style.use('revtex-presentation')
 
 
 PLOT_SIZE = 50
@@ -31,8 +31,8 @@ FRAC_ABOVE_THRESHOLD=0.2
 TOTAL_FLUX = 7.494712733226778e-10
 
 DRAW_EXTRA_CONTOURS = False
-LINE_COLOR = (0.8, 0.3, 0.1)
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/power-law/"
+LINE_COLOR ="C0"
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/power-law/"
 SHADE_SCALE=25
 
 def shade(field, threshold, xs, ys, off=False):
@@ -47,22 +47,8 @@ def shade(field, threshold, xs, ys, off=False):
                 fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
 SHADE_SCALE=25
-
-def shade(field, threshold, xs, ys, off=False):
-    px = []
-    py = []
-    for x in range(0 if off else 1, SHADE_SCALE, 1):
-        inx = int(float(x) / SHADE_SCALE * field.shape[1])
-        for y in range(0 if off else 1, SHADE_SCALE, 1):
-            iny = int(float(y) / SHADE_SCALE * field.shape[0])
-            if field[iny][inx] < threshold:
-                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
-                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
-                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
[…]

### 2021-06-10 paper/draft.tex
added paper

\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jcappub} % for details on the use of the package, please
                     % see the JCAP-author-manual

\usepackage[T1]{fontenc} % if needed

\title{\boldmath A title with some math: $x=1$}

%% %simple case: 2 authors, same institution
%% \author{A. Uthor}
%% \author{and A. Nother Author}
%% \affiliation{Institution,\\Address, Country}

\author{Jack Dinsmore}
\author{and Tracy Slatyer}
\affiliation{Massachusetts Institute of Technology \\Cambridge, MA, USA}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{jtdinsmo@mit.edu}
\emailAdd{tslater@mit.edu}

\abstract{Abstract...}

\begin{document}
\maketitle
\flushbottom

\section{Some examples and best-practices}
\label{sec:intro}

Here follow some examples of common features that you may wanto to use
or build upon.

For internal references use label-refs: see section~\ref{sec:intro}.
Bibliographic citations can be done with cite: refs.~\cite{a,b,c}.
When possible, align equations on the equal sign. The package
\texttt{amsmath} is already loaded. See \eqref{eq:x}.
\begin{equation}
\label{eq:x}
\begin{split}
x &= 1 \,,
\qquad
y = 2 \,,
\\
z &= 3 \,.
\end{split}
\end{equation}
Also, watch out for the punctuation at the end of the equations.

If you want some equations without the tag (number), please use the available
starred-environments. For example:
\begin{equation*}
x = 1
\end{equation*}

The amsmath package has many features. For example, you can use use
\texttt{subequations} environment:
\begin{subequations}\label{eq:y}
\begin{align}
\label{eq:y:1}
a & = 1
\\
\label{eq:y:2}
b & = 2
\end{align}
and it will continue to operate across the text also.
\begin{equation}
\label{eq:y:3}
c = 3
\end{equation}
\end{subequations}
The references will work as you'd expect: \eqref{eq:y:1},
\eqref{eq:y:2} and \eqref{eq:y:3} are all part of \eqref{eq:y}.

A similar solution is available for figures via the \texttt{subfigure}
package (not loaded by default and not shown here).
All figures and tables should be referenced in the text and should be
placed at the top of the page where they are first cited or in
subsequent pages. Positioning them in the source file
after the paragraph where you first reference them usually yield good
results. See figure~\ref{fig:i} and table~\ref{tab:i}.

\begin{table}[tbp]
\centering
\begin{tabular}{|lr|c|}
\hline
x&y&x and y\\
\hline
a & b & a and b\\
1 & 2 & 1 and 2\\
$\alpha$ & $\beta$ & $\alpha$ and $\beta$\\
\hline
\end{tabular}
\caption{\label{tab:i} We prefer to have borders around the tables.}
\end{table}

We discourage the use of inline figures (wrapfigure), as they may be
difficult to position if the page layout changes.

We suggest not to abbreviate: ``section'', ``appendix'', ``figure''
and ``table'', but ``eq.'' and ``ref.'' are welcome. Also, please do
not use \texttt{\textbackslash emph} or \texttt{\textbackslash it} for
latin abbreviaitons: i.e., et al., e.g., vs., etc.

\section{Sections}
\subsection{And subsequent}
\subsubsection{Sub-sections}
\paragraph{Up to paragraphs.} We find that having more levels usually
reduces the clarity of the article. Also, we strongly discourage the
use of non-numbered sections (e.g.~\texttt{\textbackslash
  subsubsection*}).  Please also see the use of
``\texttt{\textbackslash texorpdfstring\{\}\{\}}'' to avoid warnings
from the hyperref package when you have math in the section titles

\appendix
\section{Some title}
Please always give a title also for appendices.

\acknowledgments

This is the most common positions for acknowledgments. A macro is
available to maintain the same layout and spelling of the heading.

\paragraph{Note added.} This is also a good position for notes added
after the paper has been written.

% The bibliography will probably be heavily edited during typesetting.
% We'll parse it and, using the arxiv number or the journal data, will
% query inspire, trying to verify the data (this will probalby spot
% eventual typos) and retrive the document DOI and eventual errata.
% We however suggest to always provide author, title and journal data:
% in short all the informations that clearly identify a document.

\bibliographystyle{plain}
\bibliography{gce.bib}

\end{document}

### 2021-06-10 summaries/jan-2021/jan-2021.tex
Added .tex files

\documentclass{C://Aliases//Dropbox-MIT//Latex_Templates//personal}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{epstopdf}

\usepackage[backend=biber, style=numeric, sorting=none]{biblatex}
\def\bibfont{\normalsize}

\addbibresource{jan-21-bib.bib}

\author{Jack Dinsmore}
\title{GCE UROP Summary}

\begin{document}
\maketitle

\begin{abstract}
We examine a millisecond pulsar model for the Galactic center excess and extract predictions for the total number of pulsars in the Galactic center, the number that can be resolved by \textit{Fermi} Gamma-Ray Space Telescope, and the fraction of resolvable luminosity for four luminosity functions found in the literature. We compare the latter two extracted values to observations. We perform the analysis for two models of the telescope's sensitivity: a step function probability of detection, and a more detailed, position-dependent model. Results depend strongly on the sensitivity model used, but no luminosity functions analyzed differed from the observables by more than a factor of ten.
\end{abstract}

\section{Introduction}
The Galactic Center GeV Excess (GCE) is an unexpected source of gamma radiation originating from with 20 degrees of the Galactic center, detected recently by the \textit{Fermi} Gamma-ray Space Telescope (\textit{Fermi}) \cite{Goodenough:2009gk, Eckner:2017oul}. Its origin is debated; the GCE holds potential to be the first evidence observed for dark matter annihilation \cite{Abazajian:2012pn,}, yet several studies have also shown that point sources such as millisecond pulsars (MSPs) may be responsible for the excess \cite{Wang:2005, Yuan:2014yda}.

The spacial distribution of the GCE has been found to match the square of a  Navarro-Frenk-White (NFW) profile with density $\rho_{\text{NFW}} = \parens{r / r_s}^{\gamma-1}\parens{1 + r/r_s}^{-3+\gamma}$, where $r_s \approx \SI{20}{\kilo\parsec}$ and $\gamma \approx 1.2$ \cite{Goodenough:2009gk, Zhong:2019ycb}.

Previous work has interpreted this MSP model. Ref. \cite{Zhong:2019ycb} has proposed an exponentially damped power-law luminosity function
\begin{equation}
    \frac{dN}{dL} = L^{-\alpha} \expp{-\frac{L}{L_\text{max}}}\brackets{\Gamma\parens{1-\alpha, \frac{L_\text{min}}{L_\text{max}}}L_\text{max}^{1-\alpha}}^{-1},
    \label{eqn:power-law}
\end{equation}
restricting the range of luminosities to $[L_\text{min}, \infty)$, where $L_\text{min}$, $L_\text{max}$, and $\alpha$ are free parameters. This reference found that $(\SI{1e29}{\erg\per\second}, \SI{1e35}{\erg\per\second}, 1.94)$ is required reproduced observations. It assumed a step-function model of \textit{Fermi}'s sensitivity, where all the MSPs with luminosity $L>L_{th}$ are observed and those with $L<L_\text{th}$ are not, where the threshold luminosity was fixed at $L_\text{th}=\SI{e34}{\erg\per\second}$. They find that this model admits three million MSPs in the GCE, which differs from estimates based on the physical properties of observed MSPs that estimate the number of MSPs at the Galactic center at the order of 40,000 \cite{citation needed}.

Ref. \cite{osti_1305131} proposes a luminosity function of 
\begin{equation}
    \frac{dN}{dL} = \frac{\log_{10} e}{\sigma \sqrt{2\pi} L}\expp{-\frac{\parens{\log_{10} L - \log_{10} L_0}^2}{2\sigma^2}},
    \label{eqn:log-normal}
\end{equation}
where $L_0$ and $\sigma$ are free parameters. It fits this model to data from globular cluster data, yielding values $L_0 = \SI{8.8e33}{\erg\per\second}$ and $\sigma=0.62$. It predicts thousands of MSPs to occupy the GCE if the entire excess is to be explained by MSPs.

Ref. \cite{Ploeg:2020jeh} proposes several more intricate luminosity functions, derived from a model of the pulsars themselves. They find that the same model may be used for resolved, gobular cluster MSPs in the Galactic disk and unresolved MSPs at the Galactic center. We use their luminosity function generated for the galactic disk. It closely resembles a log-normal luminosity function as in equation \ref{eqn:log-normal}, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$.

Finally, ref. \cite{Lee:2015fea} proposes a broken-power-law luminosity function of 
\begin{equation}
    \frac{dN}{dL} = \parens{\frac{\parens{1-n_1}\parens{1-n_2}}{L_b \parens{n_1 - n_2}}}\begin{cases}
        \parens{\fraci{L}{L_\text{b}}}^{-n_{1}} & L < L_{b} \\
        \parens{\fraci{L}{L_\text{b}}}^{-n_{2}} & L > L_b
    \end{cases}
    \label{eqn:nptf}
\end{equation}
where the free parameters  $n_1$, $n_2$, and $L_b$ were found via a Non-Poissonian Template Fitting model (NPTF) to be $(18.2, -0.66, \SI{8.66e+33}{\erg\per\second})$ for an NFW-squared-distributed population of MSPs named NFW PS. The paper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.34e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced. We set $L_\text{min}=\SI{1e29}{\erg\per\second}$, which is the same minimum pulsar luminosity used by ref. \cite{Zhong:2019ycb}. TThe turnover luminosity $L_\text{b}$ was given as a photon flux value in units of photons per centimeter squared per second; the process used to convert from photon flux to luminosity is detailed in the methods section.

All the above-mentioned luminosity functions are shown in figure \ref{fig:lum-funcs}.

\begin{figure}
    \centering
    \begin{subfigure}{.48\textwidth}
        \includegraphics[width=\linewidth]{figs/superimposed.png}
        \caption{Luminosity functions as in the integral for expected number of MSPs.}
    \end{subfigure}
    \hfill
    \begin{subfigure}{.48\textwidth}
        \includegraphics[width=\linewidth]{figs/superimposed-times-l.png}
        \caption{Luminosity functions, multiplied by L as in the integral for expected flux.}
    \end{subfigure}
    \caption{Luminosity functions considered in this summary. The black line indicates the threshold sensitivity used by ref. \cite{Zhong:2019ycb}.}
    \label{fig:lum-funcs}
\end{figure}

This UROP seeks to better understand the MSP model for the GCE by extracting the total number of MSPs in the GCE ($N$), the number resolvable with \textit{Fermi} ($N_\text{r}$), and the fraction of GCE luminosity emitted by resolved point sources ($R_\text{r}$). Observed values are $N_\text{r} \leq 47$ and $R_r \leq 0.2$ \cite{Zhong:2019ycb}.

For the purposes of this summary, we will take the GCE spectrum to be between $0.1$ and $100$ GeV, as in \cite{osti_1305131}. We take the total luminosity to be $L_\text{GCE}=\SI{6.756e+36}{\erg\per\second}$, which was obtained from ref. \cite{Zhong:2019ycb}'s value of $L_\text{GCE}=\SI{6.37e36}{\erg \per\second}$ for a range of 0.275 to 51.9 GeV, and extrapolating it using the power-law fit to the spectrum of the GCE produced in ref. \cite{Calore:2014xka}.

\section{Methods}
We will use two models for \textit{Fermi}'s sensitivity to generate predictions of $N$, $N_\text{r}$, and $R_\text{r}$ for each luminosity model. The first is a step-function model like those used in \cite{Zhong:2019ycb, osti_1305131}, and the second is a more detailed, position-dependent model. For clarity, the region of interest of $2^\circ < |b| < 20^\circ$ and $|\ell| < 20^\circ$ will be denoted as $\mathcal{R}$.

For the first, step-function model, we assumed that all pulsars with luminosity $L < L_\text{th}$ were unresolvable, and all with $L>L_\text{th}$ were resolved, with threshold luminosity $L_\text{th} = \SI{e34}{\erg\per\second}$ as used in ref. \cite{Zhong:2019ycb}. A slightly higher value of $L_\text{th}$ may be more accurate, as shown by the flux distribution of resolved point sources obtained from the 4FGL data release \cite{Fermi-LAT:2019yla, Ballet:2020hze}. See fig. \ref{fig:observed-distros}. The expected luminosity they predict is
\begin{equation}
    L = N\int_{L_\text{min}}^{L_\text{max}} L P(L) dL.
\end{equation}
Here, the total number of pulsars in the GCE $N$ is set by requiring that $L = L_\text{GCE}$, where $L_\text{GCE} = \SI{6.756e36}{\erg\per\second}$ is the luminosity of the entire excess. The observed number of pulsars and their expected luminosity in this model are
\begin{equation}
    N_\text{r} = N\int_{L_\text{th}}^{L_\text{max}} P(L) dL
\end{equation}
\begin{equation}
    L_\text{r} = N \int_{L_\text{th}}^{L_\text{max}} L P(L) dL.
\end{equation}

\begin{figure}
    \centering
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{figs/flux-histo.png}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{figs/luminosity-histo.png}
    \end{subfigure}
    \caption{\textit{Left}: Distribution of fluxes observed per resolved point source in the 4FGL catalog. \textit{Right}: Flux shown in \textit{Left} converted to luminosity, assuming that all the point sources are located at the galactic center at $r_\text{c} = \SI{8.5}{\kilo\parsec}$. The black line is the $L_\text{th}=\SI{1e34}{\erg\per\second}$ sensitivity threshold used in ref. \cite{Zhong:2019ycb}.}
    \label{fig:observed-distros}
\end{figure}

For the second, position-dependent sensitivity model, we obtained a map of position-dependent thresholds given as flux values from the same source \cite{Fermi-LAT:2019yla, Ballet:2020hze} (see figure \ref{fig:flux-thresholds}) and assumed that the MSPs are distributed according to the square of an NFW profile. Using an arbitrary normalized luminosity function $P(L)$, the total number of pulsars in the GCE is given by 
\begin{equation}
    N = \iint_{\mathcal{R}}\cos b dbd\ell \int_0^\infty s^2 ds A \rho_\text{NFW}^2 (r).
    \label{eqn:n}
\end{equation}
where the third integral is taken along the line of sight, with $r^2 = r_\text{c}^2 + s^2 - 2r_\text{c} s \cos b \cos \ell$, where $r_\text{c} = \SI{8.5}{\kilo\parsec}$ is the distance to the galactic center. Here, $A$ is the constant of proportionality of $\rho_{NFW}^2$, which is fixed by setting the total flux of the GCE
\begin{equation}
    F = \iint_{\mathcal{R}}\cos b dbd\ell \int_0^\infty s^2 ds A \rho_{NFW}^2 (r) \frac{1}{4\pi s^2}\int_{L_{min}}^{L_{max}}LP(L)dL.
    \label{eqn:f}
\end{equation}
equal to the observed value $F_\text{GCE}$. Then the number of resolved MSPs and resolved flux can be calculated respectively as 
\begin{equation}
    N_r = \iint_{\mathcal{R}}\cos b dbd\ell \int_0^\infty s^2 ds A \rho_\text{NFW}^2 (r) \int_{L_\text{th}(b, \ell)}^{L_\text{max}}P(L)dL.
    \label{eqn:nr}
\end{equation}
\begin{equation}
    F_r = \iint_{\mathcal{R}}\cos b dbd\ell \int_0^\infty s^2 ds A \rho_\text{NFW}^2 (r) \frac{1}{4\pi s^2}\int_{L_\text{th}(b, \ell)}^{L_\text{max}}LP(L)dL.
    \label{eqn:fr}
\end{equation}
with the ratio of resolved flux to total flux being $R_\text{r} = F_\text{r}/F$. Note that $L_\text{th}$ in the above equations was given by $L_\text{th}(b, \ell) = 4\pi s^2 F_\text{th}(b, \ell)$, where $F_\text{th}(b, \ell)$ was given in the sensitivity map (figure \ref{fig:flux-thresholds}).

\begin{figure}
    \centering
    \includegraphics[width=.6\linewidth]{figs/flux-thresholds.png}
    \caption{Position-dependent flux values per point source necessary in order to resolve the point source. A GCE location of $2^\circ < |b| < 20^\circ$, $|\ell| < 20^\circ$ is shown.}
    \label{fig:flux-thresholds}
\end{figure}

We calculated the observed flux of the GCE $F_\text{GCE}$ from the observed luminosity $L_\text{GCE}$ by assuming an NFW-distributed population of $N$ MSPs, all with the same luminosity $L = L_\text{GCE} / N$, yielding a flux of 
\begin{equation}
    F_\text{GCE} = \frac{L_\text{GCE}}{4\pi}\brackets{\iint_{\mathcal{R}}\cos b db d\ell \int_0^\infty ds \rho_\text{NFW}^2 (r)}\brackets{\iint_{\mathcal{R}}\cos b db d\ell \int_0^\infty s^2 ds \rho_\text{NFW}^2 (r)}^{-1}
    \label{eqn:l-to-f}
\end{equation}
via equations \ref{eqn:n} and \ref{eqn:f}. The calculated value was $F_\text{GCE}=\SI{7.631e-10}{\erg\per\centi\meter\squared\per\second}$, which differs from the naive value of $F_\text{GCE} = L_\text{GCE} / (4\pi r_c^2)$ by 4.2\%.

The step function sensitivity model can be conveniently thought of as a simplified version of the position-dependent model, where $L_\text{th}(b, \ell)$ has been set to a constant value of $L_\text{th}$ throughout the region of interest, and the division by $4\pi s^2$ of equations \ref{eqn:f} and \ref{eqn:fr} has been approximated by the constant value of $4\pi r_\text{c}^2$.
%%%%%%%%%%%% ADDRESS THE COMMENT

The luminosity function given in ref. \cite{Lee:2015fea} gave the turnover luminosity $L_b$ as a flux value of $F_{\gamma, \text{b}}$ in units of photons per centimeter squared per second, which we convert to an energy flux value by $F_\text{b} = E_\gamma F_{\gamma, \text{b}}$ with an average energy per photon of
\begin{equation}
    E_\gamma = \brackets{\int_{\SI{1.893}{\giga\electronvolt}}^{\SI{11.943}{\giga\electronvolt}} \frac{dN_\gamma}{dE} E dE} \brackets{\int_{\SI{1.893}{\giga\electronvolt}}^{\SI{11.943}{\giga\electronvolt}} \frac{dN_\gamma}{dE} E dE }^{-1},
    \label{eqn:photon-energy}
\end{equation}
where $\fraci{dN_\gamma}{dE} = A E^{-\alpha} \expp{-E / E_\text{cut}}$ is the photon spectrum of the GCE given by ref. \cite{Calore:2014xka}, with $\alpha \approx 2.25$ and $E_\text{cut} = \SI{2.25}{\giga\electronvolt}$. The range of integration of equation \ref{eqn:photon-energy} was set by the GCE spectrum range used in  ref. \cite{Lee:2015fea}. The proportionality constant is fixed by assertion that the (known) total observed flux of the GCE in the $0.1-100$ GeV is $F_\text{GCE} = \int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} \parens{\fraci{dN_\gamma}{dE}}E dE$. The turnover luminosity was then calculated using the flux-luminosity ratio given in equation \ref{eqn:l-to-f}.

\section{Results}
For each of the luminosity functions described above, we calculated $N$, $N_r$, and $R_r = F_r / F$ using both the step-function sensitivity model and the position-dependent model. Results are displayed in table \ref{tab:point-results}.

Since the power-law and log-normal luminosity function models form a two-dimensional space of functions, parameterized by $(L_\text{min}, L_\text{max})$ and $(L_0, \sigma)$ respectively (we keep $\alpha =1.94$ for the power-law), we may display the predicted number of pulsars for all configurations, and superimpose the two observational constraints: $N_\text{r} = 47$ and $R_\text{r} = 0.2$. This is done using the step-function sensitivity model and the position-dependent sensitivity model in figure \ref{fig:contours}.

For the position-dependent sensitivity, we can easily simulate the power of a more advanced, next-generation gamma ray telescope by dividing the sensitivity per pixel provided by refs \cite{Fermi-LAT:2019yla, Ballet:2020hze} by some position-independent constant. This was done for a 2-, 5-, and 10-times improvement in sensitivity for both the power-law and the log-normal luminosity functions, and is shown in figure \ref{fig:sensitivity-increase}.

\begin{figure}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=.48\linewidth]{figs/power-law/power-law-step.png}
        \hfill
        \includegraphics[width=.48\linewidth]{figs/power-law/power-law-pos-x1.png}
        \caption{Power law luminosity functions. The purple point is the configuration identified in ref. \cite{Zhong:2019ycb}: $L_\text{min}=\SI{1e29}{\erg\per\second}$, $L_\text{max} = \SI{1e35}{\erg\per\second}$.}
        \label{fig:power-law-contours-step}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=.48\linewidth]{figs/log-normal/log-normal-step.png}
        \hfill
        \includegraphics[width=.48\linewidth]{figs/log-normal/log-normal-pos-x1.png}
        \caption{Log normal luminosity functions. The blue point is the configuration identified in ref. \cite{osti_1305131}: $L_0=\SI{8.8e33}{\erg\per\second}$, $\sigma=0.62$, and the green point is a fit to the luminosity function found in ref. \cite{Ploeg:2020jeh}: $L_0=\SI{1.61e32}{\erg\per\second}$, $\sigma=0.700$.}
    \end{subfigure}
    \caption{Predicted number of MSPs $N$ plotted for different configurations of luminosity functions, with the $N_\text{r}=47$ constraint and the $R_\text{r}=0.2$ constraint  superimposed. \textit{Left}: The step-function sensitivity model was used, with $L_\text{th} = \SI{e34}{\erg\per\second}$. \textit{Right}: The position-depeondent sensitivity model was used. The \texttt{-} shading represents configurations that satisfy the number constraint $N_\text{r} < 47$, while the \texttt{|} shading represents those with $R_r < 0.2$. The \texttt{+} shading represents both.}
    \label{fig:contours}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[t]{.45\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{figs/power-law/power-law-pos-x1.png}
        \includegraphics[width=.99\linewidth]{figs/power-law/power-law-pos-x2.png}
        \includegraphics[width=.99\linewidth]{figs/power-law/power-law-pos-x5.png}
        \includegraphics[width=.99\linewidth]{figs/power-law/power-law-pos-x10.png}
        \caption{Power law luminosity functions}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{.45\textwidth}
        \centering
        \includegraphics[width=.99\linewidth]{figs/log-normal/log-normal-pos-x1.png}
        \includegraphics[width=.99\linewidth]{figs/log-normal/log-normal-pos-x2.png}
        \includegraphics[width=.99\linewidth]{figs/log-normal/log-normal-pos-x5.png}
        \includegraphics[width=.99\linewidth]{figs/log-normal/log-normal-pos-x10.png}
        \caption{Log normal luminosity functions}
    \end{subfigure}
    \caption{Predicted number of MSPs over the space of power-law and log-normal luminosity functions, and different sensitivities of the telescope, with current observational constraints superimposed.}
    \label{fig:sensitivity-increase}
\end{figure}

Using the position-dependent sensitivity model, the predicted number of pulsars is largely unchanged as expected, but the observational constraints differ greatly from the step-function sensitivity model.

\begin{table}
    \centering
    \begin{subtable}[h]{0.9\textwidth}
        \centering
        \begin{tabular}{|l|c|c|c|}
            \hline
            Luminosity function & $N$ & $N_r$ & $R_r$ \\ \hline
            Observations & - & 47 & 0.2 \\
            Ref. \cite{Zhong:2019ycb}: Power-law & $\num{3.54e6}$ & 50.0 & 0.193 \\
            Ref. \cite{osti_1305131}: Log-normal & 277 & 129 & 0.910 \\
            Ref. \cite{Ploeg:2020jeh}: Custom  & $\num{8.76e3}$ & 54.5 & 0.355 \\
            Ref. \cite{Ploeg:2020jeh}: Log-normal fit  & $\num{1.14e4}$ & 59.7 & 0.171 \\
            Ref. \cite{Lee:2015fea}: Broken power-law, NFW PS & $\num{1.23e3}$ & 4.41 & $\num{6.94e-3}$ \\
            Ref. \cite{Lee:2015fea}: Broken power-law, Disk PS & $\num{1.21e4}$ & 92.1 & 0.880 \\ \hline
        \end{tabular}
        \caption{Results for a step-function sensitivity model with $L_{th} = \SI{e34}{\erg\per\second}$}
        \label{tab:step}
    \end{subtable}

    \vspace{1em}

    \begin{subtable}[h]{0.9\textwidth}
        \centering
        \begin{tabular}{|l|c|c|c|}
            \hline
            Luminosity function & $N$ & $N_\text{r}$ & $R_\text{r}$ \\ \hline
            Observations & - & 47 & 0.2 \\
            Ref. \cite{Zhong:2019ycb}: Power-law & $\num{3.42e6}$ & 10.2 & 0.101 \\
            Ref. \cite{osti_1305131}: Log-normal & 268 & 44.8 & 0.692 \\
            Ref. \cite{Ploeg:2020jeh}: Custom  & $\num{8.48e3}$ & 9.66 & 0.266 \\
            Ref. \cite{Ploeg:2020jeh}: Log-normal fit  & $\num{1.11e4}$ & 7.76 & 0.0648 \\
            Ref. \cite{Lee:2015fea}: Broken power-law, NFW PS & $\num{1.19e3}$ & 4.06 & 0.0283 \\
            Ref. \cite{Lee:2015fea}: Broken power-law, Disk PS & $\num{1.17e4}$ & 42.1 & 0.751 \\ \hline
        \end{tabular}
        \caption{Results for a position-dependent sensitivity function}
        \label{tab:position}
    \end{subtable}
    \caption{Predictions for $N$, the total number of MSPs required to make up the GCE; $N_\text{r}$, the number of resolvable MSPs; and $R_\text{r}$, the fraction of luminosity that comes from resolved sources. The luminosity functions used are those proposed by the various references cited. For the final luminosity function, a cutoff value of $L_\text{min}=\SI{1e29}{\erg\per\second}$ was used so that the function would be normalizable. The observed values are discussed in ref. \cite{Zhong:2019ycb}.}
    \label{tab:point-results}
\end{table}
\begin{table}
    \centering
    \begin{subtable}[h]{0.9\textwidth}
        \centering
        \begin{tabular}{|l|c|c|c|c|}
            \hline
            Luminosity function & $\times 1$ & $\times 2$ & $\times 5$ & $\times 10$ \\ \hline
            Ref. \cite{Zhong:2019ycb}: Power-law & 10.2 & 26.5 & 79.1 & 167 \\
            Ref. \cite{osti_1305131}: Log-normal & 44.8 & 82.1 & 145 & 191 \\
            Ref. \cite{Ploeg:2020jeh}: Custom  & 9.66 & 26.1 & 110 & 281 \\
            Ref. \cite{Ploeg:2020jeh}: Log-normal fit  & 7.76 & 28.3 & 128 & 343 \\
            Ref. \cite{Lee:2015fea}: Broken power-law, NFW PS & 4.06 & 27.1 & 318 & 819 \\
            Ref. \cite{Lee:2015fea}: Broken power-law, Disk PS & 42.1 & 64.7 & 106 & 149 \\ \hline
        \end{tabular}
        \caption{$N_r$ values for different sensitivities.}
    \end{subtable}

    \vspace{1em}

    \begin{subtable}[h]{0.9\textwidth}
        \centering
        \begin{tabular}{|l|c|c|c|c|}
            \hline
            Luminosity function & $\times 1$ & $\times 2$ & $\times 5$ & $\times 10$ \\ \hline
            Ref. \cite{Zhong:2019ycb}: Power-law & 0.101 & 0.157 & 0.237 & 0.298 \\
            Ref. \cite{osti_1305131}: Log-normal & 0.692 & 0.831 & 0.941 & 0.979 \\
            Ref. \cite{Ploeg:2020jeh}: Custom  & 0.266 & 0.315 & 0.435 & 0.552 \\
            Ref. \cite{Ploeg:2020jeh}: Log-normal fit  & 0.0648 & 0.129 & 0.270 & 0.416 \\
            Ref. \cite{Lee:2015fea}: Broken power-law, NFW PS & 0.0283 & 0.0853 & 0.451 & 0.867 \\
            Ref. \cite{Lee:2015fea}: Broken power-law, Disk PS & 0.751 & 0.835 & 0.905 & 0.937 \\ \hline
        \end{tabular}
        \caption{$R_\text{r}$ values for different sensitivities.}
     \end{subtable}
     \caption{Predictions for $N_\text{r}$ and $R_\text{r}$ simulated for a 2-, 5-, and 10-times global increase in telescope sensitivity.}
\end{table}

\section{Conclusion}
An excess of gamma rays in the galactic center suggests an undiscovered population of millisecond pulsars. Several luminosity functions found in the literature were examined for the number of MSPs they predict to inhabit the galactic center; the result depends strongly on the type of luminosity function used. Luminosity functions fit to globular clusters, not GCE data, tend not to reproduce observational values of the number of resolved pulsars and the fraction of GCE luminosity emitted from them.

A more detailed sensitivity model was applied to these luminosity functions, and the result was found to drastically alter the predicted number of resolvable pulsars and the fraction of luminosity emitted from them.

Potential future steps include to predict the observables attainable assuming a higher sensitivity, to simulate a next generation gamma ray telescope, or extending the analysis to search for complementary radio wave signals from MSPs.

\printbibliography

\end{document}

### 2021-06-10 summaries/numerical-integration/numerical-integration.tex
Added .tex files

\documentclass{C://Aliases//Dropbox-MIT//Latex_Templates//personal}

\author{Jack Dinsmore}
\title{Writeup of numerical integration algorithm}

\begin{document}
\maketitle

\begin{abstract}
In this project, a luminosity function was extracted from the image of a plot in another paper. This extracted luminosity function, consisting of a finite set of points, then had to be integrated. The methods for doing so accurately are found below.
\end{abstract}

\section{Introduction}
A luminosity function was extracted from a plot in Ploeg et al.\cite{ploeg} See the Jan-2021 summary for the analysis of this luminosity function. The extracted function is shown in figure \ref{fig:func}. The task is to compute the following two integrals:
\begin{equation}
    \int_{L_{min}}^\infty \frac{dN}{dL}dL \indent \indent \int_{L_{min}}^\infty L\frac{dN}{dL}dL
    \label{eqn:ints}
\end{equation}
which are known as the number integral and luminosity integral respectively. Here, $L_{min}$ is some arbitrary value, which in practice was either a value near the peak of the luminosity function, $L_{min} = L_{th}$ (see figure \ref{fig:func}) or $L_{min} = 0$.

The methods for performing these integrals are given below, followed by a comparison between the values attained by the numerical method, and those attained by analytically integrating over the log normal fit.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{get-estimates.png}
    \caption{Luminosity function to be integrated over. The blue plot is the extracted function, while the orange is a log-normal fit to it. The black line is the threshold luminosity $L_{th}$, sometimes used as an integration bound.}
    \label{fig:func}
\end{figure}

\section{Methods}
Methods employed for both integrals approximate the luminosity function as piecewise-linear, that is:
\begin{equation}
\frac{dN}{dL}(x) \approx \begin{cases}
    \frac{y_2 - y_1}{x_2 - x_1}(x - x_1) + y_1 & x_1 \leq x < x_2 \\
    \frac{y_3 - y_2}{x_3 - x_2}(x - x_2) + y_2 & x_2 \leq x < x_3 \\
    \vdots & \vdots \\
    \frac{y_N - y_{N-1}}{x_N - x_{N-1}}(x - x_{N-1}) + y_{N-1} & x_{N-1} \leq x \leq x_{N} \\
    \label{eqn:approx}
\end{cases}
\end{equation}
where $x_1,\dots, x_N$ and $y_1,\dots, y_N$ are the points extracted from the luminosity function found in the literature, structured so that $x_1 < x_2 < \dots < x_N$ and $y_i = \frac{dN}{dL}(x_i)$.

The bounds of the integral are then restricted to the domain $[x_1, x_N]$. For example, the integral over $[0, \infty)$ becomes an integral over $[x_1, x_N]$.

\subsection{Number integral}
We will compute the first integral given in equation \ref{eqn:ints} by integrating the components of equation \ref{eqn:approx}. The result is
\begin{equation*}
    \int_{L_{min}}^\infty \frac{dN}{dL}dL = \int_{L_{min}}^{x_{n}}\frac{y_{min} - y_n}{L_{min} - x_n}\parens{x - L_{min}} + y_{n-1} dx + \sum_{i = n}^{N-1}\int_{x_i}^{x_{i+1}}\frac{y_{i+1} - y_i}{x_{i+1} - x_i}\parens{x - x_i} + y_i dx
\end{equation*}
where we have chosen $n$ such that $x_{n-1} \leq L_{min} < x_n$, and set $y_{min} = \frac{y_{n} - y_{n-1}}{x_{n} - x_{n-1}}\parens{L_{min} - x_{n-1}} + y_{n-1}$. Performing the integral, we get
\begin{equation}
    \int_{L_{min}}^\infty \frac{dN}{dL}dL = \frac{1}{2} \parens{x_n - L_{min}}\parens{y_n + y_{min}} + \sum_{i=n}^{N-1}\frac{1}{2} \parens{x_{i+1} - x_i}\parens{y_{i+1} + y_{i}}
\end{equation}
which is equivalent to trapezoidal integration. This series can be simplified, but we will not do so.

\subsection{Luminosity integral}
The same process can be applied to integrate the second integral given in equation \ref{eqn:ints}. We will compute
\begin{equation*}
    \int_{L_{min}}^\infty \frac{dN}{dL}dL = \int_{L_{min}}^{x_{n}}\frac{y_{min} - y_n}{L_{min} - x_n}\parens{x^2 - xL_{min}} + xy_{n-1} dx + \sum_{i = n}^{N-1}\int_{x_i}^{x_{i+1}}\frac{y_{i+1} - y_i}{x_{i+1} - x_i}\parens{x^2 - xx_i} + xy_i dx.
\end{equation*}
The result is
\begin{align}\begin{split}
    \int_{L_{min}}^\infty \frac{dN}{dL}dL & = \frac{1}{6}\parens{x_n - L_{min}}\brackets{y_{min}\parens{2 L_{min} + x_n} + y_n\parens{L_{min} + 2x_n}}\\ 
    &+ \frac{1}{6}\sum_{i=n}^{N-1}\parens{x_{i+1} - x_{i}}\brackets{y_{i}\parens{2 x_{i} + x_{i+1}} + y_{i+1}\parens{x_{i} + 2x_{i+1}}}.
\end{split}\end{align}

\section{Results}
We may compare the accuracy of this numerical method by fitting a log-normal distribution to the luminosity function and comparing the analytical and numerical results of the integrals in equation \ref{eqn:ints}. The log normal distribution used is 
\begin{equation}
    \frac{dN}{dL} = \frac{\log_{10} e}{\sigma \sqrt{2\pi} L}\expp{-\frac{\parens{\log_{10} L - \log_{10} L_0}^2}{2\sigma^2}},
    \label{eqn:log-normal}
\end{equation}
and the fit achieved values of $L_0 = \SI{1.6084e+32}{\erg\per\second}$ and $\sigma=0.7003$. The integrals were computed analytically, and the function was sampled with $N$ points in $[\SI{e29}{\erg\per\second}, \SI{e35}{\erg\per\second}]$ spaced evenly in log space. The percent deviation of the numerical integrals from the analytical integrals is shown in figure \ref{fig:compare-integral}. The percent deviations as calculated for four points commonly used in the jan-2021 summary of this UROP are shown in table \ref{tab:calc-points}.

\begin{figure}[h]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=0.99\linewidth]{num-integral-deviation.png}
        \caption{Number integral}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=0.99\linewidth]{lum-integral-deviation.png}
        \caption{Luminosity integral}
    \end{subfigure}
    \caption{Percent deviation between the numerical integral, calculated by sampling $N$ points, equally-spaced in log space, from a log normal distribution and using the described methods to integrate over the range from $L_{min}$ to the edge of the domain, which was $\SI{e35}{\erg\per\second}$ here.}
    \label{fig:compare-integral}
\end{figure}

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        & Number integral & Luminosity integral \\ \hline
        $L_{min} = \SI{e29}{\erg\per\second}$ & 0.321\% & 0.0796\%\\ \hline
        $L_{min} = L_{th} = \SI{e34}{\erg\per\second}$ & 0.934\% & 3.65\% \\ \hline
    \end{tabular}
    \caption{Percent deviations between the numerical and analytical values of the integrals shown in equation \ref{eqn:ints}, for the log-normal fit to Ploeg et al.'s data.}
    \label{tab:calc-points}
\end{table}

\section{Conclusion}
We developed a method to numerically integrate a luminosity function and its expectation value, and affirmed that it was accurate to within four percent at relevant points.

The position-dependent sensitivity model cited in the jan-2021 summary may be more inaccurate than table \ref{tab:calc-points} suggests, because for pixels near the galactic plane, the threshold luminosity can rise to as much as five times the value of $L_{th}$ used here.

The luminosity function extracted from Ploeg et al. does not match the log-normal fit perfectly, particularly at high luminosities. The deviations present between the ``custom'' luminosity function and the log normal fit in the jan-2021 summary are most likely caused by this disagreement, not numerical error.

\begin{thebibliography}{99}
    \bibitem{ploeg} H. Ploeg, C. Gordon, R. Crocker, O. Macias. ``Comparing the Galactic Bulge and Galactic Disk Millisecond Pulsars.'' arXiv:2008.10821v2 (2020).

\end{thebibliography}

\end{document}

### 2021-06-10 summaries/oct-2020/oct-2020.tex
Added .tex files

@@
 
-For the purposes of this summary, we will take the luminosity of the GCE to be \SI{6.37}{\erg \per\second}, which is consistent with the luminosity used in ref. \cite{fermilab}.
+For the purposes of this summary, we will take the luminosity of the GCE to be \SI{6.37e36}{\erg \per\second}, which is consistent with the luminosity used in ref. \cite{fermilab}.
 
@@
 The \textit{Fermi} Space Telescope has observed two features which we explore in this summary.
-We model the sensitivity of the telescope as a step function, with the telescope detecting no pulsars of luminosity below $L_{t} = \SI{e34}{\erg\per\second}$ and all the pulsars above it.
 
@@
 Similarly, it is likely that the true value of this ratio is less than or equal to one quarter, which further limits the parameter space of luminosity functions.
+
+We model the sensitivity of the telescope as a step function, with the telescope detecting no pulsars of luminosity below $L_{t} = \SI{e34}{\erg\per\second}$ and all the pulsars above it.
+Future parts of this study will test the sensitivity of our results on the value of $L_t$ and try more realistic sensitivity functions, such as that given by equation 2.34 of ref.
+\cite{ploeg}.
 
@@
 Of these, the log-normal luminosity function is more physically relevant, but the power law is simpler.
-Both have been studied in detail by the papers cited, but the observations from \textit{Fermi} have not yet been applied to a log-normal luminosity function, so it is useful to compare the two in this light.
+Both have been studied in detail by refs \cite{fermilab, log-normal}, but the observations from \textit{Fermi} have not yet been applied to a log-normal luminosity function, so it is useful to compare the two in this light.
 
@@
 \begin{figure}[h]
-    \label{contour-overlay-power-law}
     \centering
-    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-overlay.png}
+    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/step-sensitivity/contour-overlay.png}
     \caption{Above is plotted the number of MSPs needed to reproduce the GCE under a power law luminosity with an exponential cutoff.
 In red is plotted the configurations required to match \textit{Fermi}'s observation of $R=1/4$, and in green their observation that $N_f = 47$.
-}
+The circle represents the values of $L_{max}$ and $L_{min}$ used in ref.
+\cite{fermilab}.}
+    \label{contour-overlay-power-law}
 \end{figure}
 
-The intersection point between these two families represents the only power law configuration that simultaneously realizes both of \textit{Fermi}'s observations, and it corresponds to $\si{3.3e6}$ MSPs in the GCE which is unrealistic.
+The intersection point between these two families represents the only power law configuration that simultaneously realizes both of \textit{Fermi}'s observations, and it corresponds to $\SI{3.3e6}{}$ MSPs in the GCE which is unrealistic.
 The region for $R < 1/4$ and $N_f < 47$, which is allowed by observation, appears beneath both curves.
@@
 \begin{figure}[h]
-    \label{contour-overlay-extra-power-law}
     \centering
-    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-overlay-extra.png}
+    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/step-sensitivity/contour-overlay-extra.png}
     \caption{Above is plotted the number of MSPs needed to reproduce the GCE under a power law luminosity with an exponential cutoff.
 In red curves are plotted different values of $R$, with yellow representing higher values, while different values of $N_f$ are plotted in green, with brighter green representing higher $N_f$.
-The Fermilab results $R=1/4$ and $N_f=47$ are bolded.}
+The \textit{Fermi} results $R=1/4$ and $N_f=47$ are bolded.
+The circle represents the values of $L_{max}$ and $L_{min}$ used in ref.
+\cite{fermilab}.}
+    \label{contour-overlay-extra-power-law}
 \end{figure}
@@
 \begin{figure}[h]
-    \label{contour-vary-alpha}
     \centering
-    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-vary-alpha-exp.png}
-    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/contour-vary-alpha-hard.png}
+    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/step-sensitivity/contour-vary-alpha-exp.png}
+    \includegraphics[width=0.6\textwidth]{../../luminosity-models/power-law/step-sensitivity/contour-vary-alpha-hard.png}
     \caption{Above is plotted the curves representing $R=1/4$ and $N_f=47$ for various $\alpha$ from 1.22 to 2.5.
@@
 An exponential cutoff is used in the top plot, and a hard cutoff for the bottom.}
+    \label{contour-vary-alpha}
 \end{figure}
@@
 \begin{figure}[h]
-    \label{contour-overlay-log-normal}
     \centering
@@
 On the top plot, the configurations required to match \textit{Fermi}'s observation of $R=1/4$ are shown in red, and in green their observation that $N_f = 47$.
-The plot is expanded for the lower plot to different values of $R$ and $N_f$, with higher $R$ and $N_f$ represented by brighter colors.}
+The plot is expanded for the lower plot to different values of $R$ and $N_f$, with higher $R$ and $N_f$ represented by brighter colors.
+The purple point represents the population configuration calculated by ref.
+\cite{log-normal} for globular clusters; the purple lines represent 1-$\sigma$ error bars around this point; and the black point is the configuration requiring the least pulsars within one standard deviation of the $\sigma$ calculated in ref.
+\cite{log-normal} while remaining within the observational constraints.}
+    \label{contour-overlay-log-normal}
 \end{figure}
@@
 \begin{thebibliography}{99}
-    \bibitem{fermilab}Y.
+    \bibitem{fermilab} Y.
 Zhong, S.
@@
 
-    \bibitem{log-normal}D. Hooper and T. Linden. ``The Gamma-Ray Pulsar Population of
-    Globular Clusters: Implications for the
-    GeV Excess.'' \textit{JCAP} (2016).
+    \bibitem{log-normal} D. Hooper and T. Linden. ``The Gamma-Ray Pulsar Population of
+    Globular Clusters: Implications for the GeV Excess.'' \textit{JCAP} (2016).
+
+    \bibitem{ploeg} H. Ploeg, C. Gordon, R. Crocker, O. Macias. ``Comparing the Galactic Bulge and Galactic Disk Millisecond Pulsars'' arXiv:2008.10821v2 (2020).
 

### 2021-06-11 flux-histograms/power-law-step/hist-generator.py
Added line to flux histogram indicating the step sensitivity model for fermilab

@@ -1,0 +1,54 @@
+from math import log, exp
+from scipy.special import gammainc, gamma
+import numpy as np
+
+ALPHA_L = 1.94
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47#6.756e36# 6.37e36  # All units are in ergs per second
+L_THRESH = 1.0e34
+L_MIN = 1e29
+L_MAX = 1e35
+MIN_FLUX = 1e-12
+MAX_FLUX = 1e-9
+
+FLUX_TO_LUM_RATIO = 1.1093417307914119e-46
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/5.0
+
+def fluxToLum(flux):
+    return flux / FLUX_TO_LUM_RATIO
+
+def lumToFlux(lum):
+    return lum * FLUX_TO_LUM_RATIO
+
+def Gamma(s, x):
+    if(s < 0):
+        return (Gamma(s+1, x) - x**s * exp(-x))/s
+    return gamma(s) * (1-gammainc(s, x))
+
+def getNumPulsars(lMin, lMax, lum):
+    lumExp = lMax**(2-ALPHA_L) * Gamma(2-ALPHA_L, lMin / lMax)
+    Aexp = L_EXCESS / lumExp
+
+    if lum > L_THRESH:
+        return Aexp * lum**-ALPHA_L * np.exp(-lum/L_MAX)
+    else:
+        return 0
+
+output = open("power-law-step.txt", 'w')
+binEdges = 10**np.linspace(start=np.log10(fluxToLum(MIN_FLUX)), stop=np.log10(fluxToLum(MAX_FLUX)), num=41)
+bins = [(binEdges[i+1] + binEdges[i])/2 for i in range(len(binEdges) - 1)]
+binWidths = [binEdges[i+1] - binEdges[i] for i in range(len(binEdges) - 1)]
+sumCounts = 0
+
+for lum in bins:
+    output.write(str(lumToFlux(lum)) + ", ")
+output.write('\n')
+for (i, lum) in enumerate(bins):
+    thisCount = getNumPulsars(L_MIN, L_MAX, lum) * binWidths[i]
+    sumCounts += thisCount
+    output.write(str(thisCount) + ', ')
+
+print(sumCounts)
+
+output.close()

### 2021-06-11 gautam/fit.py
Fitted new (gautam) luminosity function

@@ -1,0 +1,52 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import lmfit
+import scipy.optimize as optimization
+
+def get_data(filename):
+    xs = []
+    ys = []
+    f = open(filename, 'r')
+    for line in f.readlines():
+        if line == '':
+            continue
+        x, y = line.split(', ')
+        xs.append(float(x))
+        ys.append(float(y))
+    return np.asarray(xs), np.asarray(ys)
+
+def power_law(x, c, alpha, lmax):
+    return np.log10(c * (10**x)**(-alpha) * np.exp(-10**x / lmax))
+
+def log_normal(x, c, l0, sigma):
+    return np.log10(c/10**x * np.exp(-(x - np.log10(l0))**2 / (2 * sigma**2)))
+
+def fit_power_law(filename, color):
+    datax, datay = get_data(filename)
+    params = optimization.curve_fit(power_law, datax, datay, (1, 1, 1))[0]
+    fity = power_law(datax, params[0], params[1], params[2])
+    plt.plot(datax, fity, linestyle='dashed', c=color)
+    plt.plot(datax, datay, c=color)
+    return params[1], params[2]
+
+def fit_log_normal(filename, color):
+    datax, datay = get_data(filename)
+    params = optimization.curve_fit(log_normal, datax, datay, (1, 1, 1))[0]
+    fity = log_normal(datax, params[0], params[1], params[2])
+    plt.plot(datax, fity, linestyle='dotted', c=color)
+    plt.plot(datax, datay, c=color)
+    return params[1], params[2]
+
+plt.plot([], [], linestyle='dashed', c='black', label='power law fit')
+plt.plot([], [], linestyle='dotted', c='black', label="log normal fit")
+plt.legend()
+
+fit_power_law("blue.csv", color='C0')
+fit_power_law("orange.csv", color='C1')
+fit_log_normal("blue.csv", color='C0')
+fit_log_normal("orange.csv", color='C1')
+plt.xlabel("log10(F/(ergs/s/cm^2))")
+plt.ylabel("unknown")
+
+plt.savefig("fit results.png")
+plt.show()

### 2021-06-15 luminosity-models-smoothing/graph-log-normal.py
Switch to linux

@@ -1,0 +1,148 @@
+from matplotlib import pyplot as plt
+from math import log, exp, sqrt
+from scipy.special import erfc, erf
+import matplotlib.colors as colors
+import numpy as np
+
+from matplotlib.lines import Line2D
+
+plt.style.use('revtex-presentation')
+
+
+PLOT_SIZE = 50
+L_0_RANGE=[1.0e30, 2.0e36]#[1.0e32, 2.0e34]
+SIGMA_L_RANGE=[0.001, 1]
+
+MULTIPLIER = 1
+
+lOPowerStep = (L_0_RANGE[1] / L_0_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/5.0
+TOTAL_FLUX = 7.494712733226778e-10
+
+DRAW_EXTRA_CONTOURS = False
+LINE_COLOR = "C1"
+DRAW_PLOEG_POINT = True
+
+paperPoint = [0.88e34, 0.62]
+ploegPoint = [10**32.206, 0.70585]
+
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/log-normal/"
+SHADE_SCALE=25
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
+
+# ========================== Load data ===========================
+
+totalNum = []
+numSeen = []
+lumSeen = []
+
+f = open(PATH_TO_FILE + "total-num.txt")
+for line in f.read().split('\n')[:-1]:
[…]

### 2021-06-15 luminosity-models-smoothing/graph-power-law-alpha.py

@@ -1,0 +1,151 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+from scipy.special import gammainc, gamma
+import matplotlib.colors as colors
+from matplotlib.lines import Line2D
+import numpy as np
+
+plt.style.use('revtex')
+
+
+PLOT_SIZE = 50
+
+L_MIN = 1e29
+ALPHA_RANGE = [1.1, 2.5]
+L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+maxPowerStep = (L_MAX_RANGE[1] / L_MAX_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+MULTIPLIER = 1
+
+paperPoint = [1e35, 1e29]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=0.2
+TOTAL_FLUX = 7.494712733226778e-10
+
+DRAW_EXTRA_CONTOURS = False
+LINE_COLOR = (0.8, 0.3, 0.1)
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/power-law-alpha/"
+SHADE_SCALE=25
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
+SHADE_SCALE=25
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
[…]

### 2021-06-15 luminosity-models-smoothing/graph-power-law.py

@@ -1,0 +1,144 @@
+''' Things to check:
+    Is the NFW profile a number density?
+    What is r_s from the Fermilab paper?
+    I should integrate the square of the NFW profile, not square the integral, right?
+    Am I using the number position distribution and luminosity position distribution in the correct places?
+'''
+
+from matplotlib import pyplot as plt
+import matplotlib.colors as colors
+from math import log
+import numpy as np
+from matplotlib.lines import Line2D
+
+plt.style.use('revtex-presentation')
+
+
+PLOT_SIZE = 50
+
+ALPHA = 1.94
+L_MIN_RANGE = [1.0e28, 1.0e34]
+L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+minPowerStep = (L_MIN_RANGE[1] / L_MIN_RANGE[0]) ** (1.0 / PLOT_SIZE)
+maxPowerStep = (L_MAX_RANGE[1] / L_MAX_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+MULTIPLIER = 1
+
+paperPoint = [1e35, 1e29]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=0.2
+TOTAL_FLUX = 7.494712733226778e-10
+
+DRAW_EXTRA_CONTOURS = False
+LINE_COLOR ="C0"
+PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/power-law/"
+SHADE_SCALE=25
+
+def shade(field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
[…]

### 2021-06-15 luminosity-models-smoothing/overlay-calculator/overlay-calculator/overlay-calculator - Copy.cpp

@@ -1,0 +1,735 @@
+#include <iostream>
+#include <string>
+#include <vector>
+#include <assert.h>
+#include <fstream>
+#include <sstream>
+#include <thread>
+#include <future>
+#include <boost/math/special_functions/gamma.hpp>
+
+typedef std::pair<double, double> CoordPair;
+typedef std::pair<int, int> IndexPair;
+typedef std::vector<std::vector<double>> DoubleVector;
+
+//#define LOTS_OF_THREADS // Use on Erebus
+/* When LOTS_OF_THREADS is defined, a target of 80-90 threads are made and run concurrently.
+   Otherwise, four threads are made and run concurrently. */
+
+#define POWER_STEP 1.1 // 1 is the minimum
+#define pi 3.14159265358979323
+#define ONE_PLUS_EPSILON 1.0000000001
+#define max(a, b) (((a) > (b)) ? (a) : (b))
+
+#define ALPHA 1.94
+#define DIST_TO_CENTER 8.5 // kpc
+#define CM_PER_KPC_SQUARED 9.523396e+42
+#define FLUX_EXCESS 7.494712733226778e-10  // All flux units are in ergs per second per square centimeter
+#define ERGS_PER_PHOTON 0.00545625167499331 // Use the ergs per photon for the NPTF paper
+
+
+const double L_MIN_RANGE[2] = { 1.0e28, 1.0e34 };
+const double L_MAX_RANGE[2] = { 1.0e34, 1.0e36 };
+const double L0_RANGE[2] = { 1.0e32, 2.0e34 };
+const double SIGMA_RANGE[2] = { 0.001, 1 };
+
+const double fermilabPaperPoint[2] = { 1e35, 1e29 };
+const double logNormalPaperPoint[2] = { 0.88e34, 0.62 };
+const double logNormalPloegPoint[2] = { 1.6084e+32, 0.7003 };
+
+// Values for the computation of the integral of the NFW profile.
+#define GAMMA 1.2
+#define NFW_SCALE_DIST 20 // kpc
+#define INTEGRAL_HALF_WIDTH (DIST_TO_CENTER * 0.9)// / 2 // kpc
+#define NFW_INTEGRAL_STEPS 1000
+
+#define ROOT "C:/Users/goods/Dropbox (MIT)/GCE UROP/"
+#define SENSITIVITY_PATH (ROOT "sensitivity/sensitivity.txt")
[…]

### 2021-06-15 luminosity-models-smoothing/overlay-calculator/overlay-calculator/overlay-calculator.cpp

@@ -1,0 +1,1058 @@
+#include <iostream>
+#include <string>
+#include <vector>
+#include <assert.h>
+#include <fstream>
+#include <sstream>
+#include <thread>
+#include <future>
+#include <boost/math/special_functions/gamma.hpp>
+
+typedef std::pair<double, double> CoordPair;
+typedef std::pair<int, int> IndexPair;
+typedef std::vector<std::vector<double>> DoubleVector;
+
+//#define LOTS_OF_THREADS // Use on Erebus
+/* When LOTS_OF_THREADS is defined, a target of 80-90 threads are made and run concurrently.
+   Otherwise, four threads are made and run concurrently. */
+
+#define SENSITIVITY_DIVISOR 10.0
+
+#define pi 3.14159265358979323
+#define ONE_PLUS_EPSILON 1.0000000001
+#define max(a, b) (((a) > (b)) ? (a) : (b))
+
+#define ALPHA 1.94
+#define L_MIN 1.0e29
+#define DIST_TO_CENTER 8.5 // kpc
+#define CM_PER_KPC_SQUARED 9.523396e+42
+#define FLUX_EXCESS 1.2953417255755896e-09  // All flux units are in ergs per second per square centimeter
+
+#define FLUX_HIST_BINS 40
+#define FLUX_HIST_LOW 1.0731612e-12
+#define FLUX_HIST_HIGH 1.3719972e-09
+#define ALPHA_HIST 1.94
+#define L_MIN_HIST 1.0e29
+#define L_MAX_HIST 1.0e35
+#define L0_HIST 0.88e34
+#define SIGMA_HIST 0.62
+#define L0_PLOEG_HIST 1.6084e+32
+#define SIGMA_PLOEG_HIST 0.7003
+#define NPTF_L_BREAK_HIST 8.656487610122969e+33
+#define NPTF_N_1_HIST -0.66
+#define NPTF_N_2_HIST 18.2
+
+
+
+std::array<double, FLUX_HIST_BINS> fluxValues, fluxWidths;
+
+const double L_MIN_RANGE[2] = { 1.0e28, 1.0e34 };
+const double L_MAX_RANGE[2] = {1.0e34, 1.0e38}; //{ 1.0e34, 1.0e36 };
+const double ALPHA_RANGE[2] = { 1.1, 2.5 };
+const double L0_RANGE[2] = {1.0e30, 2.0e36}; //{ 1.0e32, 2.0e34 };
[…]

### 2021-06-15 luminosity-models-position/calc.cpp
Rearranging for linux

@@ -16,7 +16,7 @@ typedef std::vector<std::vector<double>> DoubleVector;
 /* When LOTS_OF_THREADS is defined, a target of 80-90 threads are made and run concurrently.
    Otherwise, four threads are made and run concurrently. */
 
-#define SENSITIVITY_DIVISOR 10.0
+#define SENSITIVITY_DIVISOR 1.0
 
 #define pi 3.14159265358979323
 #define ONE_PLUS_EPSILON 1.0000000001
@@ -64,7 +64,7 @@ const double logNormalPloegPoint[2] = { 1.6084e+32, 0.7003 };
 #define PLOT_SIZE 50
 #define FERMILAB_ALPHA 1.94
 
-#define ROOT "C:/Users/goods/Dropbox (MIT)/GCE UROP/"
+#define ROOT "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/"
 #define SENSITIVITY_PATH (ROOT "sensitivity/sensitivity.txt")
 #define PLOEG_PATH (ROOT "luminosity-models-step/ploeg/data/disk.csv")
 #define DISPLAY_SIZE 20.0
@@ -290,13 +290,6 @@ public:
     std::vector<double> logxs, ys, xs;
     double normalization;
 };
-
-template<int N>
-void addArrays(std::array<double, N>& result, std::array<double, N> summand) {
-    for (int i = 0; i < N; i++) {
-        result[i] += summand[i];
-    }
-}
 
 const SensitivityMap thresholds;
 const PloegData ploegData;
@@ -919,7 +912,9 @@ int hist() {
             CoordPair latLon = thresholds.indexToLatLon({ x, y });
             if (myAbs(latLon.first) > 2 * pi / 180) {// Cut out 2 degrees around the equator on each side.
                 std::array<double, FLUX_HIST_BINS> probs_here = getHistAtLatLon(latLon, thresholds.getFluxThreshold(latLon));
-                addArrays(probs, probs_here);
+                for (int i = 0; i < FLUX_HIST_BINS; i++) {
+                    probs[i] += probs_here[i];
+                }
             }
         }
     }

### 2021-06-15 luminosity-models-position/overlay-calculator/overlay-calculator/overlay-calculator - Copy.cpp

@@ -1,735 +1,0 @@
-#include <iostream>
-#include <string>
-#include <vector>
-#include <assert.h>
-#include <fstream>
-#include <sstream>
-#include <thread>
-#include <future>
-#include <boost/math/special_functions/gamma.hpp>
-
-typedef std::pair<double, double> CoordPair;
-typedef std::pair<int, int> IndexPair;
-typedef std::vector<std::vector<double>> DoubleVector;
-
-//#define LOTS_OF_THREADS // Use on Erebus
-/* When LOTS_OF_THREADS is defined, a target of 80-90 threads are made and run concurrently.
-   Otherwise, four threads are made and run concurrently. */
-
-#define POWER_STEP 1.1 // 1 is the minimum
-#define pi 3.14159265358979323
-#define ONE_PLUS_EPSILON 1.0000000001
-#define max(a, b) (((a) > (b)) ? (a) : (b))
-
-#define ALPHA 1.94
-#define DIST_TO_CENTER 8.5 // kpc
-#define CM_PER_KPC_SQUARED 9.523396e+42
-#define FLUX_EXCESS 7.494712733226778e-10  // All flux units are in ergs per second per square centimeter
-#define ERGS_PER_PHOTON 0.00545625167499331 // Use the ergs per photon for the NPTF paper
-
-
-const double L_MIN_RANGE[2] = { 1.0e28, 1.0e34 };
-const double L_MAX_RANGE[2] = { 1.0e34, 1.0e36 };
-const double L0_RANGE[2] = { 1.0e32, 2.0e34 };
-const double SIGMA_RANGE[2] = { 0.001, 1 };
-
-const double fermilabPaperPoint[2] = { 1e35, 1e29 };
-const double logNormalPaperPoint[2] = { 0.88e34, 0.62 };
-const double logNormalPloegPoint[2] = { 1.6084e+32, 0.7003 };
-
-// Values for the computation of the integral of the NFW profile.
-#define GAMMA 1.2
-#define NFW_SCALE_DIST 20 // kpc
-#define INTEGRAL_HALF_WIDTH (DIST_TO_CENTER * 0.9)// / 2 // kpc
-#define NFW_INTEGRAL_STEPS 1000
-
-#define ROOT "C:/Users/goods/Dropbox (MIT)/GCE UROP/"
-#define SENSITIVITY_PATH (ROOT "sensitivity/sensitivity.txt")
[…]

### 2021-06-15 luminosity-models-smoothing/calc.cpp

@@ -8,6 +8,8 @@
 #include <future>
 #include <boost/math/special_functions/gamma.hpp>
 
+#define INVALID -3789213.4812047 // A random number designed to encode an invalid input.
+
 typedef std::pair<double, double> CoordPair;
 typedef std::pair<int, int> IndexPair;
 typedef std::vector<std::vector<double>> DoubleVector;
@@ -16,14 +18,14 @@ typedef std::vector<std::vector<double>> DoubleVector;
 /* When LOTS_OF_THREADS is defined, a target of 80-90 threads are made and run concurrently.
    Otherwise, four threads are made and run concurrently. */
 
-#define SENSITIVITY_DIVISOR 10.0
+#define SENSITIVITY_DIVISOR 1.0
 
-#define pi 3.14159265358979323
+#define PI 3.14159265358979323
 #define ONE_PLUS_EPSILON 1.0000000001
 #define max(a, b) (((a) > (b)) ? (a) : (b))
 
-#define ALPHA 1.94
-#define L_MIN 1.0e29
+#define ALPHA 1.94 // for power law
+#define L_MIN 1.0e29 // for power law alpha
 #define DIST_TO_CENTER 8.5 // kpc
 #define CM_PER_KPC_SQUARED 9.523396e+42
 #define FLUX_EXCESS 1.2953417255755896e-09  // All flux units are in ergs per second per square centimeter
@@ -41,6 +43,10 @@ typedef std::vector<std::vector<double>> DoubleVector;
 #define NPTF_L_BREAK_HIST 8.656487610122969e+33
 #define NPTF_N_1_HIST -0.66
 #define NPTF_N_2_HIST 18.2
+
+#define START_FLUX_INTEGRAL 1.0e-25
+#define STOP_FLUX_INTEGRAL 1.0e35
+#define NUM_FLUX_STEPS 1e5
 
 
 
@@ -64,7 +70,7 @@ const double logNormalPloegPoint[2] = { 1.6084e+32, 0.7003 };
 #define PLOT_SIZE 50
 #define FERMILAB_ALPHA 1.94
 
-#define ROOT "C:/Users/goods/Dropbox (MIT)/GCE UROP/"
+#define ROOT "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/"
 #define SENSITIVITY_PATH (ROOT "sensitivity/sensitivity.txt")
[…]

### 2021-06-17 paper/draft.tex
Added paper template
Improve plots and work on Ploeg smoothing

@@
 \documentclass[a4paper,11pt]{article}
-\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
-             % images in pdf, png or jpg format)
+%\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
+%             % images in pdf, png or jpg format)
 
@@
                      % see the JCAP-author-manual
-
+\usepackage{siunitx}
 \usepackage[T1]{fontenc} % if needed
@@
 
+\newcommand{\parens}[1]{\left(#1\right)}
+\newcommand{\brackets}[1]{\left[#1\right]}
+\newcommand{\expp}[1]{\exp \parens{#1}}
+\newcommand{\fraci}[2]{#1 / #2}
+\newcommand{\comment}[1]{\emph{\color{red}{#1}}}
+
+\DeclareSIUnit\erg{erg}
+\DeclareSIUnit\parsec{pc}
+
 \abstract{Abstract...}
@@
 
-\section{Some examples and best-practices}
-\label{sec:intro}
+\section{Introduction}
 
-Here follow some examples of common features that you may wanto to use
-or build upon.
+\section{Methods \& Datasets}
 
-For internal references use label-refs: see section~\ref{sec:intro}.
-Bibliographic citations can be done with cite: refs.~\cite{a,b,c}.
-When possible, align equations on the equal sign. The package
-\texttt{amsmath} is already loaded. See \eqref{eq:x}.
+\subsection{Observables}
+To fit the luminosity functions described in section \ref{sec:lum-funcs}, we will use three observables: the total flux of the GCE $F_\text{GCE}$, the ratio of the total flux to the flux visible from point sources resolved by \textit{Fermi} $R_\text{r}$, and the number of resolved point sources $N_\text{r}$.
+We fix the first observable at $F_\text{GCE}= \SI{1.295e-09}{\erg\per\second}$ according to the methods outlined in section \ref{sec:total-lum}.
+We allow the other two observables to vary as functions of the parameters of the luminosity functions.
+
+We will also discuss a third feature of a potential MSP population in the GC: the total number of MSPs $N_\text{GCE}$, resolved or unresolved.
+This number is not measurable, but serves as a useful reference to gauge the physicality of any population of MSPs.
+\comment{Mention that it's expected to be around 40,000.}
+
+\subsection{Total GCE Luminosity}
+\label{sec:total-lum}
+Since an estimate of the total flux of the GCE is necessary for our data, we extract the total flux from several previous analyses of spectra using the following three methods and compare them.
+The spectral analyses we study here are refs.
+\cite{Zhong:2019ycb, Calore:2014xka, DiMauro:2021raz, Abazajian:2014fta, Gordon, Ajello}.
+Each reference reports the total flux $F_\gamma(E)$ observed in an energy bin centered on $E$.
+The spectra from these sources are reported in figure \ref{fig:all-spectra}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/all-spectra.pdf}
+    \caption{}
+    \label{fig:all-spectra}
+\end{figure}
+
+\comment{Describe the sources: what's similar between them, what's different.}
+
+We use compare three methods of extracting the total GCE flux from these analyses.
+The first method is direct numerical integration of the spectra provided by each source.
+This method is most sensitive to the data measured by \textit{Fermi} and does not attempt to abstract over it with a smooth function.
+
+However, numerical integration cannot account for the spectrum lying outside of \textit{Fermi}'s spectrum of sensitivity, and it may be oversensitive to experimental error.
+Therefore, we also consider a broken law fit to the data, of the same form as the NPTF luminosity function: eq.
+\ref{eqn:nptf}.
+It has four parameters: a constant of proportionality, the turnover flux $F_\text{b}$, and the slopes above and below the turnover flux $n_2$ and $n_1$.
+This function can then be analytically integrated over all flux values to get the total flux of the GCE.
+Many of the analyses cited above only report error bars on some points, because error bars on the other points are too large.
+We therefore fit only to the points with error bars reported.
+\comment{Mention the specific range fitted over}.
+
+Unfortunately, for some analyses, the number of points reported with error bars is only slightly larger than the number of parameters of the broken power law function.
+To ensure that the fit result is less prone to statistical deviations of a small number of points, we use a third method in addition to the above two.
+Ref.
+\cite{Calore:2014xka} provides their fit parameters for their GCE flux spectral data: $F_\text{b} = $.
+$n_1 = -1.42$, $n_2 = 2.63$.
+\comment{Check for sign errors in the original.
+Also get the flux they provide.}.
+The third fitting method is to fix these three broken power law parameters at these values and allow only the overall normalization to vary.
+
+An example of all three of these fitting methods applied to reference \cite{DiMauro:2021raz} is shown in figure \ref{fig:di-mauro-example}.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/di-mauro-example.pdf}
+    \caption{}
+    \label{fig:di-mauro-example}
+\end{figure}
+
+In practice,
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/total-flux-bars.pdf}
+    \caption{}
+    \label{fig:total-flux-bars}
+\end{figure}
+
+\comment{Just double check that I normalized the power law correctly in parse\_spectrum.py.}
+
+\subsection{GCE Spacial distribution}
 \begin{equation}
-\label{eq:x}
+    \rho_\text{NFW}(r) = \parens{\frac{r}{r_s}}^{-\gamma}\parens{1 + \frac{r}{r_s}}^{-3-\gamma}
+    \label{eqn:nfw}
+\end{equation}
+where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work.
+
+\subsection{Luminosity Functions}
+\label{sec:lum-funcs}
+Previous work has interpreted this MSP model. Ref. \cite{Zhong:2019ycb} has proposed an exponentially damped power law luminosity function
+\begin{equation}
+    P_\text{Power law}(L) = L^{-\alpha} \expp{-\frac{L}{L_\text{max}}}\brackets{\Gamma\parens{1-\alpha, \frac{L_\text{min}}{L_\text{max}}}L_\text{max}^{1-\alpha}}^{-1}.
+    \label{eqn:power-law}
+\end{equation}
+The function has been normalized so that $P_\text{Power law}(L)$ represents the probability that a given MSP has luminosity $L$.
+This luminosity function restricts the range of luminosities to $[L_\text{min}, \infty)$, where $L_\text{min}$, $L_\text{max}$, and $\alpha$ are free parameters.
+\comment{The following should probably be moved to the introduction, where Fermilab's research is described.} This reference found that $(\SI{1e29}{\erg\per\second}, \SI{1e35}{\erg\per\second}, 1.94)$ is required reproduced observations.
+They find that this model admits three million MSPs in the GCE, which differs from estimates based on the physical properties of observed MSPs that estimate the number of MSPs at the Galactic center at the order of 40,000 \cite{citation_needed}.
+
+Ref. \cite{osti_1305131} proposes a power law luminosity function of
+\begin{equation}
+    P_\text{Log normal}(L)= \frac{\log_{10} e}{\sigma \sqrt{2\pi} L}\expp{-\frac{\parens{\log_{10} L - \log_{10} L_0}^2}{2\sigma^2}},
+    \label{eqn:log-normal}
+\end{equation}
+where $L_0$ and $\sigma$ are free parameters.
+The ref.
+fits this model to data from globular cluster (GCL) data, yielding values $L_0 = \SI{8.8e33}{\erg\per\second}$ and $\sigma=0.62$.
+It predicts thousands of MSPs to occupy the GCE if the entire excess is to be explained by MSPs.
+
+Ref.
+\cite{Ploeg:2020jeh} proposes several more intricate luminosity functions, derived from a model of the pulsars themselves.
+They find that the same model may be used for resolved, globular cluster MSPs in the Galactic disk and unresolved MSPs at the Galactic center.
+We use their luminosity function generated for the galactic disk.
+It closely resembles a log normal luminosity function as in equation \ref{eqn:log-normal}, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$.
+
+Finally, ref. \cite{Lee:2015fea} proposes a broken-power law luminosity function of
+\begin{equation}
+    P_\text{NPTF}(L) = \parens{\frac{\parens{1-n_1}\parens{1-n_2}}{L_b \parens{n_1 - n_2}}}\begin{cases}
+        \parens{\fraci{L}{L_\text{b}}}^{-n_{1}} & L < L_{b} \\
+        \parens{\fraci{L}{L_\text{b}}}^{-n_{2}} & L > L_b
+    \end{cases}
+    \label{eqn:nptf}
+\end{equation}
+where the free parameters  $n_1$, $n_2$, and $L_b$ were found via a Non-Poissonian Template Fitting model (NPTF) to be $(18.2, -0.66, \SI{8.66e+33}{\erg\per\second})$ for an NFW-squared-distributed population of MSPs named NFW PS.
+The pxxxaper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.34e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced.
+We set $L_\text{min}=\SI{1e29}{\erg\per\second}$, which is the same minimum pulsar luminosity used by ref.
+\cite{Zhong:2019ycb}.
+The turnover luminosity $L_\text{b}$ was given as a photon flux value in units of photons per centimeter squared per second; the process used to convert from photon flux to luminosity is detailed in the methods section.
+
+All the above-mentioned luminosity functions are shown in figure \ref{fig:lum-funcs}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{figs/lum-funcs.pdf}
+    \includegraphics[width=0.49\textwidth]{figs/l-lum-funcs.pdf}
+    \caption{\textit{Left:} Power law, GCL log normal, GCE log normal, and NPTF luminosity functions for MSPs in the GCE, vertically rescaled.
+\textit{Right:} Same plot as \textit{left} but weighted by luminosity.}
+    \label{fig:lum-funcs}
+\end{figure}
+
+\subsection{Sensitivity Models}
+The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some bright sources to be unresolved.
+We make use of three sensitivity models to model these factors.
+
+The first, and simplest, is a step function luminosity model.
+It asserts that all point sources with $L>L_\text{th}$ are resolved, and none with $L<L_{\text{th}}$.
+Here, $L_\text{th} = \SI{e34}{\erg\per\second}$.
+This sensitivity model is the one used by ref.
+\cite{Zhong:2019ycb} to obtain the parameters of the power law luminosity function described in the paragraph after eq.
+\ref{eqn:power-law}.
+The four properties we intend to measure are then given by
+\begin{equation}
     \begin{split}
-x &= 1 \,,
-\qquad
-y = 2 \,,
-\\
-z &= 3 \,.
+        L_\text{GCE} &= N_\text{GCE}\int_{L_\text{min}}^\infty L P(L) dL \,, \qquad
+        L_\text{r} = N_\text{GCE}\int_{L_\text{th}}^\infty L P(L) dL \,, \\
+        N_\text{r} &= N_\text{GCE}\int_{L_\text{th}}^\infty P(L) dL \,,
+        \label{eqn:observables-sens-1}
     \end{split}
 \end{equation}
-Also, watch out for the punctuation at the end of the equations.
+where $N_\text{GCE}$ is a normalization constant, fixed by requiring that $L_\text{GCE}$ reproduces the flux $F_\text{GCE}$ observed.
+The conversion between $L_\text{GCE}$ and $F_\text{GCE}$ is outlined in appendix \ref{app:lum-to-flux}.
 
-If you want some equations without the tag (number), please use the available
-starred-environments. For example:
-\begin{equation*}
-x = 1
-\end{equation*}
+The second sensitivity model acknowledges the effect of background flux on resolvability and uses a position-dependent flux threshold $F_\text{th}(b, l)$ published by the \textit{Fermi} team \cite{Fermi-LAT:2019yla, Ballet:2020hze} (figure \ref{fig:sensitivity}).
+\comment{Here, I could talk about how to convert between flux and luminosity and then use the mean of this map to assess how accurate 1e34 ergs/s actually is.}.
+To calculate the four properties of GC MSP populations, we use
+\begin{equation}
+    \begin{split}
+        F_\text{GCE} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\int_{L_\text{min}}^\infty dL \frac{L}{4\pi s^2}P(L)\,, \\
+        N_\text{GCE} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\,, \\
+        F_\text{r} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\int_{4\pi s^2F_\text{th}(b,\ell)}^\infty dL \frac{L}{4\pi s^2}P(L)\,, \\
+        N_\text{r} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\int_{4\pi s^2F_\text{th}(b,\ell)}^\infty dL P(L) \,. \\
+        \label{eqn:observables-sens-2}
+    \end{split}
+\end{equation}
+Here, $\Omega$ represents the $20^\circ \times 20^\circ$ region of interest with $|b| < 2^\circ$ cut out, and $A$ is the coefficient of equation \ref{eqn:nfw}, fixed by forcing $F_\text{GCE}$ to equal the observed value.
+In equation \ref{eqn:observables-sens-2} represents the distance to the galactic center from the point of integration, and is determined by the law of cosines:
+$r^2 = s^2 + r_c^2 - 2r_c s \cos \ell$.
 
-The amsmath package has many features. For example, you can use use
-\texttt{subequations} environment:
-\begin{subequations}\label{eq:y}
-\begin{align}
-\label{eq:y:1}
-a & = 1
-\\
-\label{eq:y:2}
-b & = 2
-\end{align}
-and it will continue to operate across the text also.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figs/sensitivity-map.pdf}
+    \caption{Position-dependent flux thresholds required to resolve an MSP, published by refs. \cite{Fermi-LAT:2019yla, Ballet:2020hze}.}
+    \label{fig:sensitivity}
+\end{figure}
+
+The third and final sensitivity model takes into account the statistical fluctuation of photons from point sources.
+Ref.
+\cite{Ploeg:2020jeh} models the probability that a point source with average flux $F$ is resolved as
 \begin{equation}
-\label{eq:y:3}
-c = 3
+    P_\text{r}(F) = \frac{1}{\sigma_\text{th} F\sqrt{2\pi}} \expp{-\frac{(\ln F - (F_\text{th}(\ell, b) - K_\text{th}))^2}{2\sigma_\text{th}^2}}
+    \label{eqn:ploeg-smoothing}
 \end{equation}
-\end{subequations}
-The references will work as you'd expect: \eqref{eq:y:1},
-\eqref{eq:y:2} and \eqref{eq:y:3} are all part of \eqref{eq:y}.
+where $K_\text{th}$ and $\sigma_\text{th}$ were determined via an MCMC fit to globular cluster MSPs.
+\comment{What are the values?} The observables are calculated simply by multiplying the integrand of the luminosity integral in equation \ref{eqn:observables-sens-2} by $P_r(L/4\pi s^2)$ for $F_\text{r}$ and $N_\text{r}$.
+(Not for $F_\text{GCE}$, because we do not require that the $F_\text{GCE}$ flux be resolved.)
 
-A similar solution is available for figures via the \texttt{subfigure}
-package (not loaded by default and not shown here).
-All figures and tables should be referenced in the text and should be
-placed at the top of the page where they are first cited or in
-subsequent pages. Positioning them in the source file
-after the paragraph where you first reference them usually yield good
-results. See figure~\ref{fig:i} and table~\ref{tab:i}.
+\section{Results}
 
-\begin{table}[tbp]
-\centering
-\begin{tabular}{|lr|c|}
-\hline
-x&y&x and y\\
-\hline
-a & b & a and b\\
-1 & 2 & 1 and 2\\
-$\alpha$ & $\beta$ & $\alpha$ and $\beta$\\
-\hline
-\end{tabular}
-\caption{\label{tab:i} We prefer to have borders around the tables.}
-\end{table}
+\section{Future Sensitivity}
 
-We discourage the use of inline figures (wrapfigure), as they may be
-difficult to position if the page layout changes.
-
-We suggest not to abbreviate: ``section'', ``appendix'', ``figure''
-and ``table'', but ``eq.'' and ``ref.'' are welcome. Also, please do
-not use \texttt{\textbackslash emph} or \texttt{\textbackslash it} for
-latin abbreviaitons: i.e., et al., e.g., vs., etc.
-
-\section{Sections}
-\subsection{And subsequent}
-\subsubsection{Sub-sections}
-\paragraph{Up to paragraphs.} We find that having more levels usually
-reduces the clarity of the article. Also, we strongly discourage the
-use of non-numbered sections (e.g.~\texttt{\textbackslash
-  subsubsection*}).  Please also see the use of
-``\texttt{\textbackslash texorpdfstring\{\}\{\}}'' to avoid warnings
-from the hyperref package when you have math in the section titles
+\section{Conclusion}
 
 \appendix
-\section{Some title}
-Please always give a title also for appendices.
+\section{Conversion Between GCE Luminosity and Flux}
+\label{app:lum-to-flux}
+\comment{Copy most of this from the January summary, if I include it.}
 

### 2021-06-17 compare-spectra/make-example.py

@@ -1,0 +1,31 @@
+import numpy as np
+import parse_spectrum as ps
+from matplotlib import pyplot as plt
+import matplotlib.lines as mlines
+import matplotlib.transforms as mtrans
+
+plt.style.use("jcap")
+
+NAME = ps.DI_MAURO
+SPECTRUM_RANGE = [0.5, 10]# GeV
+NUM_PLOTS = 7
+SHAPES=['o', 's', '^', '*', 'd', '+', 'x']
+
+fig, ax = plt.subplots()
+
+f = ps.Spectrum(NAME)
+f.display_data(ax)
+f.display_calore(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1], show_all=True)
+f.display_power_law(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1], show_all=True)
+numerical_flux = f.get_numerical_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+calore_flux = f.get_calore_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+fit_flux = f.get_power_law_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+f.label_axes(ax)
+
+ax.plot([], [], color='C1', linestyle='--', label="Calore fit")
+ax.plot([], [], color='C2', linestyle='-.', label="Power law fit")
+
+fig.tight_layout()
+fig.savefig("example.pdf")
+ax.legend()
+plt.show()

### 2021-06-17 compare-spectra/numerical-integration.py

@@ -4,10 +4,11 @@ from matplotlib import pyplot as plt
 import matplotlib.lines as mlines
 import matplotlib.transforms as mtrans
 
-plt.style.use("latex")
+plt.style.use("jcap")
 
 SPECTRUM_RANGE = [0.5, 10]# GeV
 NUM_PLOTS = 7
+SHAPES=['o', 's', '^', '*', 'd', '+', 'x']
 
 fig, axes = plt.subplots(nrows=3, ncols=3, figsize=(10, 6), sharex='col', sharey='row')
 
@@ -39,10 +40,10 @@ for i in range(0, NUM_PLOTS):
     ax = axes[i%3][i//3]
     f = ps.Spectrum(i)
     names.append(f.get_name())
-    f.display_data(allax, color="C"+str(i))
+    f.display_data(allax, color="C"+str(i), shape=SHAPES[i])
     f.display_data(ax)
     f.display_calore(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
-    f.display_power_law(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+    #f.display_power_law(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     numerical_flux = f.get_numerical_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     calore_flux = f.get_calore_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     fit_flux = f.get_power_law_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
@@ -57,7 +58,7 @@ for i in range(0, NUM_PLOTS):
     f.label_axes(allax)
 
     print(f.get_name(), numerical_flux)
-    
+
     ax.annotate("Num: {}\nCalore: {}\nFit: {}".format(sciNot(numerical_flux), sciNot(calore_flux), sciNot(fit_flux)), (0.2, 0.1), xycoords='axes fraction')
 
 
@@ -68,29 +69,32 @@ fig.delaxes(axes[1][2])
 
 while None in fit_fluxes:
     index = fit_fluxes.index(None)
-    del fit_fluxes[index]
-    del calore_fluxes[index]
-    del num_fluxes[index]
-    del names[index]
+    fit_fluxes[index] = 0
+    #del fit_fluxes[index]
+    #del calore_fluxes[index]
+    #del num_fluxes[index]
+    #del names[index]
 
 while None in num_fluxes:
[…]

### 2021-06-17 compare-spectra/parse_spectrum.py

@@ -66,14 +66,14 @@ class Spectrum:
             self.pointsy /= LARGE_ROI_FACTOR
             self.up_barsy /= LARGE_ROI_FACTOR
             self.down_barsy /= LARGE_ROI_FACTOR
-        
+
         self.id = id
         self.calore_norm = None
         self.fit_norm = None
         self.fit_alpha_below = None
         self.fit_alpha_above = None
         self.fit_l_break = None
-    
+
     def get_name(self):
         if self.id == FERMILAB_GNFW:
             return "Fermilab gNFW"
@@ -103,7 +103,7 @@ class Spectrum:
             yres.append(10**float(y) * ERGS_PER_GEV)
         f.close()
         return np.asarray(xres), np.asarray(yres) * ROI_SIZE
-    
+
     def _get_point(self, logx, datax, datay):
         i = 0
         if logx < datax[0] or logx > datax[-1]:
@@ -169,7 +169,7 @@ class Spectrum:
         self._fit_calore(l_min, l_max)
         ergs_l_min = l_min * ERGS_PER_GEV
         ergs_l_max = l_max * ERGS_PER_GEV
-        return self.calore_norm * (CALORE_L_BREAK**CALORE_ALPHA_BELOW / (CALORE_ALPHA_BELOW - 2) * (ergs_l_min**(2 - CALORE_ALPHA_BELOW) - CALORE_L_BREAK**(2 - CALORE_ALPHA_BELOW)) + 
+        return self.calore_norm * (CALORE_L_BREAK**CALORE_ALPHA_BELOW / (CALORE_ALPHA_BELOW - 2) * (ergs_l_min**(2 - CALORE_ALPHA_BELOW) - CALORE_L_BREAK**(2 - CALORE_ALPHA_BELOW)) +
                             CALORE_L_BREAK**CALORE_ALPHA_ABOVE / (CALORE_ALPHA_ABOVE - 2) * (CALORE_L_BREAK**(2 - CALORE_ALPHA_ABOVE) - ergs_l_max**(2 - CALORE_ALPHA_ABOVE)))
 
     def get_power_law_flux(self, l_min, l_max):
@@ -178,7 +178,7 @@ class Spectrum:
             return None
         ergs_l_min = l_min * ERGS_PER_GEV
         ergs_l_max = l_max * ERGS_PER_GEV
[…]

### 2021-06-17 luminosity-models-position/calc.cpp

@@ -615,8 +615,11 @@ int powerLaw() {
     std::cout << paperScale << std::endl;
     std::cout << writeText << std::endl;
     std::ofstream recordFile;
+
     recordFile.open(ROOT "luminosity-models-position/data-" + std::to_string((int)SENSITIVITY_DIVISOR) + "x/power-law/record.txt");
     recordFile << writeText;
+
+    recordFile.close();
 
     // Generate unscaled data
     DoubleVector totalNum, numSeen, fluxSeen, totalFlux;

### 2021-06-17 luminosity-models-smoothing/calc.cpp

@@ -44,9 +44,9 @@ typedef std::vector<std::vector<double>> DoubleVector;
 #define NPTF_N_1_HIST -0.66
 #define NPTF_N_2_HIST 18.2
 
-#define START_FLUX_INTEGRAL 1.0e-25
-#define STOP_FLUX_INTEGRAL 1.0e35
-#define NUM_FLUX_STEPS 1e5
+#define START_FLUX_INTEGRAL 1.0e-12
+#define STOP_FLUX_INTEGRAL 1.0e-8
+#define NUM_FLUX_STEPS 1e3
 
 
 
@@ -234,6 +234,10 @@ double get_lum_func_strip(double arg1, double arg2) {
 }
 
 double sensitivity(double flux, double threshold) {
+    // Need to check for whether the sensitivity should be used or not here.
+    if (threshold == INVALID) {
+        return 1.0;
+    }
     if (flux > threshold) {
         return 1.0;
     }
@@ -246,18 +250,18 @@ double integrate(double threshold, double distance, double arg1, double arg2) {
     double start_flux_integral;
     switch (luminosityFunction) {
     case LUMINOSITY_FUNCTION::POWER_LAW:
-        start_flux_integral = arg1;
+        start_flux_integral = arg1 / (4 * PI * distance * distance * CM_PER_KPC_SQUARED);
         break;
     case LUMINOSITY_FUNCTION::POWER_LAW_ALPHA:
-        start_flux_integral = L_MIN;
+        start_flux_integral = L_MIN / (4 * PI * distance * distance * CM_PER_KPC_SQUARED);
         break;
     default:
         start_flux_integral = START_FLUX_INTEGRAL;
         break;
     }
-    double step_width = (STOP_FLUX_INTEGRAL - START_FLUX_INTEGRAL) / 
+    double step_width = (STOP_FLUX_INTEGRAL - start_flux_integral) /
         NUM_FLUX_STEPS;
-    for (double flux = START_FLUX_INTEGRAL;
+    for (double flux = start_flux_integral;
         flux < STOP_FLUX_INTEGRAL;
         flux += step_width) {
 
@@ -273,44 +277,49 @@ double lintegrate(double threshold, double distance, double arg1, double arg2) {
     // lMin, lMax; l0, sigma; nBelow, nAbove
     double integral = 0;
     double start_flux_integral;
+    double flux_to_lum = (4 * PI * distance * distance * CM_PER_KPC_SQUARED);
[…]

### 2021-06-17 paper/figs/get-figs.py

@@ -1,0 +1,20 @@
+import os, shutil
+
+ROOT = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/"
+
+f = open("fig-sources.txt", 'r')
+for line in f.readlines():
+    if line == '':
+        continue
+    args = line[:-1].split(' ')
+    if len(args) != 2:
+        continue
+    name, path = args
+    if not os.path.isfile(ROOT + path):
+        print("Could not find " + path)
+        continue
+    if path[-4:] not in [".eps", ".pdf"]:
+        print("WARNING: .eps or .pdf file formats are preferred")
+    shutil.copyfile(ROOT+path, "./"+name)
+
+f.close()

### 2021-06-17 plot-functions/plotter.py

@@ -3,30 +3,28 @@ from math import pi
 from scipy.special import gammainc, gamma
 from matplotlib.lines import Line2D
 import numpy as np
-from numpy import exp, sqrt, log10, log
-import ploegload as pl
 
-plt.style.use('latex')
+plt.style.use('jcap')
 
 def Gamma(s, x):
     if(s < 0):
-        return (Gamma(s+1, x) - x**s * exp(-x))/s
+        return (Gamma(s+1, x) - x**s * np.exp(-x))/s
     return gamma(s) * (1-gammainc(s, x))
 
 CM_PER_KPC_SQUARED = 9.523396e+42
 ERGS_PER_PHOTON = 0.00545625167499331
 DIST_TO_CENTER = 8.5
 
-ploegFunc = pl.LuminosityFunction(pl.DISK)
+LUM_TO_FLUX = 1.1093417307914119e-46
 
 NUM_PLOT_POINTS = 200
 PLOT_LOG_MIN = 29.0
-PLOT_LOG_MAX = ploegFunc.logxs[-1]
+PLOT_LOG_MAX = 35.0
 
 ALPHA = 1.94
 L_MIN = 1.0e29
 L_MAX = 1.0e35
-L_THRESH = 34
+L_THRESH = 10e34
 L0_LOG_NORMAL = 8.8e33
 SIGMA_LOG_NORMAL = 0.62
 L0_PLOEG_FIT = 1.61e32
@@ -39,76 +37,80 @@ N_ABOVE_DISK = 17.5
 L_BREAK_DISK = 6.8e-9 * ERGS_PER_PHOTON * 4 * pi * (DIST_TO_CENTER * DIST_TO_CENTER * CM_PER_KPC_SQUARED)
 
 
-def powerLaw(x):
-    return log(10) * x * x**(-ALPHA) * exp(- x / L_MAX) / (Gamma(1 - ALPHA, L_MIN / L_MAX) * L_MAX ** (1 - ALPHA))
-
+def powerLaw(x, lmin, lmax, alpha):
+    return x**-alpha * np.exp(-x / lmax) / (Gamma(1-alpha, lmin/lmax) * lmax**(1-alpha))
 def logNormal(x, L0, sigma):
-    return log(10) * x * log10(exp(1)) / (sigma * sqrt(2 * pi) * x) * exp(- (log10(x) - log10(L0))**2 / (2 * sigma**2))
-
-def ploeg(x):
-    return log(10) * x * ploegFunc(x)
-
[…]

### 2021-06-17 sensitivity/thresholds.py

@@ -8,15 +8,14 @@
 # https://arxiv.org/pdf/1911.12369.pdf
 
 import numpy as np
-import matplotlib
+import matplotlib as mpl
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 from astropy.utils.data import download_file
 from astropy.io import fits
 from math import pi, cos, sqrt
 
-matplotlib.font_manager.FontManager()
-plt.style.use('latex')
+plt.style.use('jcap')
 
 DIST_TO_CENTER = 8.5
 KAPPA = 0.5 # dist to center / r_s
@@ -68,16 +67,16 @@ for x in range(len(image_data)):
 trimmed_flux_data = np.asarray(trimmed_flux_data)
 trimmed_lum_data = np.asarray(trimmed_lum_data)
 
+#plt.figure(figsize=(8, 6))
+#mpl.rcParams["font.size"]=12
 
 # Display flux data:
-plt.figure()
 c = plt.imshow(trimmed_flux_data, 
                    norm=colors.LogNorm(vmin=np.nanmin(trimmed_flux_data),
                    vmax=np.nanpercentile(trimmed_flux_data, 99)))
 cbar = plt.colorbar(c)
-cbar.set_label("$F_{th}(b, \\ell)$ (erg/cm$^2$/s)")
+cbar.set_label("$F_\\textrm{th}(b, \\ell)$ (erg/cm$^2$/s)")
 
-plt.title("Fermi LAT flux sensitivity (0.1-100 GeV)")
 xPositions = np.arange(0, trimmed_flux_data.shape[1], trimmed_flux_data.shape[1]//NUM_X_LABELS) # pixel count at label position
 xLabels = np.linspace(start=-DISPLAY_SIZE, stop=DISPLAY_SIZE, num=NUM_X_LABELS+1) # labels you want to see
 np.append(xPositions, trimmed_flux_data.shape[1])
@@ -90,7 +89,7 @@ plt.yticks(yPositions, [int(i) for i in yLabels])
 plt.xlabel("$\\ell$ (deg)")
 plt.ylabel("$b$ (deg)")
 plt.tight_layout()
-plt.savefig("flux-thresholds.png")
+plt.savefig("flux-thresholds.pdf")
 
 # Cut luminosity data
 '''for x in range(len(trimmed_lum_data)):

### 2021-06-18 paper/draft.tex
Added many plots to paper

@@
 \usepackage[T1]{fontenc} % if needed
+\usepackage{subcaption}
 
@@
 \subsection{Observables}
+\label{sec:observables}
 To fit the luminosity functions described in section \ref{sec:lum-funcs}, we will use three observables: the total flux of the GCE $F_\text{GCE}$, the ratio of the total flux to the flux visible from point sources resolved by \textit{Fermi} $R_\text{r}$, and the number of resolved point sources $N_\text{r}$.
-We fix the first observable at $F_\text{GCE}= \SI{1.295e-09}{\erg\per\second}$ according to the methods outlined in section \ref{sec:total-lum}.
-We allow the other two observables to vary as functions of the parameters of the luminosity functions.
+All of these observables will be made with reference to a region of interest (ROI) defined by $|\ell| < 20^\circ$ and $2^\circ < |b| < 20^\circ$, and we will restrict the GCE spectrum to $\SI{0.1}{\giga\electronvolt} < E_\gamma < \SI{100}{\giga\electronvolt}$.
+
+The other two observables have been studied by \comment{Some technical name for the Fermilab team.} \cite{Zhong:2019ycb}.
+The authors performed a template fit to data from Fermi-LAT to isolate spacial peaks in flux, finding 110 \comment{(I got 110; their paper says 107)} peaks within 0.3$^\circ$ of a source in the 4FGL catalog within the region of interest \cite{Abdollahi_2020}.
+Of these 110 sources, they exclude all that are listed in the 4FGL catalog as not associated with pulsars.
+Of those that are known to be pulsars, they exclude all whose positions are known not to be within 2 kpc of the GC via the ATNF Pulsar Catalog \cite{Hobbs04}.
+This leaves 47 point sources in the 4FGL catalog whose origins are either known to be pulsars in the GC or are unknown.
+We will therefore set $N_\text{r} = 47$ for this paper.
+If the allowed distance between a flux peak and a 4FGL source is extended from 0.3$^\circ$ to $0.55^\circ$, five more sources are added.
+Together, the 47 sources are responsible for $R_\text{r}=0.2$ of the total GCE flux.
+\comment{Shouldn't I actually redo this addition given the fact that I'm now not using the same GCE flux as Fermilab?} These 47+5 sources used here are displayed in figure \ref{fig:47-sources}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/point-source-positions.pdf}
+    \caption{The 47 point sources within $0.3^\circ$ of a 4FGL source.
+Also shown are the 5 sourecs added by extending to $0.55^\circ$ separation.
+The sources are scaled by luminosity in radius.
+The gray band represents the $|b| \leq 2^\circ$ cut made around the galactic disk.}
+    \label{fig:47-sources}
+\end{figure}
+
+It is important to note that the above values for $N_\text{r}$ and $R_\text{r}$ define an allowed region, which includes populations with lower $N_\text{r}$ and $R_\text{r}$, because some of the unknown sources might not be pulsars.
 
@@
     \includegraphics[width=0.5\textwidth]{figs/all-spectra.pdf}
-    \caption{}
+    \caption{Spectra from seven analyses of the GCE, using different background models, shown with error bars when reported.}
     \label{fig:all-spectra}
@@
 The third fitting method is to fix these three broken power law parameters at these values and allow only the overall normalization to vary.
+An example of all three of these fitting methods applied to reference \cite{DiMauro:2021raz} and shown in figure \ref{fig:di-mauro-example}.
 
-An example of all three of these fitting methods applied to reference \cite{DiMauro:2021raz} is shown in figure \ref{fig:di-mauro-example}.
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{figs/di-mauro-example.pdf}
-    \caption{}
+    \caption{Spectrum produced by di Mauro in ref. \cite{DiMauro:2021raz}, with the two broken power law models fitted and shown.}
     \label{fig:di-mauro-example}
@@
 
-In practice,
+In practice, the three fitting methods yield very similar results for a single analysis.
+However, the values provided by different analyses vary greatly.
+For this study, we use the value obtained from di Mauro's analysis because it occupies a position near the middle of the distribution of GCE luminosities and is a recent study.
+We choose the value obtained by numerical integration, which is $F_\text{GCE} = \SI{1.295e-9}{\erg\per\centi\meter\squared\per\second}$.
+
+\comment{Discuss how rescaling of the ROI was done}
+
 \begin{figure}
@@
     \includegraphics[width=0.5\textwidth]{figs/total-flux-bars.pdf}
-    \caption{}
+    \caption{Total flux of the GCE as determined by the three integration methods discussed.
+\comment{Here I would discuss why Ajello doesn't have a value for the power law case if this is still true once I have the original source}.}
     \label{fig:total-flux-bars}
@@
 \end{equation}
-where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work.
+where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work. Also, $r_c = \SI{8.5}{\kilo\parsec}$
 
@@
 where the free parameters  $n_1$, $n_2$, and $L_b$ were found via a Non-Poissonian Template Fitting model (NPTF) to be $(18.2, -0.66, \SI{8.66e+33}{\erg\per\second})$ for an NFW-squared-distributed population of MSPs named NFW PS.
-The pxxxaper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.34e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced.
+The paper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.34e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced.
 We set $L_\text{min}=\SI{1e29}{\erg\per\second}$, which is the same minimum pulsar luminosity used by ref.
@@
 \subsection{Sensitivity Models}
+\label{sec:sensitivity}
 The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some bright sources to be unresolved.
@@
     \includegraphics[width=0.7\textwidth]{figs/sensitivity-map.pdf}
-    \caption{Position-dependent flux thresholds required to resolve an MSP, published by refs. \cite{Fermi-LAT:2019yla, Ballet:2020hze}.}
+    \caption{Position-dependent flux thresholds required to resolve an MSP, published by refs.
+\cite{Fermi-LAT:2019yla, Ballet:2020hze}.
+\comment{Maybe I shouldn't show this plot.
+It's barely original; just a display of a FITS file pulled from the 4FGL website.
+But I could overlay the previous figure of where the 47 point sources are.
+Would that be useful?}}
     \label{fig:sensitivity}
@@
 \end{equation}
-where $K_\text{th}$ and $\sigma_\text{th}$ were determined via an MCMC fit to globular cluster MSPs.
-\comment{What are the values?} The observables are calculated simply by multiplying the integrand of the luminosity integral in equation \ref{eqn:observables-sens-2} by $P_r(L/4\pi s^2)$ for $F_\text{r}$ and $N_\text{r}$.
+where $K_\text{th} = 0.45$ and $\sigma_\text{th} = 0.28$ were determined via an MCMC fit to globular cluster MSPs.
+The observables are calculated simply by multiplying the integrand of the luminosity integral in equation \ref{eqn:observables-sens-2} by $P_r(L/4\pi s^2)$ for $F_\text{r}$ and $N_\text{r}$.
 (Not for $F_\text{GCE}$, because we do not require that the $F_\text{GCE}$ flux be resolved.)
@@
 \section{Results}
+\subsection{Step function and position dependent sensitivity models}
+Using each of the luminosity functions outlined in section \ref{sec:sensitivity}, we extract the total number of resolvable point sources $N_\text{r}$, the ratio of the flux received from those resolved point sources to the total flux of the GCE $R_\text{r}$, and the total number of point sources $N_\text{GCE}$ by forcing each function to reproduce the observed flux of the GCE.
+This is done for many parameterizations of the power law and log normal luminosity functions (eqs.
+\ref{eqn:power-law} and \ref{eqn:log-normal}), with results using the step function and the position-dependent sensitivity models shown in figures \ref{fig:step-function} and \ref{fig:position-dependent} respectively.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figs/power-law-step.pdf}
+        \includegraphics[width=\textwidth]{figs/power-law-alpha-step.pdf}
+        \includegraphics[width=\textwidth]{figs/log-normal-step.pdf}
+        \caption{Step function sensitivity model}
+        \label{fig:step-function}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figs/power-law-pos-1x.pdf}
+        \includegraphics[width=\textwidth]{figs/power-law-alpha-pos-1x.pdf}
+        \includegraphics[width=\textwidth]{figs/log-normal-pos-1x.pdf}
+        \caption{Position dependent sensitivity model}
+        \label{fig:position-dependent}
+    \end{subfigure}
+    \caption{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ calculations generated for parameterizations of a power law luminosity function (top two plots) and log normal (bottom plots).
+The parameterizations used in other analyses are marked.
+Regions allowed by the $N_\text{r} \leq 47$ and $R_\text{r} \leq 0.2$ are marked with \texttt{|} and \texttt{-} respectively, while regions allowed by both constraints are marked with \texttt{+}.
+The top power law plot (blue) fixes $\alpha=1.94$ while the lower (green) fixes $L_\text{min}=\SI{1e29}{erg\per\second}$ }
+\end{figure}
+
+Also shaded in these figures is the ``allowed region'' for each luminosity function---that is, the set of parameters that yield $N_\text{r} \leq 47$ and $R_\text{r} \leq 0.2$.
+
+The analysis is also performed on the NPTF luminosity function, but only for the parameterization outlined in ref.
+\cite{Lee:2015fea} and therefore no figure is generated.
+Predictions for $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for the specific parameterizations suggested by previous works are shown in tables \ref{tab:step-function-results} and \ref{tab:position-dependent-results}.
+
+\begin{table}
+    \centering
+    \begin{subtable}[h]{0.55\textwidth}
+        \begin{tabular}{|l|c|c|c|}
+            \hline
+            Luminosity function & $N_\text{r}$ & $R_\text{r}$ & $N_\text{GCE}$\\ \hline \hline
+            Observation & 47 & 0.2 & \\ \hline
+            Power law & 115 & 0.193 & $\num{8.14e6}$ \\
+            Log normal, GCL & 296 & 0.910 & 638 \\
+            Log normal, GCE & 142 & 0.180 & $\num{2.58e4}$ \\
+            NFW NPTF & 19.9 & 0.0136 & $\num{2.71e3}$ \\
+            DISK NPTF & 208 & 0.883 & $\num{2.73e4}$ \\
+            \hline
+        \end{tabular}
+        \caption{Step function sensitivity model}
+        \label{tab:step-function-results}
+    \end{subtable}
+    \hfill
+    \begin{subtable}[h]{0.44\textwidth}
+        \begin{tabular}{|c|c|c|}
+            \hline
+            $N_\text{r}$ & $R_\text{r}$ & $N_\text{GCE}$\\ \hline \hline
+            47 & 0.2 & \\ \hline
+            17.6 & 0.101 & $\num{5.91e6}$ \\
+            77.5 & 0.692 & 463 \\
+            13.4 & 0.0648 & $\num{1.91e4}$ \\
+            7.48 & 0.0300 & $\num{1.97e3}$ \\
+            71.7 & 0.757 & $\num{1.98e4}$ \\
+            \hline
+        \end{tabular}
+        \caption{Position-dependent sensitivity model}
+        \label{tab:position-dependent-results}
+    \end{subtable}
+    \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on four luminosity functions and the requirement that the point sources reproduce the entire flux of the GCE.}
+\end{table}
+
+The results of this analysis scale linearly with the flux of the GCE used.
+Figure \ref{fig:multiple-fluxes} shows figure \ref{tab:position-dependent-results} but with flux values from analyses other than di Mauro's represented.
+Note that $R_\text{r}$ does not vary because both fluxes in the ratio are scaled by the same amount.
+However, $N_\text{r}$ varies greatly for different GCE fluxes, especially in the power law case.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.49\textwidth]{figs/power-law-mult.pdf}
+    \includegraphics[width=0.49\textwidth]{figs/power-law-alpha-mult.pdf}
+    \includegraphics[width=0.49\textwidth]{figs/log-normal-mult.pdf}
+    \caption{$N_\text{r}$ and $R_\text{r}$ for each luminosity function, with results for $N_\text{r}=47$ constraint shown for Fermilab gNFW's, Abazajian's, and Ajello's estimates of the GCE spectrum.}
+    \label{fig:multiple-fluxes}
+\end{figure}
+
+\comment{It would probably be nice to have a table showing $N_\text{r}$ and $N_\text{GCE}$ as well.}
+
+\subsection{Smoothed sensitivity model}
+
+\subsection{Flux distribution}
+Until this point, we have compared predictions for the population of point source in the GC to observations only through the number and flux of resolved point sources.
+We may expand this analysis by comparing the flux distribution of point source population as well.
+
+Figure \ref{fig:flux-distro-fix-count} shows the flux distribution of the four luminosity functions with the number of resolvable point sources fixed at 47, which is the number we observed.
+The distributions are superimposed on the observed flux distribution of the 47 sources as obtained from the 4FGL catalog \cite{Fermi-LAT:2019yla}, as well as the flux distribution with the 0.53$^\circ$ cut (see section \ref{sec:observables}).
+Figure \ref{fig:flux-distro-fix-flux} requires each model to reproduce the total flux of the GCE, allowing the aggregate number of resolved point sources to vary.
+These histograms are calculated with the position-dependent sensitivity model.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{figs/flux-distro-fix-count.pdf}
+        \caption{Each luminosity function is forced to reproduce 47 sources, which is the observed number}
+        \label{fig:flux-distro-fix-count}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.47\textwidth}
+        \includegraphics[width=\textwidth]{figs/flux-distro-fix-flux.pdf}
+        \caption{Each luminosity function is forced to reproduce the flux of the GCE}
+        \label{fig:flux-distro-fix-flux}
+    \end{subfigure}
+    \caption{Distribution of resolved sources predicted by each luminosity function compared to observed distribution, where observed point sources are allowed to be within 0.3$^\circ$ of spatial peaks in the GCE flux (gray histogram) and 0.53$^\circ$ (black histogram).}
+\end{figure}
+
+The total GCE flux yielded by the luminosity functions shown in figure \ref{fig:flux-distro-fix-count} which are forced to reproduce the number of observed sources is shown in table \ref{tab:rescaled-gce-flux}.
+
+\begin{table}
+    \centering
+    \begin{tabular} {|l|c|c|}
+        \hline
+        Luminosity function & $F_\text{GCE}^\text{hyp}\ (\SI{}{\erg\per\second})$ & $F^\text{hyp}_\text{GCE} / F^\text{obs}_\text{GCE}$\\ \hline \hline
+        Power law & $\num{3.49e-09}$ & $\num{2.69}$\\
+        Log normal globular cluster & $\num{7.91e-10}$ & $\num{0.61}$ \\
+        Log normal GCE & $\num{4.66e-09}$ & $\num{3.60}$\\
+        NPTF & $\num{8.29e-09}$ & $\num{6.40}$\\
+        \hline
+    \end{tabular}
+    \caption{Total GCE flux ($F_\text{GCE}^\text{hyp}$) required by each luminosity function to yield 47 observed forces, and the ratio of that flux to the observed GCE flux $F_\text{GCE}^\text{obs}$ for comparison.}
+    \label{tab:rescaled-gce-flux}
+\end{table}
 
 \section{Future Sensitivity}
+We simulate an increase in sensitivity of GCE measurements by reusing the same $F_\text{th}(b, \ell)$ sensitivity map (figure \ref{fig:sensitivity}) as the one provided by the Fermi-LAT team, but with an overall multiplicative decrease.
+In particular, we study cases where the sensitivity is decreased by a factor of two, five, and ten and reproduce the analysis found earlier in the paper.
+Plots of $N_\text{r}$ for different parameterizations of the power law and log normal luminosity functions are given in figure \ref{fig:sensitivity-plots}, and values for $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for specific parameterizations are given in table \ref{tab:sensitivity-values}.
+Of course, the number of sources in the GCE does not depend on \textit{Fermi} sensitivity and will not change.
+\comment{That means that the backgrounds of the column plots do not change from plot to plot.
+I could put them all on the same thing.}
+
+\begin{figure}
+\centering
+    \begin{subfigure}[h]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{figs/power-law-sensitivity.pdf}
+        \caption{Power law}
+        \label{fig:sens-power-law}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[h]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{figs/power-law-alpha-sensitivity.pdf}
+        \caption{Power law alpha}
+        \label{fig:sens-power-law-alpha}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[h]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{figs/log-normal-sensitivity.pdf}
+        \caption{Log normal}
+        \label{fig:sens-log-normal}
+    \end{subfigure}
+    \caption{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ calculations generated for parameterizations of a power law luminosity function (left two plots) and log normal (bottom plots), for a position-dependent sensitivity model.
+The top three plots correspond to the current sensitivity of the \textit{Fermi} telescope (the same as figure \ref{fig:position-dependent}), while the second row assumes that the flux threshold $F_\text{th}(b, \ell)$ has been reduced by a factor of two at all points in the region of interest.
+The third row assumes a five times decrease and the second row assumes a ten times decrease.}
+    \label{fig:sensitivity-plots}
+\end{figure}
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|c|c|}
+        \hline
+        Luminosity function & $N_\text{r}$ & $R_\text{r}$\\ \hline \hline
+        Observation & 47 & \\ \hline
+        Power law & 115 & $\num{8.14e6}$ \\
+        Log normal, GCL & 0.910 & 638 \\
+        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
+        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
+        DISK NPTF & 208 & $\num{2.73e4}$ \\
+        \hline \hline
+        Power law & 115 & $\num{8.14e6}$ \\
+        Log normal, GCL & 0.910 & 638 \\
+        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
+        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
+        DISK NPTF & 208 & $\num{2.73e4}$ \\
+        \hline \hline
+        Power law & 115 & $\num{8.14e6}$ \\
+        Log normal, GCL & 0.910 & 638 \\
+        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
+        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
+        DISK NPTF & 208 & $\num{2.73e4}$ \\
+        \hline \hline
+        Power law & 115 & $\num{8.14e6}$ \\
+        Log normal, GCL & 0.910 & 638 \\
+        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
+        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
+        DISK NPTF & 208 & $\num{2.73e4}$ \\
+        \hline
+    \end{tabular}
+    \caption{Number of resolved point sources and total number of point sources predicted to make up the GCE based on four luminosity functions and the requirement that the point sources reproduce the entire flux of the GCE.
+The top row indicates the current \textit{Fermi} sensitivity, the second a twofold increase in $F_\text{th}(b, \ell)$, the third a fivefold increase, and the last a tenfold increase.}
+    \label{tab:sensitivity-values}
+\end{table}
 

### 2021-06-18 compare-spectra/make-example.py

@@ -25,7 +25,8 @@ f.label_axes(ax)
 ax.plot([], [], color='C1', linestyle='--', label="Calore fit")
 ax.plot([], [], color='C2', linestyle='-.', label="Power law fit")
 
+plt.title("")
 fig.tight_layout()
-fig.savefig("example.pdf")
 ax.legend()
+fig.savefig("example.pdf")
 plt.show()

### 2021-06-18 compare-spectra/numerical-integration.py

@@ -75,14 +75,6 @@ while None in fit_fluxes:
     #del num_fluxes[index]
     #del names[index]
 
-while None in num_fluxes:
-    index = num_fluxes.index(None)
-    num_fluxes[index] = 0
-    #del fit_fluxes[index]
-    #del calore_fluxes[index]
-    #del num_fluxes[index]
-    #del names[index]
-
 x = np.arange(len(fit_fluxes))
 width = 0.25
 hist_fig, hist_ax = plt.subplots()
@@ -90,7 +82,7 @@ hist_ax.bar(x, num_fluxes, width, label="Numerical")
 hist_ax.bar(x + width, calore_fluxes, width, label="Calore", hatch='////', linewidth=0.5)
 hist_ax.bar(x + 2 * width, fit_fluxes, width, label="Power law", hatch='\\\\\\\\', linewidth=0.5)
 hist_ax.legend()
-hist_ax.set_ylabel(f.get_y_label())
+hist_ax.set_ylabel("$F_\\mathrm{GCE}$ [erg / cm$^2$ / s]")
 hist_ax.set_xticks(x + width)
 hist_ax.set_xticklabels(names, rotation=30)
 hist_fig.tight_layout()

### 2021-06-18 compare-spectra/parse_spectrum.py

@@ -184,12 +184,11 @@ class Spectrum:
     def get_numerical_flux(self, l_min, l_max):
         log_min = np.log10(l_min * ERGS_PER_GEV)
         log_max = np.log10(l_max * ERGS_PER_GEV)
-        if log_min < self.pointsx[0] or log_max > self.pointsx[-1]:
-            print("Integration out of range")
-            print(self.pointsx[0], self.pointsx[-1])
-            print(log_min, log_max)
-            return
-
+        if log_min < self.pointsx[0]:
+            # Treat all points outside the data as zero flux.
+            log_min = self.pointsx[0]
+        if log_max > self.pointsx[-1]:
+            log_max = self.pointsx[-1]
         # Trapezoidal integration
         integral = 0
         i = 0
@@ -220,7 +219,7 @@ class Spectrum:
                 thisy.append(y)
                 up_err.append(u-y)
                 down_err.append(y-d)
-        ax.errorbar(thisx, thisy, yerr=[up_err, down_err], color=color, linestyle='none')
+        ax.errorbar(thisx, thisy, yerr=[up_err, down_err], color=color, linestyle='none', elinewidth=1)
         ax.set_title(self.get_name())
         ax.set_yscale("log")
 
@@ -245,7 +244,7 @@ class Spectrum:
                 up_err.append(u-y)
                 down_err.append(y-d)
         ax.errorbar(thisx, thisy, yerr=[up_err, down_err], color=color,
-            linestyle='none')
+            linestyle='none', elinewidth=1)
         ax.set_title(self.get_name())
         ax.set_yscale("log")
 

### 2021-06-18 gautam/fit.py

@@ -16,15 +16,16 @@ def get_data(filename):
     return np.asarray(xs), np.asarray(ys)
 
 def power_law(x, c, alpha, lmax):
-    return np.log10(c * (10**x)**(-alpha) * np.exp(-10**x / lmax))
+    return np.log10(c * (10**x)**(-alpha) * np.exp(-10.0**x / lmax))
 
 def log_normal(x, c, l0, sigma):
     return np.log10(c/10**x * np.exp(-(x - np.log10(l0))**2 / (2 * sigma**2)))
 
 def fit_power_law(filename, color):
     datax, datay = get_data(filename)
-    params = optimization.curve_fit(power_law, datax, datay, (1, 1, 1))[0]
+    params = optimization.curve_fit(power_law, datax, datay, (1, 1, 1e-11))[0]
     fity = power_law(datax, params[0], params[1], params[2])
+    print("Power law", params)
     plt.plot(datax, fity, linestyle='dashed', c=color)
     plt.plot(datax, datay, c=color)
     return params[1], params[2]
@@ -32,6 +33,7 @@ def fit_power_law(filename, color):
 def fit_log_normal(filename, color):
     datax, datay = get_data(filename)
     params = optimization.curve_fit(log_normal, datax, datay, (1, 1, 1))[0]
+    print("Log normal", params)
     fity = log_normal(datax, params[0], params[1], params[2])
     plt.plot(datax, fity, linestyle='dotted', c=color)
     plt.plot(datax, datay, c=color)

### 2021-06-18 luminosity-models-position/graph-log-normal.py

@@ -6,7 +6,7 @@ import numpy as np
 
 from matplotlib.lines import Line2D
 
-plt.style.use('revtex-presentation')
+plt.style.use('jcap')
 
 
 PLOT_SIZE = 50
@@ -19,7 +19,7 @@ lOPowerStep = (L_0_RANGE[1] / L_0_RANGE[0]) ** (1.0 / PLOT_SIZE)
 
 NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=1/5.0
-TOTAL_FLUX = 7.494712733226778e-10
+TOTAL_FLUX = 1.2953417255755896e-09#7.494712733226778e-10
 
 DRAW_EXTRA_CONTOURS = False
 LINE_COLOR = "C1"
@@ -28,7 +28,8 @@ DRAW_PLOEG_POINT = True
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
 
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/log-normal/"
+PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-"\
+ + str(MULTIPLIER) + "x/log-normal/"
 SHADE_SCALE=25
 
 def shade(field, threshold, xs, ys, off=False):
@@ -100,20 +101,20 @@ c1 = plt.contourf(xVals, yVals, totalNum,
                    vmax=max([max(v) for v in totalNum])), cmap='Greys_r')
 
 cbar = plt.colorbar(c1, extend='max')
-cbar.set_label("$N$")
+cbar.set_label("$N_\\textrm{GCE}$")
 
 
 # Greens
 if(DRAW_EXTRA_CONTOURS):
-    plt.contour(xVals, yVals, numSeen, [10*i for i in range(1, 10)], 
-        colors=[(0, i/10.0, 0, 1) for i in range(1, 10)], linewidths=1)
-plt.contour(xVals, yVals, numSeen, [NUM_PULSARS_ABOVE_THRESHOLD], colors=[LINE_COLOR], linewidths=2)
+    plt.contour(xVals, yVals, numSeen, [10*i for i in range(1, 10)],
+        colors=[(0, i/10.0, 0, 1) for i in range(1, 10)])
[…]

### 2021-06-18 luminosity-models-position/graph-power-law-alpha.py

@@ -5,7 +5,7 @@ import matplotlib.colors as colors
 from matplotlib.lines import Line2D
 import numpy as np
 
-plt.style.use('revtex')
+plt.style.use('jcap')
 
 
 PLOT_SIZE = 50
@@ -17,30 +17,16 @@ maxPowerStep = (L_MAX_RANGE[1] / L_MAX_RANGE[0]) ** (1.0 / PLOT_SIZE)
 
 MULTIPLIER = 1
 
-paperPoint = [1e35, 1e29]
+paperPoint = [1.94, 1e35]
 
 NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=0.2
-TOTAL_FLUX = 7.494712733226778e-10
+TOTAL_FLUX = 1.2953417255755896e-09#7.494712733226778e-10
 
 DRAW_EXTRA_CONTOURS = False
-LINE_COLOR = (0.8, 0.3, 0.1)
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/power-law-alpha/"
-SHADE_SCALE=25
-
-def shade(field, threshold, xs, ys, off=False):
-    px = []
-    py = []
-    for x in range(0 if off else 1, SHADE_SCALE, 1):
-        inx = int(float(x) / SHADE_SCALE * field.shape[1])
-        for y in range(0 if off else 1, SHADE_SCALE, 1):
-            iny = int(float(y) / SHADE_SCALE * field.shape[0])
-            if field[iny][inx] < threshold:
-                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
-                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
-                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
-                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
+LINE_COLOR = "C2"
+PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-"\
++str(MULTIPLIER)+"x/power-law-alpha/"
 SHADE_SCALE=25
 
[…]

### 2021-06-18 luminosity-models-position/graph-power-law.py

@@ -1,17 +1,10 @@
-''' Things to check:
-    Is the NFW profile a number density?
-    What is r_s from the Fermilab paper?
-    I should integrate the square of the NFW profile, not square the integral, right?
-    Am I using the number position distribution and luminosity position distribution in the correct places?
-'''
-
 from matplotlib import pyplot as plt
 import matplotlib.colors as colors
 from math import log
 import numpy as np
 from matplotlib.lines import Line2D
 
-plt.style.use('revtex-presentation')
+plt.style.use('jcap')
 
 
 PLOT_SIZE = 50
@@ -28,11 +21,12 @@ paperPoint = [1e35, 1e29]
 
 NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=0.2
-TOTAL_FLUX = 7.494712733226778e-10
+TOTAL_FLUX = 1.2953417255755896e-09#7.494712733226778e-10
 
 DRAW_EXTRA_CONTOURS = False
 LINE_COLOR ="C0"
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/power-law/"
+PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-" \
++str(MULTIPLIER) + "x/power-law/"
 SHADE_SCALE=25
 
 def shade(field, threshold, xs, ys, off=False):
@@ -48,7 +42,6 @@ def shade(field, threshold, xs, ys, off=False):
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
     plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
-SHADE_SCALE=25
 
 # ========================== Load data ===========================
 
@@ -99,23 +92,23 @@ plt.yscale("log")
 plt.xlabel("$L_\\mathrm{max}$ [ergs / s]")
 plt.ylabel("$L_\\mathrm{min}$ [ergs / s]")
 
-c1 = plt.contourf(lMaxVals, lMinVals, totalNum, 
[…]

### 2021-06-18 luminosity-models-position/sensitivity/graph-log-normal.py

@@ -1,0 +1,139 @@
+from matplotlib import pyplot as plt
+from math import log, exp, sqrt
+from scipy.special import erfc, erf
+import matplotlib.colors as colors
+import numpy as np
+
+from matplotlib.lines import Line2D
+from mpl_toolkits.axes_grid1 import ImageGrid
+
+plt.style.use('jcap')
+
+
+PLOT_SIZE = 50
+L_0_RANGE=[1.0e30, 2.0e36]#[1.0e32, 2.0e34]
+SIGMA_L_RANGE=[0.001, 1]
+
+lOPowerStep = (L_0_RANGE[1] / L_0_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=1/5.0
+TOTAL_FLUX = 1.2953417255755896e-09#7.494712733226778e-10
+
+DRAW_EXTRA_CONTOURS = False
+LINE_COLOR = "C1"
+DRAW_PLOEG_POINT = True
+
+paperPoint = [0.88e34, 0.62]
+ploegPoint = [10**32.206, 0.70585]
+SHADE_SCALE=25
+
+def get_path(mult):
+    return "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-"\
+        + str(mult) + "x/log-normal/"
+
+def shade(ax, field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
+    ax.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
+
+# ========================== Load data ===========================
+
+
+xVals = [L_0_RANGE[0] * lOPowerStep**i for i in range(PLOT_SIZE)]
[…]

### 2021-06-18 luminosity-models-position/sensitivity/graph-power-law-alpha.py

@@ -1,0 +1,137 @@
+from matplotlib import pyplot as plt
+from math import log, exp
+from scipy.special import gammainc, gamma
+import matplotlib.colors as colors
+from matplotlib.lines import Line2D
+import numpy as np
+from mpl_toolkits.axes_grid1 import ImageGrid
+
+plt.style.use('jcap')
+
+PLOT_SIZE = 50
+
+L_MIN = 1e29
+ALPHA_RANGE = [1.1, 2.5]
+L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+maxPowerStep = (L_MAX_RANGE[1] / L_MAX_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+MULTIPLIER = 1
+
+paperPoint = [1.94, 1e35]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=0.2
+TOTAL_FLUX = 1.2953417255755896e-09#7.494712733226778e-10
+
+DRAW_EXTRA_CONTOURS = False
+LINE_COLOR = "C2"
+SHADE_SCALE=25
+
+def get_path(mult):
+    return "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-"\
+        + str(mult) + "x/power-law-alpha/"
+
+def shade(ax, field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
+    ax.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
+
+# ========================== Load data ===========================
+
+
[…]

### 2021-06-18 luminosity-models-position/sensitivity/graph-power-law.py

@@ -1,0 +1,136 @@
+from matplotlib import pyplot as plt
+import matplotlib.colors as colors
+from math import log
+import numpy as np
+from matplotlib.lines import Line2D
+from mpl_toolkits.axes_grid1 import ImageGrid
+
+plt.style.use('jcap')
+
+
+PLOT_SIZE = 50
+
+ALPHA = 1.94
+L_MIN_RANGE = [1.0e28, 1.0e34]
+L_MAX_RANGE = [1.0e34, 1.0e38]#[1.0e34, 1.0e36]
+minPowerStep = (L_MIN_RANGE[1] / L_MIN_RANGE[0]) ** (1.0 / PLOT_SIZE)
+maxPowerStep = (L_MAX_RANGE[1] / L_MAX_RANGE[0]) ** (1.0 / PLOT_SIZE)
+
+MULTIPLIER = 1
+
+paperPoint = [1e35, 1e29]
+
+NUM_PULSARS_ABOVE_THRESHOLD = 47
+FRAC_ABOVE_THRESHOLD=0.2
+TOTAL_FLUX = 1.2953417255755896e-09#7.494712733226778e-10
+
+DRAW_EXTRA_CONTOURS = False
+LINE_COLOR ="C0"
+SHADE_SCALE=25
+
+def get_path(mult):
+    return "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-"\
+        + str(mult) + "x/power-law/"
+
+def shade(ax, field, threshold, xs, ys, off=False):
+    px = []
+    py = []
+    for x in range(0 if off else 1, SHADE_SCALE, 1):
+        inx = int(float(x) / SHADE_SCALE * field.shape[1])
+        for y in range(0 if off else 1, SHADE_SCALE, 1):
+            iny = int(float(y) / SHADE_SCALE * field.shape[0])
+            if field[iny][inx] < threshold:
+                fracx = float(x) / SHADE_SCALE * field.shape[1] - inx
+                fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
+                px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
+                py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
+    ax.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
+
+# ========================== Load data ===========================
+
[…]

### 2021-06-18 luminosity-models-step/NPTF/get-estimates.py

@@ -12,7 +12,7 @@ from matplotlib import pyplot as plt
 import numpy as np
 from math import log10
 
-plt.style.use('latex')
+plt.style.use('jcap')
 
 L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47 # 3.3440751340173124e+36  # 1.893 to 11.943 GeV
 DIST_FROM_GALACTIC_CENTER_KILOPARSEC = 8.5

### 2021-06-18 luminosity-models-step/log-normal/contour-overlay.py

@@ -5,7 +5,7 @@ import matplotlib.colors as colors
 from matplotlib.lines import Line2D
 import numpy as np
 
-plt.style.use('latex')
+plt.style.use('jcap')
 
 DIM_TRIALS=100
 
@@ -17,10 +17,12 @@ powerStep =(L_0_RANGE[1] / L_0_RANGE[0])**(1/DIM_TRIALS)
 
 NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=1/5.0
-LINE_COLOR = (0.8, 0.3, 0.1)
-
-DRAW_EXTRA_CONTOURS = False
+LINE_COLOR = "C1"
+DRAW_EXTRA_CONTOURS =False
 DRAW_PLOEG_POINT = True
+
+paperPoint = [0.88e34, 0.62]
+ploegPoint = [10**32.206, 0.70585]
 SHADE_SCALE=25
 
 def shade(field, threshold, xs, ys, off=False):
@@ -35,7 +37,7 @@ def shade(field, threshold, xs, ys, off=False):
                 fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
 
 def getTotalLum(L0, sigma):
     return exp(0.5 * sigma**2 * log(10)**2) * L0
@@ -72,7 +74,7 @@ def getMinNumPulsarsInTriangle():
             n = getNumPulsars(L0, sigma)
             if(n < minSoFar or minSoFar < 0):
                 minSoFar = n
-    
+
     print("Minimum number of total pulsars in allowed triangle: ", minSoFar)
     return minSoFar
 
@@ -87,7 +89,7 @@ def getMinPulsarsWithinOneStdevOfSigma():
         sigma= SIGMA_L_RANGE[0]  + (SIGMA_L_RANGE[1]-SIGMA_L_RANGE[0]) / (DIM_TRIALS * EXTRA_DENSITY) * j
         if sigma < SHORT_SIGMA_RANGE[0] or SHORT_SIGMA_RANGE[1] < sigma:
             continue
[…]

### 2021-06-18 luminosity-models-step/power-law-alpha/contour-overlay.py

@@ -5,27 +5,27 @@ import matplotlib.colors as colors
 from matplotlib.lines import Line2D
 import numpy as np
 
-plt.style.use('latex')
+plt.style.use('jcap')
 
 POWER_STEP = 1.1 # 1 is the minimum
 
-L_EXCESS = 9.7787012e+36# 6.756e36# 6.37e36  # All units are in ergs per second
+L_EXCESS = 1.2953417255755896e-09 / 8.331593765023139e-47
 L_THRESH = 1.0e34
 L_MIN = 1e29
 ALPHA_RANGE = [1.1, 2.5]
-L_MAX_RANGE = [1.0e33, 1.0e38]#[1.0e34, 1.0e36]
+L_MAX_RANGE = [1.0e34, 1.0e38]
 
 NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=1/5.0
 
 DRAW_EXTRA_CONTOURS = False
-LINE_COLOR = (0.8, 0.3, 0.1)
+LINE_COLOR = "C2"
 SHADE_SCALE=25
 
 dimAlpha= 50
 dimMax= int(log(L_MAX_RANGE[1]/L_MAX_RANGE[0]) / log(POWER_STEP))
 
-paperPoint = [1e35, 1.94]
+paperPoint = [1.94, 1e35]
 
 def shade(field, threshold, xs, ys, off=False):
     px = []
@@ -40,7 +40,7 @@ def shade(field, threshold, xs, ys, off=False):
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
     plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
-        
+
 
 def Gamma(s, x):
     if(s < 0):
@@ -64,14 +64,6 @@ def getFracLumAboveThreshold(alpha, lMax):
     # return (lum above thresh) / totalLum
     fracAbove = Gamma(2-alpha, L_THRESH / lMax) / (Gamma(2-alpha, L_MIN / lMax))
     return fracAbove
-
-
-print("""Paper point info:
-    Coordinates: L0 = {0}, sigma = {1}
-    Total num pulsars: {2}
-    Num pulsars above threshold: {3}
[…]

### 2021-06-18 luminosity-models-step/power-law/contour-overlay.py

@@ -5,7 +5,7 @@ import matplotlib.colors as colors
 from matplotlib.lines import Line2D
 import numpy as np
 
-plt.style.use('latex')
+plt.style.use('jcap')
 
 POWER_STEP = 1.1 # 1 is the minimum
 
@@ -19,7 +19,7 @@ NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=1/5.0
 
 DRAW_EXTRA_CONTOURS = False
-LINE_COLOR = (0.8, 0.3, 0.1)
+LINE_COLOR = "C0"
 SHADE_SCALE=25
 
 dimMin= int(log(L_MIN_RANGE[1]/L_MIN_RANGE[0]) / log(POWER_STEP))
@@ -39,8 +39,7 @@ def shade(field, threshold, xs, ys, off=False):
                 fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.5)
-        
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=0.7)
 
 def Gamma(s, x):
     if(s < 0):
@@ -70,7 +69,7 @@ print("""Paper point info:
     Coordinates: L0 = {0}, sigma = {1}
     Total num pulsars: {2}
     Num pulsars above threshold: {3}
-    Fraction luminosity above threshold: {4}""".format(paperPoint[1], paperPoint[0], getNumPulsars(paperPoint[1], paperPoint[0]), 
+    Fraction luminosity above threshold: {4}""".format(paperPoint[1], paperPoint[0], getNumPulsars(paperPoint[1], paperPoint[0]),
     getNumPulsarsAboveThreshold(paperPoint[1], paperPoint[0]), getFracLumAboveThreshold(paperPoint[1], paperPoint[0])))
 
 print("Delta function values:", getNumPulsars(L_THRESH, L_THRESH*1.0001))
@@ -93,7 +92,7 @@ def getGreenYIntercept():
         else:
             lowLmin = mid
             numLow = numMid
-    
+
[…]

### 2021-06-18 multiple-flux-values/luminosity-models-position/graph-log-normal.py

@@ -6,7 +6,7 @@ import numpy as np
 
 from matplotlib.lines import Line2D
 
-plt.style.use('revtex-presentation')
+plt.style.use('jcap')
 
 
 PLOT_SIZE = 50
@@ -29,15 +29,16 @@ FRAC_ABOVE_THRESHOLD=1/5.0
 TOTAL_FLUX = 7.494712733226778e-10
 
 DRAW_EXTRA_CONTOURS = True
-LINE_COLOR = (0.8, 0.3, 0.1)
 DRAW_PLOEG_POINT = True
 
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
 SHOW_NUMBERS = False
 
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/log-normal/"
+PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/log-normal/"
 SHADE_SCALE=25
+LINE_COLOR = "C1"
+STYLES = ["solid", "dashed", "dotted", "dashdot"]
 
 def shade(field, threshold, xs, ys, off=False):
     px = []
@@ -51,7 +52,7 @@ def shade(field, threshold, xs, ys, off=False):
                 fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c='black', sizes = (20,), alpha=0.5)
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=1.0)
 
 # ========================== Load data ===========================
 
@@ -99,31 +100,28 @@ plt.ylim(bottom=SIGMA_L_RANGE[0], top=SIGMA_L_RANGE[1])
 
 plt.xscale("log")
 plt.ylabel("$\sigma$")
-plt.xlabel("$L_0$")
-plt.title("Log-normal, position-dependent")
+plt.xlabel("$L_0$ [erg / s]")
 
 if SHOW_NUMBERS:
     cols = colors.LogNorm(vmin=min([min(v) for v in totalNum]),
[…]

### 2021-06-18 multiple-flux-values/luminosity-models-position/graph-power-law-alpha.py

@@ -5,7 +5,7 @@ import matplotlib.colors as colors
 from matplotlib.lines import Line2D
 import numpy as np
 
-plt.style.use('revtex')
+plt.style.use('jcap')
 
 
 FERMILAB_GNFW_FLUX = 5.716826056794996e-10
@@ -30,11 +30,12 @@ NUM_PULSARS_ABOVE_THRESHOLD = 47
 FRAC_ABOVE_THRESHOLD=0.2
 TOTAL_FLUX =1.2953417255755896e-09
 
-DRAW_EXTRA_CONTOURS = True
-SHOW_NUMBERS = False
-LINE_COLOR = (0.8, 0.3, 0.1)
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/power-law-alpha/"
+PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/power-law-alpha/"
 SHADE_SCALE=25
+LINE_COLOR = "C2"
+STYLES = ["solid", "dashed", "dotted", "dashdot"]
+SHOW_NUMBERS = False
+DRAW_EXTRA_CONTOURS = True
 
 def shade(field, threshold, xs, ys, off=False):
     px = []
@@ -48,7 +49,7 @@ def shade(field, threshold, xs, ys, off=False):
                 fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c='k', sizes = (20,), alpha=0.5)
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=1)
 
 # ========================== Load data ===========================
 
@@ -86,9 +87,6 @@ lumSeen = np.transpose(np.stack(lumSeen, axis=0))
 
 # ========================= Display data =========================
 
-dimMin = len(totalNum)
-dimMax = len(totalNum[0])
-
[…]

### 2021-06-18 multiple-flux-values/luminosity-models-position/graph-power-law.py

@@ -1,17 +1,10 @@
-''' Things to check:
-    Is the NFW profile a number density?
-    What is r_s from the Fermilab paper?
-    I should integrate the square of the NFW profile, not square the integral, right?
-    Am I using the number position distribution and luminosity position distribution in the correct places?
-'''
-
 from matplotlib import pyplot as plt
 import matplotlib.colors as colors
 from math import log
 import numpy as np
 from matplotlib.lines import Line2D
 
-plt.style.use('revtex-presentation')
+plt.style.use('jcap')
 
 
 PLOT_SIZE = 50
@@ -39,9 +32,10 @@ TOTAL_FLUX = 7.494712733226778e-10
 
 DRAW_EXTRA_CONTOURS = True
 SHOW_NUMBERS = False
-LINE_COLOR = (0.8, 0.3, 0.1)
-PATH_TO_FILE = "C:/Users/goods/Dropbox (MIT)/GCE UROP/luminosity-models-position/data/power-law/"
+LINE_COLOR = "C0"
+PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/power-law/"
 SHADE_SCALE=25
+STYLES = ["solid", "dashed", "dotted", "dashdot"]
 
 def shade(field, threshold, xs, ys, off=False):
     px = []
@@ -55,7 +49,7 @@ def shade(field, threshold, xs, ys, off=False):
                 fracy = float(y) / SHADE_SCALE * field.shape[0] - iny
                 px.append(xs[inx] + fracx * (xs[inx+1] - xs[inx]))
                 py.append(ys[iny] + fracy * (ys[iny+1] - ys[iny]))
-    plt.scatter(px, py, marker=('|' if off else '_'), c='k', sizes = (20,), alpha=0.5)
+    plt.scatter(px, py, marker=('|' if off else '_'), c=LINE_COLOR, sizes = (20,), alpha=1)
 
 # ========================== Load data ===========================
 
@@ -103,26 +97,25 @@ fig, ax = plt.subplots(figsize=(6, 4))
 
 plt.xscale("log")
 plt.yscale("log")
[…]

### 2021-06-18 paper/figs/get-figs.py

@@ -2,7 +2,7 @@ import os, shutil
 
 ROOT = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/"
 
-f = open("fig-sources.txt", 'r')
+f = open(ROOT + "paper/figs/fig-sources.txt", 'r')
 for line in f.readlines():
     if line == '':
         continue
@@ -15,6 +15,6 @@ for line in f.readlines():
         continue
     if path[-4:] not in [".eps", ".pdf"]:
         print("WARNING: .eps or .pdf file formats are preferred")
-    shutil.copyfile(ROOT+path, "./"+name)
+    shutil.copyfile(ROOT+path, ROOT + "paper/figs/"+name)
 
 f.close()

### 2021-06-22 paper/draft.tex
Wrote more to the paper, started fitting with error bars

@@
 \DeclareSIUnit\parsec{pc}
+\DeclareSIUnit\photon{photon}
 
@@
 \section{Methods \& Datasets}
+\subsection{GCE Spacial distribution}
+We model the spacial distribution of MSPs in the GC with an NFW squared profile, to match with empirical data.
+The number density of an NFW profile is spherically symmetric, with radial density profile
+\label{sec:spacial-distro}
+\begin{equation}
+    \rho_\text{NFW}(r) \propto \parens{\frac{r}{r_s}}^{-\gamma}\parens{1 + \frac{r}{r_s}}^{-3-\gamma}
+    \label{eqn:nfw}
+\end{equation}
+where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work. Other sources occasionally use $\gamma = 1$.
+
+We allow this NFW distribution to extend over a region of interest (ROI) extending within $|\ell| < 20^\circ$ and $2^\circ < |b| < 20^\circ$, where we have cut out the Galactic disk.
+We also restrict the luminosity of the GCE to within $\SI{0.1}{\giga\electronvolt} < E_\gamma < \SI{100}{\giga\electronvolt}$.
+Both these ranges are slightly on the larger side of those commonly used in literature.
 
@@
 To fit the luminosity functions described in section \ref{sec:lum-funcs}, we will use three observables: the total flux of the GCE $F_\text{GCE}$, the ratio of the total flux to the flux visible from point sources resolved by \textit{Fermi} $R_\text{r}$, and the number of resolved point sources $N_\text{r}$.
-All of these observables will be made with reference to a region of interest (ROI) defined by $|\ell| < 20^\circ$ and $2^\circ < |b| < 20^\circ$, and we will restrict the GCE spectrum to $\SI{0.1}{\giga\electronvolt} < E_\gamma < \SI{100}{\giga\electronvolt}$.
+The first observable, $F_\text{GCE}$, is described in section \ref{sec:total-lum}, but we describe the other two observables in this section.
 
-The other two observables have been studied by \comment{Some technical name for the Fermilab team.} \cite{Zhong:2019ycb}.
+$N_\text{r}$ and $R_\text{r}$ have been studied by \comment{Some technical name for the Fermilab team.} \cite{Zhong:2019ycb}.
 The authors performed a template fit to data from Fermi-LAT to isolate spacial peaks in flux, finding 110 \comment{(I got 110; their paper says 107)} peaks within 0.3$^\circ$ of a source in the 4FGL catalog within the region of interest \cite{Abdollahi_2020}.
@@
 
-\subsection{GCE Spacial distribution}
-\begin{equation}
-    \rho_\text{NFW}(r) = \parens{\frac{r}{r_s}}^{-\gamma}\parens{1 + \frac{r}{r_s}}^{-3-\gamma}
-    \label{eqn:nfw}
-\end{equation}
-where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work. Also, $r_c = \SI{8.5}{\kilo\parsec}$
-
 \subsection{Luminosity Functions}
@@
 
+Another study by Gautam et al.
+analyzes the possibility that the hypothetical MSP population in the GCE is generated not by the Low Mass X-Ray Binary formation, but by Accretion Induced Collapse \cite{Gautam:2021wqn}.
+\comment{To distinguish between this, a definition of these two collapse methods, along with models other than an MSP model, should be put in the introduction.
+Mention the fact that the MSPs in the GCE would have to look different from that in the disk.} Their binary system model yields a numerical luminosity function for MSPs in the GC, reported as a function of flux.
+Converting to luminosity in the manner described in appendix \ref{app:lum-to-flux}, we find that a log normal distribution fits their function well, with $L_0 = \SI{3.92e+32}{\erg\per\second}$ and $\sigma = 0.937$.
+We call this model the AIC Log normal model.
+
 Finally, ref. \cite{Lee:2015fea} proposes a broken-power law luminosity function of
@@
 The paper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.34e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced.
+\comment{I will want to remove the unnormalizable one.
+When should I do it?} The luminosity-valued parameters were originally given as fluxes in $\SI{}{\photon \per \centi\meter\squared \per \second}$.
+The photon energy was calculated via appendix \ref{app:photon-energy} and the flux converted to luminosity via appendix \ref{app:lum-to-flux}.
+
 We set $L_\text{min}=\SI{1e29}{\erg\per\second}$, which is the same minimum pulsar luminosity used by ref.
@@
     \includegraphics[width=0.49\textwidth]{figs/l-lum-funcs.pdf}
+    \includegraphics[width=0.49\textwidth]{figs/l2-lum-funcs.pdf}
     \caption{\textit{Left:} Power law, GCL log normal, GCE log normal, and NPTF luminosity functions for MSPs in the GCE, vertically rescaled.
-\textit{Right:} Same plot as \textit{left} but weighted by luminosity.}
+\textit{Right:} Same plot as \textit{left} but weighted by luminosity.
+\textit{Bottom:} Same plot as above two but weighted by luminosity squared.}
     \label{fig:lum-funcs}
@@
             Log normal, GCE & 142 & 0.180 & $\num{2.58e4}$ \\
+            Log normal, AIC & 258 & 0.744 & $\num{3.87e3}$ \\
             NFW NPTF & 19.9 & 0.0136 & $\num{2.71e3}$ \\
@@
             13.4 & 0.0648 & $\num{1.91e4}$ \\
+            0 & 0 & $\num{0}$ \\
             7.48 & 0.0300 & $\num{1.97e3}$ \\
@@
         Power law & $\num{3.49e-09}$ & $\num{2.69}$\\
-        Log normal globular cluster & $\num{7.91e-10}$ & $\num{0.61}$ \\
+        Log normal GCL & $\num{7.91e-10}$ & $\num{0.61}$ \\
         Log normal GCE & $\num{4.66e-09}$ & $\num{3.60}$\\
+        Log normal AIC & $\num{0}$ & $\num{0}$ \\
         NPTF & $\num{8.29e-09}$ & $\num{6.40}$\\
@@
 \appendix
+\section{Scaling of ROIs}
+\label{sec:scale-rois}
+To establish a value for the total flux of the GCE, we draw on several analyses of the GCE spectrum in section \ref{sec:total-lum}.
+However, not all the analyses we study use the same ROI as ours.
+To convert between our ROI and others', we assume an NFW squared spacial distribution of MSPs in the GCE as discussed in section \ref{sec:spacial-distro}.
+Then we simply calculate the ratio of flux in our region of interest $F_\Omega$ to flux in another analysis's region of interest $F_{\Omega'}$ via
+\begin{equation}
+    \frac{F_{\Omega'}}{F_\Omega} = \brackets{\int_{\Omega'}d\Omega\int_0^\infty ds \rho_\text{NFW}^2 (r)}\brackets{\int_{\Omega}d\Omega\int_0^\infty ds \rho_\text{NFW}^2 (r)}^{-1}.
+    \label{eqn:roi-conversion}
+\end{equation}
+Here, $s$ represents the distance between Earth and the point of integration, and $r$ represents the galactocentric distance.
+They are related by $r^2 = s^2 + r_c^2 - 2 s r_c \cos\ell$, where $\ell$ is the Galactic longitude and $r_c$ is the distance between Earth and the center of the Galaxy, taken here to be $\SI{8.5}{\kilo\parsec}$ to be consistent with the rest of this study.
+
+The flux ratio as computed by equation \ref{eqn:roi-conversion} between our region and the same $40^\circ \times 40^\circ$ without the Galactic disk cutout is 2.10.
+Similarly, the ratio is 1.64, 1.27, 0.915, and 1.013 \comment{Wrong!} for a $30^\circ \times 30^\circ $, $20^\circ \times 20^\circ$, $10^\circ \times 10^\circ$, and $7^\circ \times 7^\circ$ respectively.
+
 \section{Conversion Between GCE Luminosity and Flux}
 \label{app:lum-to-flux}
-\comment{Copy most of this from the January summary, if I include it.}
+This analysis requires luminosity functions to be expressed as probability distributions as a function of luminosity, since they are intended to be statements solely about the GC MSP population, made without reference to the distance of observation, and therefore the flux.
+Yet several papers referenced in this study express luminosity functions as a function of flux.
+This appendix describes how the conversion to luminosity is done.
+
+As discussed in section \ref{sec:spacial-distro}, we represent the MSP population as distributed according to an NFW squared distribution with $\gamma = 1.2$.
+One way to convert a function of flux to luminosity would be to simply use the luminosity function which, when integrated over the NFW squared spacial distribution, would reproduce the observed function of flux.
+But this method would change the functional form of the luminosity function so that, for example, a luminosity function that is log normal when written in terms of flux would no longer be log normal when written in terms of luminosity.
+\comment{Is it worth devoting a whole paragraph to describing something I do not intend to do?
+I do it to avoid confusion.}
+
+So for this paper, we simply convert the flux value of every bin to a luminosity according to the following method.
+We assume that the entire population of MPSs only contains pulsars with luminosity $L$ and ask what average flux $F$ per pulsar is observed.
+Integrated over the region of interest $\Omega$, this yields a constant flux to luminosity ratio of
+\begin{equation}
+    \frac{F}{L} = \frac{1}{4\pi}\brackets{\int_{\Omega}d\Omega\int_0^\infty ds \rho_\text{NFW}^2 (r)}\brackets{\int_{\Omega}d\Omega \int_0^\infty s^2 ds \rho_\text{NFW}^2 (r)}^{-1} = \SI{1.11e-46}{\per\centi\meter\squared}.
+    \label{eqn:f-to-l}
+\end{equation}
+Here, $s$ represents the distance from Earth to the point of integration, and $r$ represents the distance from the GC to the point of integration.
+They are related by the law of cosines: $r^2 = s^2 + r_c^2 - 2s r_c \cos \ell$, where $\ell$ is the Galactic longitude.
+The numerical value reported was computed for $r_c = \SI{8.5}{\kilo\parsec}$.
+It is slightly lower than the na\"ive value of $\frac{F}{L} = \frac{1}{4\pi r_c^2} = \SI{1.16e-46}{\per\centi\meter\squared}$, which assumes that all the MSPs are at the Galactic center, and therefore does not rely on a choice of $\gamma$.
+
+\section{Calculation of photon energy}
+\label{app:photon-energy}
+The parameterization of the NPTF luminosity function of ref.
+\cite{Lee:2015fea} is given with flux units of photons per second.
+To convert this to luminosity via appendix \ref{app:lum-to-flux}, we need to find the energy of a single GCE photon.
+To do this, we fit a broken power law to the GCE spectrum found by di Mauro and described in section \ref{sec:total-lum}, defining the flux observed from photons in an energy bin of energy $E_\gamma$ and width $dE_\gamma$ as $dF = E_\gamma N(E_\gamma)dE_\gamma$.
+The function $E_\gamma N(E_\gamma)$ is plotted in figure \ref{fig:di-mauro-example}.
+The average photon energy is then calculated by
+\begin{equation}
+    \langle E_\gamma \rangle =  \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} E_\gamma N(E_\gamma) dE_\gamma} \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} N(E_\gamma) dE_\gamma}^{-1} = \SI{0}{\giga\electronvolt}.
+    \label{eqn:photon-energy}
+\end{equation}
+\comment{I'd like to finish this. Give examples of photon energy.}
 
@@
 available to maintain the same layout and spelling of the heading.
-
-\paragraph{Note added.} This is also a good position for notes added
-after the paper has been written.
 

### 2021-06-22 compare-spectra/convert-rois/convert-rois.py

@@ -1,22 +1,23 @@
 '''
 Method:
     By integrating the NFW distribution over space, I'm going to calculate
-    the number of particles present in a given ROI and divide by the 
-    number of particles present in my ROI. I will use this factor to 
+    the number of particles present in a given ROI and divide by the
+    number of particles present in my ROI. I will use this factor to
     convert fluxes, under the assumption that the flux goes like the
     number of sources.
 '''
 
 '''Convert a GCE luminosity to a flux, assuming an NFW-squared distributed
-pattern of pulsars with delta function luminosity. See Jan summary for 
+pattern of pulsars with delta function luminosity. See Jan summary for
 calculation.'''
 
 from math import pi, cos, sqrt
 
-DELTA_ANGLE = 0.01
+DELTA_ANGLE = 0.001
 DELTA_S = 0.01
 R_C=8.5
-R_S=200
+R_S=20
+INTEGRAL_LIMIT=100
 
 def NFWSquared(r, gamma):
     return ((r/R_S)**(-gamma) * (1 + r/R_S)**(-3+gamma))**2
@@ -32,7 +33,7 @@ def calculateIntegral(maxB, minB, maxL, gamma):# Give angles in units of degrees
             continue
         while l < maxL * pi / 180.0:
             s=0
-            while s < 2*R_S:
+            while s < INTEGRAL_LIMIT:
                 r = sqrt(R_C*R_C + s * s - 2 * R_C * s * cos(b) * cos(l))
                 integral += NFWSquared(r, gamma) * volumeElement
                 s += DELTA_S
@@ -43,9 +44,16 @@ def calculateIntegral(maxB, minB, maxL, gamma):# Give angles in units of degrees
 my_ROI = calculateIntegral(20, 2, 20, 1.2)
 my_ROI_Abazajian = calculateIntegral(20, 2, 20, 1.0)
 square_ROI = calculateIntegral(20, 0, 20, 1.2)
-small_ROI = calculateIntegral(3.5, 0, 3.5, 1.2) 
+fifteen_ROI = calculateIntegral(15, 0, 15, 1.2)
+ten_ROI = calculateIntegral(10, 0, 10, 1.2)
+five_ROI = calculateIntegral(5, 0, 5, 1.2)
+small_ROI = calculateIntegral(3.5, 0, 3.5, 1.2)
[…]

### 2021-06-22 fit-functions/fit.py

@@ -1,0 +1,166 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from lmfit import Model, Parameter, report_fit
+import scipy.optimize as optimization
+
+plt.style.use("jcap")
+
+LUM_TO_FLUX = 1.1093417307914119e-46
+NUM_POINTS = 100
+
+def power_law(x, c, alpha, lmax):
+    return np.log10(c * (10**x)**(-alpha) * np.exp(-10.0**x / lmax))
+
+def log_normal(x, c, l0, sigma):# log(dN/dE)
+    return np.log10(c/10**x * np.exp(-(x - np.log10(l0))**2 / (2 * sigma**2)))
+
+def sci_not(i):
+    if i == None:
+        return "None"
+    if i == np.nan:
+        return "NaN"
+    if i == 0:
+        return "0"
+    negative = False
+    if i < 0:
+        negative = True
+        i *= -1
+    d = int(np.log10(i))
+    if np.log10(i) < 0: d -= 1
+    if not negative:
+        return str(round(i / 10**d, 3)) + "e"+str(d)
+    return "-"+str(round(i / 10**d, 3)) + "e"+str(d)
+
+class Data:
+    def __init__(self, name, filename, bar_bottom, bar_top, convert_x_to_log=False,
+        convert_y_to_log=False, convert_to_flux=False, convert_to_ergs=False):
+
+        self.name = name
+        xs, ys = self.get_data(filename, convert_x_to_log,
+            convert_y_to_log, convert_to_flux, convert_to_ergs)
+        xdown, ydown = self.get_data(bar_bottom, convert_x_to_log,
+            convert_y_to_log, convert_to_flux, convert_to_ergs)
+        xup, yup = self.get_data(bar_top, convert_x_to_log,
+            convert_y_to_log, convert_to_flux, convert_to_ergs)
+        min_x = max(np.min(xs), np.min(xdown), np.min(xup))
+        max_x = min(np.max(xs), np.max(xdown), np.max(xup))
+        if min_x >= max_x:
+            raise Exception("Bars and points share no common domain")
+        self.xs = np.linspace(min_x, max_x, 100)
+        self.ys = np.asarray([self.at(x, xs, ys) for x in self.xs])
+        self.ydown = self.ys - np.asarray([self.at(x, xdown, ydown)
+            for x in self.xs])
+        self.yup = np.asarray([self.at(x, xup, yup) for x in self.xs]) - self.ys
[…]

### 2021-06-22 gautam/fit.py

@@ -1,54 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import lmfit
-import scipy.optimize as optimization
-
-def get_data(filename):
-    xs = []
-    ys = []
-    f = open(filename, 'r')
-    for line in f.readlines():
-        if line == '':
-            continue
-        x, y = line.split(', ')
-        xs.append(float(x))
-        ys.append(float(y))
-    return np.asarray(xs), np.asarray(ys)
-
-def power_law(x, c, alpha, lmax):
-    return np.log10(c * (10**x)**(-alpha) * np.exp(-10.0**x / lmax))
-
-def log_normal(x, c, l0, sigma):
-    return np.log10(c/10**x * np.exp(-(x - np.log10(l0))**2 / (2 * sigma**2)))
-
-def fit_power_law(filename, color):
-    datax, datay = get_data(filename)
-    params = optimization.curve_fit(power_law, datax, datay, (1, 1, 1e-11))[0]
-    fity = power_law(datax, params[0], params[1], params[2])
-    print("Power law", params)
-    plt.plot(datax, fity, linestyle='dashed', c=color)
-    plt.plot(datax, datay, c=color)
-    return params[1], params[2]
-
-def fit_log_normal(filename, color):
-    datax, datay = get_data(filename)
-    params = optimization.curve_fit(log_normal, datax, datay, (1, 1, 1))[0]
-    print("Log normal", params)
-    fity = log_normal(datax, params[0], params[1], params[2])
-    plt.plot(datax, fity, linestyle='dotted', c=color)
-    plt.plot(datax, datay, c=color)
-    return params[1], params[2]
-
-plt.plot([], [], linestyle='dashed', c='black', label='power law fit')
-plt.plot([], [], linestyle='dotted', c='black', label="log normal fit")
-plt.legend()
-
-fit_power_law("blue.csv", color='C0')
-fit_power_law("orange.csv", color='C1')
-fit_log_normal("blue.csv", color='C0')
-fit_log_normal("orange.csv", color='C1')
-plt.xlabel("log10(F/(ergs/s/cm^2))")
-plt.ylabel("unknown")
-
-plt.savefig("fit results.png")
-plt.show()

### 2021-06-22 luminosity-models-position/calc.cpp

@@ -529,7 +529,7 @@ void generatePowerLawPlotMap(VALUE value, DoubleVector* plotMap) {
         }
     }
 
-#else 
+#else
     for (int i = 0; i < PLOT_SIZE; i++) {
         double lMin = L_MIN_RANGE[0] * pow(powerSteps.first, i);
         std::vector<std::future<double>*> futures(PLOT_SIZE, nullptr);
@@ -564,7 +564,7 @@ void generatePowerLawAlphaPlotMap(VALUE value, DoubleVector* plotMap) {
         }
     }
 
-#else 
+#else
     std::cout << "Unimplemented" << std::endk;
     throw "Unimplemented";
 #endif
@@ -586,7 +586,7 @@ void generateLogNormalPlotMap(VALUE value, DoubleVector* plotMap) {
         }
     }
 
-#else 
+#else
     for (int i = 0; i < PLOT_SIZE; i++) {
         double l0 = L0_RANGE[0] * pow(powerSteps.first, i);
         std::vector<std::future<double>*> futures(PLOT_SIZE, nullptr);
@@ -835,7 +835,7 @@ int nptf() {
     std::future<double> totalFlux = std::async(std::launch::async, getValueAtConfig, VALUE::TOTAL_FLUX, -0.66, 18.2);
     std::future<double> totalNum = std::async(std::launch::async, getValueAtConfig, VALUE::TOTAL_NUM, -0.66, 18.2);
     std::future<double> seenFlux = std::async(std::launch::async, getValueAtConfig, VALUE::SEEN_FLUX, -0.66, 18.2);
-    std::future<double> seenNum = std::async(std::launch::async, getValueAtConfig, VALUE::SEEN_NUM, -0.66, 18.2);    
+    std::future<double> seenNum = std::async(std::launch::async, getValueAtConfig, VALUE::SEEN_NUM, -0.66, 18.2);
 
     double nptfScale = FLUX_EXCESS / totalFlux.get();
     double totalNumScaled = totalNum.get() * nptfScale;

### 2021-06-22 luminosity-models-position/graph-log-normal.py

@@ -27,6 +27,7 @@ DRAW_PLOEG_POINT = True
 
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
+gautamPoint = [3.91983577e+32, 0.937184991]
 
 PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-"\
  + str(MULTIPLIER) + "x/log-normal/"
@@ -116,8 +117,9 @@ if(DRAW_EXTRA_CONTOURS):
         colors=[(1, i/10.0, 1-i/10.0, 1) for i in range(1, 10)])
 plt.contour(xVals, yVals, lumSeen, [FRAC_ABOVE_THRESHOLD], colors=[LINE_COLOR], linestyles='dashed')
 
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^')
-#plt.scatter(minPoint[0], minPoint[1], c='cyan')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^', markersize=6)
+plt.plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="fuchsia", marker='s', markersize=6)
+plt.plot(gautamPoint[0], gautamPoint[1], markeredgecolor='black', markerfacecolor="red", marker='*', markersize=8)
 
 # Observation
 shade(numSeen, NUM_PULSARS_ABOVE_THRESHOLD, xVals, yVals)
@@ -126,14 +128,13 @@ shade(lumSeen, FRAC_ABOVE_THRESHOLD, xVals, yVals, True)
 
 # Final points
 
-if DRAW_PLOEG_POINT:
-    plt.plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="C6", marker='s')
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR),
                 Line2D([0], [0], color=LINE_COLOR, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^', linestyle='None'),
-                Line2D([], [], markeredgecolor='black', markerfacecolor="C6", marker='s', linestyle='None'),]
[…]

### 2021-06-22 luminosity-models-position/graph-power-law-alpha.py

@@ -117,11 +117,11 @@ shade(lumSeen, FRAC_ABOVE_THRESHOLD, alphaVals, lMaxVals, True)
 
 # Final points
 
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR),
                 Line2D([0], [0], color=LINE_COLOR, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None', markersize=6),]
 plt.legend(custom_lines, ["$N_r=47$", "$R_r=0.2$", "Fermilab point"], loc='lower right')
 plt.xlim(alphaVals[0], alphaVals[-1])
 plt.ylim(lMaxVals[0], lMaxVals[-1])

### 2021-06-22 luminosity-models-position/graph-power-law.py

@@ -117,11 +117,11 @@ shade(lumSeen, FRAC_ABOVE_THRESHOLD, lMaxVals, lMinVals, True)
 
 # Final points
 
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR),
                 Line2D([0], [0], color=LINE_COLOR, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None', markersize=6),]
 plt.legend(custom_lines, ["$N_r=47$", "$R_r=0.2$", "Fermilab point"], loc='lower right')
 plt.xlim(lMaxVals[0], lMaxVals[-1])
 plt.ylim(lMinVals[0], lMinVals[-1])

### 2021-06-22 luminosity-models-step/log-normal/contour-overlay.py

@@ -23,6 +23,7 @@ DRAW_PLOEG_POINT = True
 
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
+gautamPoint = [3.91983577e+32, 0.937184991]
 SHADE_SCALE=25
 
 def shade(field, threshold, xs, ys, off=False):
@@ -109,27 +110,20 @@ def getMinPulsarsWithinOneStdevOfSigma():
     print("Fewest possible pulsars required to hit the green line with sigma in 1 stdev of paper values: {0} at coordinates L_0={1}, sigma={2}".format(minPulsars, minL0, minSigma))
     return (minL0, minSigma)
 
-def getPaperPointInfo(L0 = paperPoint[0], sigma = paperPoint[1]):
-    print("""Paper point info:
-    Coordinates: L0 = {0}, sigma = {1}
-    Total num pulsars: {2}
-    Num pulsars above threshold: {3}
-    Fraction luminosity above threshold: {4}""".format(L0, sigma, getNumPulsars(L0, sigma),
-    getNumPulsarsAboveThreshold(L0, sigma), getFracLumAboveThreshold(L0, sigma)))
-
-def getPloegPointInfo(L0, sigma):
-    print("""Ploeg point info:
-    Coordinates: L0 = {0}, sigma = {1}
-    Total num pulsars: {2}
-    Num pulsars above threshold: {3}
-    Fraction luminosity above threshold: {4}""".format(L0, sigma, getNumPulsars(L0, sigma),
+def getPaperPointInfo(name, L0 = paperPoint[0], sigma = paperPoint[1]):
+    print("""{0} point info:
+    Coordinates: L0 = {1}, sigma = {2}
+    Total num pulsars: {3}
+    Num pulsars above threshold: {4}
+    Fraction luminosity above threshold: {5}""".format(name, L0, sigma, getNumPulsars(L0, sigma),
     getNumPulsarsAboveThreshold(L0, sigma), getFracLumAboveThreshold(L0, sigma)))
 
 
 getMinNumPulsarsInTriangle()
 minPoint = getMinPulsarsWithinOneStdevOfSigma()
-getPaperPointInfo()
-getPloegPointInfo(ploegPoint[0], ploegPoint[1])
+getPaperPointInfo("Paper (GCL)")
[…]

### 2021-06-22 luminosity-models-step/power-law-alpha/contour-overlay.py

@@ -131,11 +131,11 @@ shade(fracAboveThreshold, FRAC_ABOVE_THRESHOLD, alphaVals, lMaxVals, True)
 
 
 
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR),
                 Line2D([0], [0], color=LINE_COLOR, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None', markersize=6),]
 plt.legend(custom_lines, ["$N_r=47$", "$R_r=0.2$", "Fermilab point"], loc='lower right')
 plt.xlim(alphaVals[0], alphaVals[-1])
 plt.ylim(lMaxVals[0], lMaxVals[-1])

### 2021-06-22 luminosity-models-step/power-law/contour-overlay.py

@@ -163,11 +163,11 @@ shade(fracAboveThreshold, FRAC_ABOVE_THRESHOLD, lMaxVals, lMinVals, True)
 
 
 # Final points
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR),
                 Line2D([0], [0], color=LINE_COLOR, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None', markersize=6),]
 plt.legend(custom_lines, ["$N_r=47$", "$R_r=0.2$", "Fermilab point"], loc='lower right')
 plt.xlim(lMaxVals[0], lMaxVals[-1])
 plt.ylim(lMinVals[0], lMinVals[-1])

### 2021-06-22 plot-functions/plotter.py

@@ -29,6 +29,8 @@ L0_LOG_NORMAL = 8.8e33
 SIGMA_LOG_NORMAL = 0.62
 L0_PLOEG_FIT = 1.61e32
 SIGMA_PLOEG_FIT = 0.700
+L0_GAUTAM_FIT = 3.91983577e+32
+SIGMA_GAUTAM_FIT = 0.937184991
 N_BELOW_NFW = -0.66
 N_ABOVE_NFW = 18.2
 L_BREAK_NFW = 1.76e-10 * ERGS_PER_PHOTON * 4 * pi * (DIST_TO_CENTER * DIST_TO_CENTER * CM_PER_KPC_SQUARED)
@@ -49,7 +51,7 @@ def nptf(x, n1, n2, LBreak):
 
 fig, ax1=plt.subplots()
 
-ax1.set_xlabel("Luminosity $L$ [ergs/s]")
+ax1.set_xlabel("Luminosity $L$ [erg / s]")
 ax1.set_ylabel("$\\frac{dN}{dL}$")
 ax1.set_xscale('log')
 
@@ -57,12 +59,12 @@ x = 10**np.linspace(PLOT_LOG_MIN, PLOT_LOG_MAX, NUM_PLOT_POINTS)
 
 ax2 = ax1.twiny()
 
-ax2.set_xlabel("Flux $F$ [ergs/cm$^2$/s]")
+ax2.set_xlabel("Flux $F$ [erg / cm$^2$ / s]")
 
 def convert_ax2(ax1):
     x1, x2 = ax1.get_xlim()
     ax2.set_xlim(x1 * LUM_TO_FLUX, x2 * LUM_TO_FLUX)
-    ax2.figure.canvas.draw()    
+    ax2.figure.canvas.draw()
 
 ax1.callbacks.connect("xlim_changed", convert_ax2)
 
@@ -70,17 +72,18 @@ ys = [
     powerLaw(x, L_MIN, L_MAX, ALPHA),
     logNormal(x, L0_LOG_NORMAL, SIGMA_LOG_NORMAL),
     logNormal(x, L0_PLOEG_FIT, SIGMA_PLOEG_FIT),
+    logNormal(x, L0_GAUTAM_FIT, SIGMA_GAUTAM_FIT),
     [nptf(l, N_BELOW_NFW, N_ABOVE_NFW, L_BREAK_NFW) for l in x],
[…]

### 2021-06-24 paper/draft.tex
Ploeg smoothing, Gautam luminosity function, and updated paper

@@
 
-\title{\boldmath A title with some math: $x=1$}
+\title{Physical Characteristics Required of a Millisecond Pulsar Population to Reproduce the Galactic Center Excess}
 
@@
 \emailAdd{jtdinsmo@mit.edu}
-\emailAdd{tslater@mit.edu}
+\emailAdd{tslatyer@mit.edu}
 
@@
 
-\abstract{Abstract...}
+\abstract{An excess of gamma rays emanating from the Galactic Center has been discovered and proven to be robust.
+One proposed solution is the presence of a large number of unresolved millisecond pulsars in the Galactic Center.
+We analyze the number of pulsars required for such a population to reproduce the GCE, and compare the predicted number of resolvable pulsars and the amount and distribution of flux emitted by those resolvable pulsars to observations.
+We predicate these calculations on luminosity functions discussed in literature and demonstrate which luminosity functions are excluded by observations.
+We conclude with an analysis of the capacity of future increases in observational sensitivity to rule out more luminosity functions.}
 
@@
 \section{Introduction}
+\comment{What is the GCE?}\cite{Goodenough:2009gk}
+
+\comment{What are possible explanations for the GCE? DM or MSPs. What luminosity functions might they have?}
+
+\comment{Data sources}
+
+In this paper, we extract a total flux for the GCE drawn from other analyses, and use it to calculate the total number of pulsars, number of resolved pulsars, and flux from those resolvable pulsars as predicted by various luminosity functions that have been proposed in literature.
+We indicate the luminosity functions necessary in order to meet the observational constraints imposed by a point source template fit to \textit{Fermi} data and the 4FGL catalog.
+\comment{What do we find?} We conclude with an analysis of what further luminosity function constraints could be achieved by improvements to the sensitivity of \textit{Fermi}.
 
@@
 We also restrict the luminosity of the GCE to within $\SI{0.1}{\giga\electronvolt} < E_\gamma < \SI{100}{\giga\electronvolt}$.
-Both these ranges are slightly on the larger side of those commonly used in literature.
+Both these ranges are slightly on the wider side of those commonly used in literature.
 
@@
 \label{sec:total-lum}
-Since an estimate of the total flux of the GCE is necessary for our data, we extract the total flux from several previous analyses of spectra using the following three methods and compare them.
+Since an estimate of the total flux of the GCE is necessary for our study, we extract the total flux from several previous analyses of spectra using the following three methods and compare them.
 The spectral analyses we study here are refs.
-\cite{Zhong:2019ycb, Calore:2014xka, DiMauro:2021raz, Abazajian:2014fta, Gordon, Ajello}.
+\cite{Zhong:2019ycb, Calore:2014xka, DiMauro:2021raz, Abazajian:2014fta, Gordon, Ajello:2015kwa}.
 Each reference reports the total flux $F_\gamma(E)$ observed in an energy bin centered on $E$.
+Some studies use a ROI different from ours, so we convert to our ROI using the method outlined in appendix \ref{app:roi-rescale}.
 The spectra from these sources are reported in figure \ref{fig:all-spectra}
@@
 The second sensitivity model acknowledges the effect of background flux on resolvability and uses a position-dependent flux threshold $F_\text{th}(b, l)$ published by the \textit{Fermi} team \cite{Fermi-LAT:2019yla, Ballet:2020hze} (figure \ref{fig:sensitivity}).
-\comment{Here, I could talk about how to convert between flux and luminosity and then use the mean of this map to assess how accurate 1e34 ergs/s actually is.}.
+\comment{Here, I could talk about how to convert between flux and luminosity and then use the mean of this map to assess how accurate 1e34 ergs/s actually is.
+One way would be simply to average over all the pixels in the sensitivity map and convert to luminosity.
+But isn't it better to weight the average by NFW distribution?
+In that case, I have to do a line of sight integral too, which means I can no longer use the flux to luminosity ratio in the appendix.
+It gets complicated...}.
 To calculate the four properties of GC MSP populations, we use
@@
 \begin{equation}
-    P_\text{r}(F) = \frac{1}{\sigma_\text{th} F\sqrt{2\pi}} \expp{-\frac{(\ln F - (F_\text{th}(\ell, b) - K_\text{th}))^2}{2\sigma_\text{th}^2}}
+    P_\text{r}(F) = \frac{1}{2} \parens{1 + \text{erf} \parens{\frac{\log_{10} F - (\log_{10} F_\text{th}(\ell, b) + K_\text{th})}{\sqrt{2}\sigma_\text{th}}}}
     \label{eqn:ploeg-smoothing}
@@
 \section{Results}
-\subsection{Step function and position dependent sensitivity models}
+\subsection{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for different luminosity functions}
 Using each of the luminosity functions outlined in section \ref{sec:sensitivity}, we extract the total number of resolvable point sources $N_\text{r}$, the ratio of the flux received from those resolved point sources to the total flux of the GCE $R_\text{r}$, and the total number of point sources $N_\text{GCE}$ by forcing each function to reproduce the observed flux of the GCE.
 This is done for many parameterizations of the power law and log normal luminosity functions (eqs.
-\ref{eqn:power-law} and \ref{eqn:log-normal}), with results using the step function and the position-dependent sensitivity models shown in figures \ref{fig:step-function} and \ref{fig:position-dependent} respectively.
+\ref{eqn:power-law} and \ref{eqn:log-normal}), with $N_\text{GCE}$ displayed as a contour map in figures \ref{fig:step-function} and \ref{fig:position-dependent}, using the step function and the position-dependent sensitivity models respectively.
+Regions that satisfy the observational constraints $N_\text{r} < 47$ and $R_\text{r} < 0.2$ are marked.
 
@@
 
-Also shaded in these figures is the ``allowed region'' for each luminosity function---that is, the set of parameters that yield $N_\text{r} \leq 47$ and $R_\text{r} \leq 0.2$.
-
 The analysis is also performed on the NPTF luminosity function, but only for the parameterization outlined in ref.
 \cite{Lee:2015fea} and therefore no figure is generated.
-Predictions for $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for the specific parameterizations suggested by previous works are shown in tables \ref{tab:step-function-results} and \ref{tab:position-dependent-results}.
+Predictions for $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for the specific parameterizations suggested by previous works are shown in table \ref{tab:specific-results} for all three sensitivity models.
 
@@
     \centering
-    \begin{subtable}[h]{0.55\textwidth}
-        \begin{tabular}{|l|c|c|c|}
+    \begin{subtable}[h]{\textwidth}
+        \centering
+        \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
             \hline
             Luminosity function & $N_\text{r}$ & $R_\text{r}$ & $N_\text{GCE}$\\ \hline \hline
-            Observation & 47 & 0.2 & \\ \hline
+            \textbf{Observation} & \textbf{47} & \textbf{0.2} & \\
             Power law & 115 & 0.193 & $\num{8.14e6}$ \\
@@
             DISK NPTF & 208 & 0.883 & $\num{2.73e4}$ \\
-            \hline
         \end{tabular}
@@
     \end{subtable}
-    \hfill
-    \begin{subtable}[h]{0.44\textwidth}
-        \begin{tabular}{|c|c|c|}
-            \hline
-            $N_\text{r}$ & $R_\text{r}$ & $N_\text{GCE}$\\ \hline \hline
-            47 & 0.2 & \\ \hline
-            17.6 & 0.101 & $\num{5.91e6}$ \\
-            77.5 & 0.692 & 463 \\
-            13.4 & 0.0648 & $\num{1.91e4}$ \\
-            0 & 0 & $\num{0}$ \\
-            7.48 & 0.0300 & $\num{1.97e3}$ \\
-            71.7 & 0.757 & $\num{1.98e4}$ \\
-            \hline
+
+    \vspace{2em}
+
+    \begin{subtable}[h]{\textwidth}
+        \centering
+        \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
+            Power law & 17.6 & 0.101 & $\num{5.91e6}$ \\
+            Log normal, GCL & 77.5 & 0.692 & 463 \\
+            Log normal, GCE & 13.4 & 0.0648 & $\num{1.91e4}$ \\
+            Log normal, AIC & 55.6 & 0.552 & $\num{2.81e3}$ \\
+            NFW NPTF & 7.48 & 0.0300 & $\num{1.97e3}$ \\
+            DISK NPTF & 71.7 & 0.757 & $\num{1.98e4}$ \\
         \end{tabular}
@@
     \end{subtable}
-    \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on four luminosity functions and the requirement that the point sources reproduce the entire flux of the GCE.}
+
+    \vspace{2em}
+
+    \begin{subtable}[h]{\textwidth}
+        \centering
+        \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
+            Power law & 0 & 0 & $\num{0}$ \\
+            Log normal, GCL & 0 & 0 & 0 \\
+            Log normal, GCE & 0 & 0 & $\num{0}$ \\
+            Log normal, AIC & 0 & 0 & $\num{0}$ \\
+            NFW NPTF & 0 & 0 & $\num{0}$ \\
+            DISK NPTF & 0 & 0 & $\num{0}$ \\
+            \hline
+        \end{tabular}
+        \caption{Smoothed sensitivity model}
+        \label{tab:smoothed-results}
+    \end{subtable}
+    \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE.
+For definitions of the paramterizations, see section \ref{sec:lum-funcs}.}
+    \label{tab:specific-results}
 \end{table}
@@
 
-\comment{It would probably be nice to have a table showing $N_\text{r}$ and $N_\text{GCE}$ as well.}
-
-\subsection{Smoothed sensitivity model}
+\comment{It would probably be nice to have a table showing $N_\text{r}$ and $N_\text{GCE}$ as well for different values of GCE luminosity.}
 
@@
         Log normal GCL & $\num{7.91e-10}$ & $\num{0.61}$ \\
-        Log normal GCE & $\num{4.66e-09}$ & $\num{3.60}$\\
-        Log normal AIC & $\num{0}$ & $\num{0}$ \\
+        Log normal GCE & $\num{4.57e-09}$ & $\num{3.60}$\\
+        Log normal AIC & $\num{1.10e-9}$ & $\num{0.85}$ \\
         NPTF & $\num{8.29e-09}$ & $\num{6.40}$\\
@@
 In particular, we study cases where the sensitivity is decreased by a factor of two, five, and ten and reproduce the analysis found earlier in the paper.
-Plots of $N_\text{r}$ for different parameterizations of the power law and log normal luminosity functions are given in figure \ref{fig:sensitivity-plots}, and values for $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for specific parameterizations are given in table \ref{tab:sensitivity-values}.
+Plots of $N_\text{r}$ for different parameterizations of the power law and log normal luminosity functions are given in figure \ref{fig:sensitivity}, and values for $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for specific parameterizations are given in table \ref{tab:sensitivity-values}.
 Of course, the number of sources in the GCE does not depend on \textit{Fermi} sensitivity and will not change.
@@
 
-\begin{figure}
-\centering
-    \begin{subfigure}[h]{0.32\textwidth}
-        \includegraphics[width=\textwidth]{figs/power-law-sensitivity.pdf}
-        \caption{Power law}
-        \label{fig:sens-power-law}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[h]{0.32\textwidth}
-        \includegraphics[width=\textwidth]{figs/power-law-alpha-sensitivity.pdf}
-        \caption{Power law alpha}
-        \label{fig:sens-power-law-alpha}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[h]{0.32\textwidth}
-        \includegraphics[width=\textwidth]{figs/log-normal-sensitivity.pdf}
-        \caption{Log normal}
-        \label{fig:sens-log-normal}
-    \end{subfigure}
-    \caption{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ calculations generated for parameterizations of a power law luminosity function (left two plots) and log normal (bottom plots), for a position-dependent sensitivity model.
-The top three plots correspond to the current sensitivity of the \textit{Fermi} telescope (the same as figure \ref{fig:position-dependent}), while the second row assumes that the flux threshold $F_\text{th}(b, \ell)$ has been reduced by a factor of two at all points in the region of interest.
-The third row assumes a five times decrease and the second row assumes a ten times decrease.}
-    \label{fig:sensitivity-plots}
-\end{figure}
-
 \begin{table}
     \centering
-    \begin{tabular}{|l|c|c|}
+    \begin{tabular}{|l | c c | c c | c c | c c |}
         \hline
-        Luminosity function & $N_\text{r}$ & $R_\text{r}$\\ \hline \hline
-        Observation & 47 & \\ \hline
-        Power law & 115 & $\num{8.14e6}$ \\
-        Log normal, GCL & 0.910 & 638 \\
-        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
-        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
-        DISK NPTF & 208 & $\num{2.73e4}$ \\
-        \hline \hline
-        Power law & 115 & $\num{8.14e6}$ \\
-        Log normal, GCL & 0.910 & 638 \\
-        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
-        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
-        DISK NPTF & 208 & $\num{2.73e4}$ \\
-        \hline \hline
-        Power law & 115 & $\num{8.14e6}$ \\
-        Log normal, GCL & 0.910 & 638 \\
-        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
-        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
-        DISK NPTF & 208 & $\num{2.73e4}$ \\
-        \hline \hline
-        Power law & 115 & $\num{8.14e6}$ \\
-        Log normal, GCL & 0.910 & 638 \\
-        Log normal, GCE & 0.180 & $\num{2.58e4}$ \\
-        NFW NPTF & 19.9 & $\num{2.71e3}$ \\
-        DISK NPTF & 208 & $\num{2.73e4}$ \\
+        Luminosity function & $N_\text{r}^{\times 1}$ & $R_\text{r}^{\times 1}$ & $N_\text{r}^{\times 2}$ & $R_\text{r}^{\times 2}$ & $N_\text{r}^{\times 5}$ & $R_\text{r}^{\times 5}$ & $N_\text{r}^{\times 10}$ & $R_\text{r}^{\times 10}$\\ \hline \hline
+        Power law & 17.6 & 0.101 & 45.8 & 0.157 & 137 & 0.237 & 290 & 0.298 \\
+        Log normal, GCL & 77.5 & 0.692 & 142 & 0.831 & 251 & 0.941 & 331 & 0.979 \\
+        Log normal, GCE & 13.4 & 0.0648 & 48.9 & 0.129 & 222 & 0.270 & 599 & 0.416  \\
+        Log normal, AIC & 55.6 & 0.552 & 113 & 0.670 & 256 & 0.803 & 432 & 0.878  \\
+        NFW NPTF & 7.48 & 0.0300 & 50.7 & 0.0920 & 574 & 0.480 & $\num{1.40e3}$ & 0.879 \\
+        DISK NPTF & 71.7 & 0.757 & 110 & 0.839 & 180 & 0.907 & 252 & 0.939 \\
         \hline
     \end{tabular}
-    \caption{Number of resolved point sources and total number of point sources predicted to make up the GCE based on four luminosity functions and the requirement that the point sources reproduce the entire flux of the GCE.
-The top row indicates the current \textit{Fermi} sensitivity, the second a twofold increase in $F_\text{th}(b, \ell)$, the third a fivefold increase, and the last a tenfold increase.}
+    \caption{Number of resolved point sources and ratio of resolved flux to total flux,predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE.
+The assumed sensitivity of the telescope, $F_\text{th}(\ell, b)$, has been varied by a factor of 1 (i.e., sensitivity is at its current value), 2, 5, and 10, with the factor of increase given as superscripts in the header.
+All use the position-dependent sensitivity model.
+For definitions of the paramterizations, see section \ref{sec:lum-funcs}.
+\comment{Maybe this should be a plot.}}
     \label{tab:sensitivity-values}
@@
 \appendix
-\section{Scaling of ROIs}
-\label{sec:scale-rois}
+\section{Scaling of ROIs and Spectral Ranges}
+\label{app:roi-rescale}
 To establish a value for the total flux of the GCE, we draw on several analyses of the GCE spectrum in section \ref{sec:total-lum}.

### 2021-06-24 compare-spectra/parse_spectrum.py

@@ -276,7 +276,7 @@ class Spectrum:
         ax.plot(fitx, fity, color='C2', linestyle='-.')
 
     def get_x_label(self):
-        return "$\log \\frac{E}{1\\ \\mathrm{erg}}$"
+        return "$\log \\frac{E_\\gamma}{1\\ \\mathrm{erg}}$"
 
     def get_y_label(self):
-        return "$E^2 \\frac{dN}{dE}$ [erg / cm$^2$ / s]"
+        return "$F_\\gamma$ [erg / cm$^2$ / s]"

### 2021-06-24 compare-spectra/photon-energy.py

@@ -1,30 +1,21 @@
-OLD = 0
+DI_MAURO = 0
 FERMILAB = 1
 CALORE = 2
 ERG_PER_GEV = 0.00160218
-SIZE_OF_ROI = 0.42882 # steradians
-L_BREAK = 2.06 * ERG_PER_GEV
-ALPHA_ABOVE = 2.63
-ALPHA_BELOW = 1.42
 
 TYPE = FERMILAB
 
-# The type doesn't actually matter; it doesn't come into the calcualtion
-
-SCALE = 0 # Units in erg / cm^2 / s
-if TYPE == OLD:
-    raise Exception("Old values unimplemented")
-if TYPE == FERMILAB:
-    SCALE = 25.87693692 * ERG_PER_GEV * SIZE_OF_ROI
-if TYPE == CALORE:
-    SCALE = 44.78745446 * ERG_PER_GEV * SIZE_OF_ROI
+if TYPE == FERMILAB or TYPE == CALORE:
+    L_BREAK = 2.06 * ERG_PER_GEV
+    ALPHA_ABOVE = 2.63
+    ALPHA_BELOW = 1.42
 
 def integrate(start, stop):
     topAlpha = ALPHA_ABOVE if stop > L_BREAK else ALPHA_BELOW
     bottomAlpha = ALPHA_BELOW if start < L_BREAK else ALPHA_ABOVE
     return L_BREAK / (1 - bottomAlpha) * (1 - (start / L_BREAK)**(1 - bottomAlpha)) + \
         L_BREAK / (1 - topAlpha) * ((stop / L_BREAK)**(1 - topAlpha) - 1)
-    
+
 
 def lintegrate(start, stop):
     topAlpha = ALPHA_ABOVE if stop > L_BREAK else ALPHA_BELOW
@@ -35,12 +26,13 @@ def lintegrate(start, stop):
 def getPhotonEnergy(start, stop):
     return lintegrate(start, stop) / integrate(start, stop) # Units of ergs
 
-spectrumName = "old"
 if TYPE == FERMILAB:
     spectrumName = "Fermilab"
 if TYPE == CALORE:
     spectrumName = "Calore"
+if TYPE == DI_MAURO:
+    spectrumName = "Di Mauro"
 print("Using {} spectrum".format(spectrumName))
 
[…]

### 2021-06-24 fit-functions/fit.py

@@ -33,15 +33,15 @@ def sci_not(i):
 
 class Data:
     def __init__(self, name, filename, bar_bottom, bar_top, convert_x_to_log=False,
-        convert_y_to_log=False, convert_to_flux=False, convert_to_ergs=False):
+        convert_y_to_log=False, convert_to_lum=False, convert_to_ergs=False):
 
         self.name = name
         xs, ys = self.get_data(filename, convert_x_to_log,
-            convert_y_to_log, convert_to_flux, convert_to_ergs)
+            convert_y_to_log, convert_to_lum, convert_to_ergs)
         xdown, ydown = self.get_data(bar_bottom, convert_x_to_log,
-            convert_y_to_log, convert_to_flux, convert_to_ergs)
+            convert_y_to_log, convert_to_lum, convert_to_ergs)
         xup, yup = self.get_data(bar_top, convert_x_to_log,
-            convert_y_to_log, convert_to_flux, convert_to_ergs)
+            convert_y_to_log, convert_to_lum, convert_to_ergs)
         min_x = max(np.min(xs), np.min(xdown), np.min(xup))
         max_x = min(np.max(xs), np.max(xdown), np.max(xup))
         if min_x >= max_x:
@@ -125,7 +125,7 @@ class Data:
 
 
     def get_data(self, filename, convert_x_to_log, convert_y_to_log,
-        convert_to_flux, convert_to_ergs):
+        convert_to_lum, convert_to_ergs):
 
         xs = []
         ys = []
@@ -139,8 +139,9 @@ class Data:
             if convert_x_to_log:
                 x = np.log10(x)
             if convert_y_to_log:
+                if y <= 0: continue
                 y = np.log10(y)
-            if convert_to_flux:
+            if convert_to_lum:
                 x -= np.log10(LUM_TO_FLUX)
             if convert_to_ergs:
                 raise Exception("Unimplemented")
@@ -159,8 +160,15 @@ class Data:
 
         return (ys[i+1] - ys[i]) * (x - xs[i]) / (xs[i+1] - xs[i]) + ys[i]
 
-d = Data("Gautam", "gautam/orange.csv", "gautam/bottom-band.csv", "gautam/top-band.csv",
-    convert_to_flux=True)
-print(d.fit_log_normal())
-d.plot()
[…]

### 2021-06-24 luminosity-models-position/calc.cpp

@@ -16,7 +16,9 @@ typedef std::vector<std::vector<double>> DoubleVector;
 /* When LOTS_OF_THREADS is defined, a target of 80-90 threads are made and run concurrently.
    Otherwise, four threads are made and run concurrently. */
 
-#define SENSITIVITY_DIVISOR 1.0
+#define INVALID -3789213.4812047 // A random number designed to encode an invalid input.
+
+#define SENSITIVITY_DIVISOR 5.0
 
 #define pi 3.14159265358979323
 #define ONE_PLUS_EPSILON 1.0000000001
@@ -38,6 +40,8 @@ typedef std::vector<std::vector<double>> DoubleVector;
 #define SIGMA_HIST 0.62
 #define L0_PLOEG_HIST 1.6084e+32
 #define SIGMA_PLOEG_HIST 0.7003
+#define L0_GAUTAM_HIST 3.91983577e+32
+#define SIGMA_GAUTAM_HIST 0.937184991
 #define NPTF_L_BREAK_HIST 8.656487610122969e+33
 #define NPTF_N_1_HIST -0.66
 #define NPTF_N_2_HIST 18.2
@@ -55,6 +59,7 @@ const double SIGMA_RANGE[2] = { 0.001, 1 };
 const double fermilabPaperPoint[2] = { 1e35, 1e29 };
 const double logNormalPaperPoint[2] = { 0.88e34, 0.62 };
 const double logNormalPloegPoint[2] = { 1.6084e+32, 0.7003 };
+const double logNormalGautamPoint[2] = { 3.91983577e+32, 0.937184991 };
 
 // Values for the computation of the integral of the NFW profile.
 #define GAMMA 1.2
@@ -85,6 +90,7 @@ enum class LUMINOSITY_FUNCTION {
     POWER_LAW,
     LOG_NORMAL,
     PLOEG,
+    GAUTAM,
     NPTF,
     POWER_LAW_ALPHA,
     ERROR,
@@ -331,20 +337,23 @@ double integrate(double start, double arg1, double arg2) {// arg1, arg2; l0, sig
     default:
         std::cout << "Running integrate with an invalid luminosity function." << std::endl;
         std::cin.get();
+        return 0;
     }
 }
 
 double lintegrate(double start, double arg1, double arg2) {// lMin, lMax; l0, sigma
     switch (luminosityFunction) {
     case LUMINOSITY_FUNCTION::POWER_LAW:
[…]

### 2021-06-24 luminosity-models-position/graph-log-normal.py

@@ -118,8 +118,11 @@ if(DRAW_EXTRA_CONTOURS):
 plt.contour(xVals, yVals, lumSeen, [FRAC_ABOVE_THRESHOLD], colors=[LINE_COLOR], linestyles='dashed')
 
 plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^', markersize=6)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[0.41e34], [0.79e34]], yerr=[[0.16], [0.15]], linewidth=1, color=LINE_COLOR)
 plt.plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="fuchsia", marker='s', markersize=6)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[4.1304e+31], [4.1304e+31]], yerr=[[0.01011908], [0.01011908]], linewidth=1, color="fuchsia")
 plt.plot(gautamPoint[0], gautamPoint[1], markeredgecolor='black', markerfacecolor="red", marker='*', markersize=8)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[3.0842e+31], [3.0842e+31]], yerr=[[0.00316971], [0.00316971]], linewidth=1, color="red")
 
 # Observation
 shade(numSeen, NUM_PULSARS_ABOVE_THRESHOLD, xVals, yVals)

### 2021-06-24 luminosity-models-position/sensitivity/graph-log-normal.py

@@ -26,6 +26,7 @@ DRAW_PLOEG_POINT = True
 
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
+gautamPoint = [3.91983577e+32, 0.937184991]
 SHADE_SCALE=25
 
 def get_path(mult):
@@ -113,8 +114,12 @@ for mult in [1, 2, 5, 10]:
     axs[i].contour(xVals, yVals, numSeen, [NUM_PULSARS_ABOVE_THRESHOLD], colors=[LINE_COLOR])
     axs[i].contour(xVals, yVals, lumSeen, [FRAC_ABOVE_THRESHOLD], colors=[LINE_COLOR], linestyles='dashed')
 
-    axs[i].plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^')
-    axs[i].plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="C6", marker='s')
+    axs[i].plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^', markersize=6)
+    axs[i].errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[0.41e34], [0.79e34]], yerr=[[0.16], [0.15]], linewidth=1, color=LINE_COLOR)
+    axs[i].plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="fuchsia", marker='s', markersize=6)
+    axs[i].errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[4.1304e+31], [4.1304e+31]], yerr=[[0.01011908], [0.01011908]], linewidth=1, color="fuchsia")
+    axs[i].plot(gautamPoint[0], gautamPoint[1], markeredgecolor='black', markerfacecolor="red", marker='*', markersize=8)
+    axs[i].errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[3.0842e+31], [3.0842e+31]], yerr=[[0.00316971], [0.00316971]], linewidth=1, color="red")
 
     # Observation
     shade(axs[i], numSeen, NUM_PULSARS_ABOVE_THRESHOLD, xVals, yVals)
@@ -127,10 +132,11 @@ cbar.set_label("$N_\\textrm{GCE}$")
 
[…]

### 2021-06-24 luminosity-models-position/sensitivity/graph-power-law-alpha.py

@@ -119,7 +119,7 @@ for mult in [1, 2, 5, 10]:
     shade(axs[i], numSeen, NUM_PULSARS_ABOVE_THRESHOLD, alphaVals, lMaxVals)
     shade(axs[i], lumSeen, FRAC_ABOVE_THRESHOLD, alphaVals, lMaxVals, True)
 
-    axs[i].plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+    axs[i].plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
     i += 1
 
 cbar = axs[-1].cax.colorbar(c1)
@@ -127,7 +127,7 @@ cbar.set_label("$N_\\textrm{GCE}$")
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR),
                 Line2D([0], [0], color=LINE_COLOR, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None', markersize=6),]
 axs[-1].legend(custom_lines, ["$N_r=47$", "$R_r=0.2$", "Fermilab point"],
     loc='lower left')
 plt.tight_layout()

### 2021-06-24 luminosity-models-position/sensitivity/graph-power-law.py

@@ -117,7 +117,7 @@ for mult in [1, 2, 5, 10]:
     shade(axs[i], numSeen, NUM_PULSARS_ABOVE_THRESHOLD, lMaxVals, lMinVals)
     shade(axs[i], lumSeen, FRAC_ABOVE_THRESHOLD, lMaxVals, lMinVals, True)
 
-    axs[i].plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+    axs[i].plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
     i += 1
 
 cbar = axs[-1].cax.colorbar(c1)
@@ -125,7 +125,7 @@ cbar.set_label("$N_\\textrm{GCE}$")
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR),
                 Line2D([0], [0], color=LINE_COLOR, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='None', markersize=6),]
 plt.legend(custom_lines, ["$N_r=47$", "$R_r=0.2$", "Fermilab point"], loc='lower right')
 plt.xlim(lMaxVals[0], lMaxVals[-1])
 plt.ylim(lMinVals[0], lMinVals[-1])

### 2021-06-24 luminosity-models-smoothing/calc.cpp

@@ -6,6 +6,8 @@
 #include <sstream>
 #include <thread>
 #include <future>
+#include <math.h>
+#include <cmath>
 #include <boost/math/special_functions/gamma.hpp>
 
 #define INVALID -3789213.4812047 // A random number designed to encode an invalid input.
@@ -44,9 +46,12 @@ typedef std::vector<std::vector<double>> DoubleVector;
 #define NPTF_N_1_HIST -0.66
 #define NPTF_N_2_HIST 18.2
 
-#define START_FLUX_INTEGRAL 1.0e-12
-#define STOP_FLUX_INTEGRAL 1.0e-8
-#define NUM_FLUX_STEPS 1e3
+#define START_LUM_POWER 28
+#define STOP_LUM_POWER 36
+#define NUM_LUM_STEPS 1e5
+
+#define K_TH 0.45
+#define SIGMA_TH 0.28
 
 
 
@@ -61,6 +66,7 @@ const double SIGMA_RANGE[2] = { 0.001, 1 };
 const double fermilabPaperPoint[2] = { 1e35, 1e29 };
 const double logNormalPaperPoint[2] = { 0.88e34, 0.62 };
 const double logNormalPloegPoint[2] = { 1.6084e+32, 0.7003 };
+const double logNormalGautamPoint[2] = { 3.91983577e+32, 0.937184991 };
 
 // Values for the computation of the integral of the NFW profile.
 #define GAMMA 1.2
@@ -238,71 +244,73 @@ double sensitivity(double flux, double threshold) {
     if (threshold == INVALID) {
         return 1.0;
     }
-    if (flux > threshold) {
-        return 1.0;
-    }
-    return 0.0;
+    return 0.5 * (1 + erf((log10(flux) - (log10(threshold) + K_TH)) / (sqrt(2) * SIGMA_TH)));
 }
 
 double integrate(double threshold, double distance, double arg1, double arg2) {
     // lMin, lMax; l0, sigma; nBelow, nAbove
     double integral = 0;
-    double start_flux_integral;
+    double start_power;
+    const double flux_to_lum = (4 * PI * distance * distance * CM_PER_KPC_SQUARED);
     switch (luminosityFunction) {
     case LUMINOSITY_FUNCTION::POWER_LAW:
-        start_flux_integral = arg1 / (4 * PI * distance * distance * CM_PER_KPC_SQUARED);
+        start_power = log10(arg1);
         break;
[…]

### 2021-06-24 luminosity-models-step/log-normal/contour-overlay.py

@@ -186,17 +186,12 @@ if(DRAW_EXTRA_CONTOURS):
 plt.contour(xVals, yVals, fracAboveThreshold, [FRAC_ABOVE_THRESHOLD], colors=[LINE_COLOR], linestyles='dashed')
 
 
-# Plot thresholds
-#plt.plot(L_0_RANGE, [0.62-0.16, 0.62-0.16], c='blue', linewidth=1)
-#plt.plot(L_0_RANGE, [0.62+0.15, 0.62+0.15], c='blue', linewidth=1)
-#plt.plot([(0.88-0.41) * 1e34, (0.88-0.41) * 1e34], SIGMA_L_RANGE, c='blue', linewidth=1)
-#plt.plot([(0.88+0.79) * 1e34, (0.88+0.79) * 1e34], SIGMA_L_RANGE, c='blue', linewidth=1)
-
-
 plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^', markersize=6)
-plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[0.41e34], [0.79e34]], yerr=[[0.16], [0.15]], linewidth=1)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[0.41e34], [0.79e34]], yerr=[[0.16], [0.15]], linewidth=1, color=LINE_COLOR)
 plt.plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="fuchsia", marker='s', markersize=6)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[4.1304e+31], [4.1304e+31]], yerr=[[0.01011908], [0.01011908]], linewidth=1, color="fuchsia")
 plt.plot(gautamPoint[0], gautamPoint[1], markeredgecolor='black', markerfacecolor="red", marker='*', markersize=8)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[3.0842e+31], [3.0842e+31]], yerr=[[0.00316971], [0.00316971]], linewidth=1, color="red")
 #plt.scatter(minPoint[0], minPoint[1], c='cyan')
 
 

### 2021-06-24 multiple-flux-values/luminosity-models-position/graph-log-normal.py

@@ -33,6 +33,7 @@ DRAW_PLOEG_POINT = True
 
 paperPoint = [0.88e34, 0.62]
 ploegPoint = [10**32.206, 0.70585]
+gautamPoint = [3.91983577e+32, 0.937184991]
 SHOW_NUMBERS = False
 
 PATH_TO_FILE = "/home/jtdinsmo/Dropbox (MIT)/GCE UROP/luminosity-models-position/data-1x/log-normal/"
@@ -133,8 +134,12 @@ shade(lumSeen, FRAC_ABOVE_THRESHOLD, xVals, yVals, True)
 
 # Final points
 
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor="C1", marker='^')
-plt.plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="C6", marker='s')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='^', markersize=6)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[0.41e34], [0.79e34]], yerr=[[0.16], [0.15]], linewidth=1, color=LINE_COLOR)
+plt.plot(ploegPoint[0], ploegPoint[1], markeredgecolor='black', markerfacecolor="fuchsia", marker='s', markersize=6)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[4.1304e+31], [4.1304e+31]], yerr=[[0.01011908], [0.01011908]], linewidth=1, color="fuchsia")
+plt.plot(gautamPoint[0], gautamPoint[1], markeredgecolor='black', markerfacecolor="red", marker='*', markersize=8)
+plt.errorbar([paperPoint[0]], [paperPoint[1]], xerr=[[3.0842e+31], [3.0842e+31]], yerr=[[0.00316971], [0.00316971]], linewidth=1, color="red")
 
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR, linestyle=STYLES[0], lw=2),
@@ -142,9 +147,10 @@ custom_lines = [Line2D([0], [0], color=LINE_COLOR, linestyle=STYLES[0], lw=2),
                 Line2D([0], [0], color='k', linestyle=STYLES[2], lw=1),
                 Line2D([0], [0], color='k', linestyle=STYLES[3], lw=1),
[…]

### 2021-06-24 multiple-flux-values/luminosity-models-position/graph-power-law-alpha.py

@@ -124,14 +124,14 @@ shade(lumSeen, FRAC_ABOVE_THRESHOLD, alphaVals, lMaxVals, True)
 
 # Final points
 
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR, linestyle=STYLES[0], lw=2),
                 Line2D([0], [0], color='k', linestyle=STYLES[1], lw=1),
                 Line2D([0], [0], color='k', linestyle=STYLES[2], lw=1),
                 Line2D([0], [0], color='k', linestyle=STYLES[3], lw=1),
                 Line2D([0], [0], color=LINE_COLOR, linestyle='dashed', lw=2, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='none'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='none', markersize=6),]
 plt.legend(custom_lines, ['$N_r$ Di Mauro', "$N_r$ Fermilab gNFW", "$N_r$ Abazajian", "$N_r$ Ajello", '$R_r$', "Fermilab"], loc="lower right")
 plt.ylim(lMaxVals[0], lMaxVals[-1])
 plt.xlim(alphaVals[0], alphaVals[-1])

### 2021-06-24 multiple-flux-values/luminosity-models-position/graph-power-law.py

@@ -127,14 +127,14 @@ shade(lumSeen, FRAC_ABOVE_THRESHOLD, lMaxVals, lMinVals, True)
 
 # Final points
 
-plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o')
+plt.plot(paperPoint[0], paperPoint[1], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', markersize=6)
 
 custom_lines = [Line2D([0], [0], color=LINE_COLOR, linestyle=STYLES[0], lw=2),
                 Line2D([0], [0], color='k', linestyle=STYLES[1], lw=1),
                 Line2D([0], [0], color='k', linestyle=STYLES[2], lw=1),
                 Line2D([0], [0], color='k', linestyle=STYLES[3], lw=1),
                 Line2D([0], [0], color=LINE_COLOR, linestyle='dashed', lw=2, dashes=(4, 2)),
-                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='none'),]
+                Line2D([], [], markeredgecolor='black', markerfacecolor=LINE_COLOR, marker='o', linestyle='none', markersize=6),]
 plt.legend(custom_lines, ['$N_r$ Di Mauro', "$N_r$ Fermilab gNFW", "$N_r$ Abazajian", "$N_r$ Ajello", '$R_r$', "Fermilab"], loc="lower right")
 plt.xlim(lMaxVals[0], lMaxVals[-1])
 plt.ylim(lMinVals[0], lMinVals[-1])

### 2021-07-01 paper/draft.tex
More paper

@@
 \DeclareSIUnit\photon{photon}
+\newcommand{\SIasym}[4]{#1^{+#2}_{-#3}\ \SI{}{#4}}% Asymmetric error bars
+\newcommand{\numasym}[3]{#1^{+#2}_{-#3}}% Asymmetric error bars
 
@@
 
-\comment{What are possible explanations for the GCE? DM or MSPs. What luminosity functions might they have?}
+\comment{What are possible explanations for the GCE?
+DM or MSPs.
+What luminosity functions might they have?
+Mention that the GCE MSP population must be distinct from the disk population, and that accretion induced collapse yields different MSPs than other birth processes.}
+
+\comment{Mention Fermilab's paper, the 3 M pulsar population.}
 
@@
 
+\comment{The specific luminosity function parameterizations we use correspond to parameterizations that are reasonable for an MSP explanation to the GCE.
+But a lot of this analysis, such as the plots of allowed parameterizations for the power law and log normal luminosity functions, simply model point source emission, not necessarily MSPs.
+Is it useful to make this distinction?}
+
 In this paper, we extract a total flux for the GCE drawn from other analyses, and use it to calculate the total number of pulsars, number of resolved pulsars, and flux from those resolvable pulsars as predicted by various luminosity functions that have been proposed in literature.
-We indicate the luminosity functions necessary in order to meet the observational constraints imposed by a point source template fit to \textit{Fermi} data and the 4FGL catalog.
-\comment{What do we find?} We conclude with an analysis of what further luminosity function constraints could be achieved by improvements to the sensitivity of \textit{Fermi}.
+Making use of three different models for the sensitivity of \textit{Fermi}, we indicate the luminosity function parameterizations necessary in order to meet the observational constraints imposed by a point source template fit to \textit{Fermi} data and the 4FGL catalog.
+We operate under the assumption that every resolved point source is an MSP and the GCE consists entirely of MSPs.
+
+After comparing the observed flux distribution of point sources in the GCE to the MSP flux distribution predicted by these luminosity functions, we then discuss how many MSPs are likely to make up the GCE under these assumptions, given the observational constraints.
+We conclude with an analysis of what further luminosity function constraints could be achieved by improvements to the sensitivity of \textit{Fermi}.
 
@@
 \begin{equation}
-    \rho_\text{NFW}(r) \propto \parens{\frac{r}{r_s}}^{-\gamma}\parens{1 + \frac{r}{r_s}}^{-3-\gamma}
+    \rho_\text{NFW}(r) \propto \parens{\frac{r}{r_s}}^{-\gamma}\parens{1 + \frac{r}{r_s}}^{-3+\gamma}
     \label{eqn:nfw}
@@
 where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work. Other sources occasionally use $\gamma = 1$.
+\comment{The flux that comes from this NFW profile is unnormalizable.
+For most of the project, that doesn't matter because (l, b) = 0 is cut out.
+But for converting between ROIs, it means my former method was invalid.}
 
@@
 Of these 110 sources, they exclude all that are listed in the 4FGL catalog as not associated with pulsars.
-Of those that are known to be pulsars, they exclude all whose positions are known not to be within 2 kpc of the GC via the ATNF Pulsar Catalog \cite{Hobbs04}.
+Of those that are known to be pulsars, they exclude all whose positions are known not to be within $\SI{2}{\kilo\parsec}$ of the GC via the ATNF Pulsar Catalog \cite{Hobbs04}.
 This leaves 47 point sources in the 4FGL catalog whose origins are either known to be pulsars in the GC or are unknown.
@@
 \label{sec:total-lum}
-Since an estimate of the total flux of the GCE is necessary for our study, we extract the total flux from several previous analyses of spectra using the following three methods and compare them.
+An estimate of the total flux of the GCE is necessary for our study, so we extract the total flux from several previous analyses of spectra using the following three methods and compare them.
 The spectral analyses we study here are refs.
-\cite{Zhong:2019ycb, Calore:2014xka, DiMauro:2021raz, Abazajian:2014fta, Gordon, Ajello:2015kwa}.
-Each reference reports the total flux $F_\gamma(E)$ observed in an energy bin centered on $E$.
-Some studies use a ROI different from ours, so we convert to our ROI using the method outlined in appendix \ref{app:roi-rescale}.
-The spectra from these sources are reported in figure \ref{fig:all-spectra}
+\cite{Zhong:2019ycb, Calore:2014xka, DiMauro:2021raz, Abazajian:2014fta, Gordon13, Ajello:2015kwa}.
+Although they take their data from the same source, \textit{Fermi}, the studies' spectra differ due to choices in the method of fitting.
+For example, to model the spacial distribution of the excess, refs.
+\cite{Calore:2014xka, Gordon13, Ajello:2015kwa} fix $\gamma=1.2$, while ref.
+\cite{Zhong:2019ycb} performs the analysis for both $\gamma=1.0$ and $\gamma=1.2$, and refs.
+\cite{DiMauro:2021raz, Abazajian:2014fta} allow $\gamma$ to arise out of the fit.
+For the cases in which $\gamma$ is fitted, typical valyes range in 1.1--1.3.
+
+The studies use ROIs ranging from a $40^\circ \times 40^\circ$ region without the galactic disk cut used in this paper, to a $7^\circ \times 7^\circ$ region.
+All ROIs are centered on $(\ell, b)=(0, 0)$, however.
+All studies fix $r_s=\SI{20}{\kilo\parsec}$, except for refs.
+\cite{Abazajian:2014fta, Gordon13}, which use $r_s=\SI{23.1}{\kilo\parsec}$.
+In order to compare the studies, we rescale ROIs by the process described in appendix \ref{app:roi-rescale}, but we do not correct for differences in $\gamma$ or $r_s$.
+
+The manner in which uncertainties are reported also varies; some studies report only statistical uncertainties, and some report both statistical and systematic.
+Refs.
+\cite{Calore:2014xka, Gordon13} report both separately, and for our purposes we add these in quadrature.
+
+Figure \ref{fig:all-spectra} displays all the spectra mentioned above, with ROI rescaling included.
+When error bars can be recovered from the original papers, they are displayed.
+Many studies reported flux values in units of flux per steradian; we have multiplied those fluxes by the area of their respective ROIs to attain an absolute value for the GCE spectrum.
+
 \begin{figure}
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/all-spectra.pdf}
+    \includegraphics[width=0.7\textwidth]{figs/all-spectra.pdf}
     \caption{Spectra from seven analyses of the GCE, using different background models, shown with error bars when reported.}
@@
 
-\comment{Describe the sources: what's similar between them, what's different.}
-
-We use compare three methods of extracting the total GCE flux from these analyses.
+We use compare three methods of extracting the total GCE flux from these spectrum analyses.
 The first method is direct numerical integration of the spectra provided by each source.
-This method is most sensitive to the data measured by \textit{Fermi} and does not attempt to abstract over it with a smooth function.
-
-However, numerical integration cannot account for the spectrum lying outside of \textit{Fermi}'s spectrum of sensitivity, and it may be oversensitive to experimental error.
+This method is most sensitive to the data measured by \textit{Fermi} and does not attempt to abstract over it with a smooth function, but it is only available where points are reported, and is most sensitive to experimental error.
 Therefore, we also consider a broken law fit to the data, of the same form as the NPTF luminosity function: eq.
 \ref{eqn:nptf}.
-It has four parameters: a constant of proportionality, the turnover flux $F_\text{b}$, and the slopes above and below the turnover flux $n_2$ and $n_1$.
+It has four parameters: a constant of proportionality, the turnover energy $E_\text{b}$, and the slopes above and below the turnover flux $n_2$ and $n_1$.
 This function can then be analytically integrated over all flux values to get the total flux of the GCE.
@@
 We therefore fit only to the points with error bars reported.
-\comment{Mention the specific range fitted over}.
 
@@
 Ref.
-\cite{Calore:2014xka} provides their fit parameters for their GCE flux spectral data: $F_\text{b} = $.
-$n_1 = -1.42$, $n_2 = 2.63$.
-\comment{Check for sign errors in the original.
-Also get the flux they provide.}.
+\cite{Calore:2014xka} provides broken power law fit parameters for their GCE flux spectral data: $F_\text{b} = \SIasym{2.06}{0.23}{0.17}{\giga\electronvolt}$.
+$n_1 = \numasym{1.42}{0.22}{0.31}$, $n_2 = \numasym{2.63}{0.13}{0.095}$.
 The third fitting method is to fix these three broken power law parameters at these values and allow only the overall normalization to vary.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/di-mauro-example.pdf}
+    \includegraphics[width=0.7\textwidth]{figs/di-mauro-example.pdf}
     \caption{Spectrum produced by di Mauro in ref. \cite{DiMauro:2021raz}, with the two broken power law models fitted and shown.}
@@
 
-In practice, the three fitting methods yield very similar results for a single analysis.
+In practice, the numerical integration method appears to yield lower flux values, because it does not extend the tails of the spectrum.
+However, the two power law fits usually result in similar values for a single analysis.
 However, the values provided by different analyses vary greatly.
-For this study, we use the value obtained from di Mauro's analysis because it occupies a position near the middle of the distribution of GCE luminosities and is a recent study.
-We choose the value obtained by numerical integration, which is $F_\text{GCE} = \SI{1.295e-9}{\erg\per\centi\meter\squared\per\second}$.
-
-\comment{Discuss how rescaling of the ROI was done}
+For this study, we use the value obtained from di Mauro's analysis because it occupies a position near the middle of the distribution of GCE luminosities \comment{(Not anymore!)} and is a recent study.
+We choose the value obtained by numerical integration, which was $F_\text{GCE} = \SI{1.295e-9}{\erg\per\centi\meter\squared\per\second}$.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/total-flux-bars.pdf}
+    \includegraphics[width=0.7\textwidth]{figs/total-flux-bars.pdf}
     \caption{Total flux of the GCE as determined by the three integration methods discussed.
@@
 
-\comment{Just double check that I normalized the power law correctly in parse\_spectrum.py.}
-
 \subsection{Luminosity Functions}
 \label{sec:lum-funcs}
-Previous work has interpreted this MSP model. Ref. \cite{Zhong:2019ycb} has proposed an exponentially damped power law luminosity function
+Previous work has modeled the GCE as a MSP population, and estimated the probability distribution of pulsar luminosities, termed the ``luminosity function.'' One such luminosity function, proposed by ref.
+\cite{Zhong:2019ycb} among others, is an exponentially damped power law:
 \begin{equation}
@@
 \end{equation}
-The function has been normalized so that $P_\text{Power law}(L)$ represents the probability that a given MSP has luminosity $L$.
 This luminosity function restricts the range of luminosities to $[L_\text{min}, \infty)$, where $L_\text{min}$, $L_\text{max}$, and $\alpha$ are free parameters.
-\comment{The following should probably be moved to the introduction, where Fermilab's research is described.} This reference found that $(\SI{1e29}{\erg\per\second}, \SI{1e35}{\erg\per\second}, 1.94)$ is required reproduced observations.
+\comment{The following should probably be moved to the introduction once I write it, where Fermilab's research is described.} This reference found that $(\SI{1e29}{\erg\per\second}$, $ \SI{1e35}{\erg\per\second}$, $1.94)$ is required reproduced observations.
 They find that this model admits three million MSPs in the GCE, which differs from estimates based on the physical properties of observed MSPs that estimate the number of MSPs at the Galactic center at the order of 40,000 \cite{citation_needed}.
@@
 The ref.
-fits this model to data from globular cluster (GCL) data, yielding values $L_0 = \SI{8.8e33}{\erg\per\second}$ and $\sigma=0.62$.
+fits this model to data from globular cluster (GCL) MSP populations, yielding values $L_0 = \SI{8.8e33}{\erg\per\second}$ and $\sigma=0.62$.
 It predicts thousands of MSPs to occupy the GCE if the entire excess is to be explained by MSPs.
@@
 Ref.
-\cite{Ploeg:2020jeh} proposes several more intricate luminosity functions, derived from a model of the pulsars themselves.
-They find that the same model may be used for resolved, globular cluster MSPs in the Galactic disk and unresolved MSPs at the Galactic center.
-We use their luminosity function generated for the galactic disk.
-It closely resembles a log normal luminosity function as in equation \ref{eqn:log-normal}, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$.
+\cite{Ploeg:2020jeh} proposes a more intricate luminosity function, derived from a model of the pulsars themselves.
+They find that differences in spectrum between resolved, globular cluster MSPs in the Galactic disk and unresolved MSPs at the Galactic center are not significant.
+Their luminosity function generated for the galactic disk closely resembles a log normal luminosity function as in equation, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$ were obtained from a least-squares fit with $p$-value very close to 1\comment{Is there something wrong with the error bars here?}.
 
@@
 Mention the fact that the MSPs in the GCE would have to look different from that in the disk.} Their binary system model yields a numerical luminosity function for MSPs in the GC, reported as a function of flux.
-Converting to luminosity in the manner described in appendix \ref{app:lum-to-flux}, we find that a log normal distribution fits their function well, with $L_0 = \SI{3.92e+32}{\erg\per\second}$ and $\sigma = 0.937$.
-We call this model the AIC Log normal model.
+Converting to luminosity in the manner described in appendix \ref{app:lum-to-flux}, we perform a least-squares fit of a log normal distribution to their function, which produces $L_0 = \SI{3.92e+32}{\erg\per\second}$ and $\sigma = 0.937$, with a $p$-value of 0.29.
+We call this model the AIC log normal model.
 
@@
 \label{sec:sensitivity}
-The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some bright sources to be unresolved.
-We make use of three sensitivity models to model these factors.
+\comment{Should I name these Model A, Model B, Model C, or keep the descriptive but vague names?
+Which is easier to follow?} The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some brighter sources to be unresolved.
+We make use of three sensitivity models to account for these factors.
 
@@
 \end{equation}
-where $N_\text{GCE}$ is a normalization constant, fixed by requiring that $L_\text{GCE}$ reproduces the flux $F_\text{GCE}$ observed.
-The conversion between $L_\text{GCE}$ and $F_\text{GCE}$ is outlined in appendix \ref{app:lum-to-flux}.
+where $N_\text{GCE}$ is a normalization constant, fixed by requiring that the luminosity of the GCE $L_\text{GCE}$ reproduces the flux $F_\text{GCE}$ observed.
+The conversion between $L_\text{GCE}$ and $F_\text{GCE}$ required to force this equivalence is outlined in appendix \ref{app:lum-to-flux}.
 
 The second sensitivity model acknowledges the effect of background flux on resolvability and uses a position-dependent flux threshold $F_\text{th}(b, l)$ published by the \textit{Fermi} team \cite{Fermi-LAT:2019yla, Ballet:2020hze} (figure \ref{fig:sensitivity}).
-\comment{Here, I could talk about how to convert between flux and luminosity and then use the mean of this map to assess how accurate 1e34 ergs/s actually is.
+\comment{Here, I could assess how accurate 1e34 ergs/s actually is.
 One way would be simply to average over all the pixels in the sensitivity map and convert to luminosity.
@@
         N_\text{GCE} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\,, \\
-        F_\text{r} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\int_{4\pi s^2F_\text{th}(b,\ell)}^\infty dL \frac{L}{4\pi s^2}P(L)\,, \\
-        N_\text{r} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\int_{4\pi s^2F_\text{th}(b,\ell)}^\infty dL P(L) \,. \\
+        F_\text{r} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\int_{4\pi s^2F_\text{th}(\ell, b)}^\infty dL \frac{L}{4\pi s^2}P(L)\,, \\
+        N_\text{r} &= \int_\Omega d\Omega \int_0^\infty s^2 ds A \rho_{NFW}^2(r)\int_{4\pi s^2F_\text{th}(\ell, b)}^\infty dL P(L) \,. \\
         \label{eqn:observables-sens-2}
@@
 Here, $\Omega$ represents the $20^\circ \times 20^\circ$ region of interest with $|b| < 2^\circ$ cut out, and $A$ is the coefficient of equation \ref{eqn:nfw}, fixed by forcing $F_\text{GCE}$ to equal the observed value.
-In equation \ref{eqn:observables-sens-2} represents the distance to the galactic center from the point of integration, and is determined by the law of cosines:
-$r^2 = s^2 + r_c^2 - 2r_c s \cos \ell$.
+In equation \ref{eqn:observables-sens-2} represents the distance to the galactic center from the point of integration, and is determined by the law of cosines: $r^2 = s^2 + r_c^2 - 2r_c s \cos b \cos \ell$.
 
@@
 \comment{Maybe I shouldn't show this plot.
-It's barely original; just a display of a FITS file pulled from the 4FGL website.
+It's not original; just a display of a FITS file pulled from the 4FGL website.
 But I could overlay the previous figure of where the 47 point sources are.
@@
 The observables are calculated simply by multiplying the integrand of the luminosity integral in equation \ref{eqn:observables-sens-2} by $P_r(L/4\pi s^2)$ for $F_\text{r}$ and $N_\text{r}$.
-(Not for $F_\text{GCE}$, because we do not require that the $F_\text{GCE}$ flux be resolved.)
+(Not for $F_\text{GCE}$, because we do not require that the $F_\text{GCE}$ flux be resolved.) \comment{Should I mention how much the sensitivity models differ, or wait until the results have been presented?}
 
@@
 \subsection{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for different luminosity functions}
-Using each of the luminosity functions outlined in section \ref{sec:sensitivity}, we extract the total number of resolvable point sources $N_\text{r}$, the ratio of the flux received from those resolved point sources to the total flux of the GCE $R_\text{r}$, and the total number of point sources $N_\text{GCE}$ by forcing each function to reproduce the observed flux of the GCE.
+Using each of the luminosity functions outlined in section \ref{sec:sensitivity}, we extract the total number of resolvable MSPs $N_\text{r}$, the ratio of the flux received from those resolved MSPs to the total flux of the GCE $R_\text{r}$, and the total number of MSPs $N_\text{GCE}$ by forcing each function to reproduce the observed flux of the GCE.
 This is done for many parameterizations of the power law and log normal luminosity functions (eqs.
 \ref{eqn:power-law} and \ref{eqn:log-normal}), with $N_\text{GCE}$ displayed as a contour map in figures \ref{fig:step-function} and \ref{fig:position-dependent}, using the step function and the position-dependent sensitivity models respectively.
-Regions that satisfy the observational constraints $N_\text{r} < 47$ and $R_\text{r} < 0.2$ are marked.
+The observations $N_\text{r}=47$ and $R_\text{r}=0.2$ trace out a one-parameter family of luminosity functions that is also displayed.
+Since some resolved sources may not in fact be part of the GC, the regions with $N_\text{r} < 47$ and $R_\text{r} < 0.2$ also satisfy observational constraints and are marked.
 
@@
 Regions allowed by the $N_\text{r} \leq 47$ and $R_\text{r} \leq 0.2$ are marked with \texttt{|} and \texttt{-} respectively, while regions allowed by both constraints are marked with \texttt{+}.
-The top power law plot (blue) fixes $\alpha=1.94$ while the lower (green) fixes $L_\text{min}=\SI{1e29}{erg\per\second}$ }
+The top power law plot (blue) fixes $\alpha=1.94$ while the lower (green) fixes $L_\text{min}=\SI{1e29}{erg\per\second}$}
+    \label{fig:step-and-pos}
 \end{figure}
@@
         \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
-            Power law & 0 & 0 & $\num{0}$ \\
-            Log normal, GCL & 0 & 0 & 0 \\
-            Log normal, GCE & 0 & 0 & $\num{0}$ \\
-            Log normal, AIC & 0 & 0 & $\num{0}$ \\
+            Power law & 5.38 & 0.0449 & $\num{5.91e6}$ \\
+            Log normal, GCL & 79.9 & 0.683 & 473 \\
+            Log normal, GCE & 13.5 & 0.0649 & $\num{1.90e4}$ \\
+            Log normal, AIC & 59.4 & 0.518 & $\num{2.99e3}$ \\
             NFW NPTF & 0 & 0 & $\num{0}$ \\
@@
     \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE.
-For definitions of the paramterizations, see section \ref{sec:lum-funcs}.}
+For definitions of the parameterizations, see section \ref{sec:lum-funcs}.}
     \label{tab:specific-results}
@@
 
-The results of this analysis scale linearly with the flux of the GCE used.
-Figure \ref{fig:multiple-fluxes} shows figure \ref{tab:position-dependent-results} but with flux values from analyses other than di Mauro's represented.
+Figure \ref{fig:multiple-fluxes} shows luminosity function parameterizations that follow the observational constraints $N_\text{r} < 47$, $R_\text{r} < 0.2$, similar to figure \ref{tab:position-dependent-results}.
+This time, the constraints imposed by the GCE flux extracted from other analyses have been displayed as well.
 Note that $R_\text{r}$ does not vary because both fluxes in the ratio are scaled by the same amount.
@@
     \includegraphics[width=0.49\textwidth]{figs/log-normal-mult.pdf}
-    \caption{$N_\text{r}$ and $R_\text{r}$ for each luminosity function, with results for $N_\text{r}=47$ constraint shown for Fermilab gNFW's, Abazajian's, and Ajello's estimates of the GCE spectrum.}
+    \caption{$N_\text{r}$ and $R_\text{r}$ for each luminosity function, with results for $N_\text{r}=47$ constraint shown for Fermilab gNFW's, Abazajian's, and Ajello's estimates of the GCE spectrum.
+\comment{I need to update the legends of these plots to be consistent with the new names of the spectrum analyses.}}
     \label{fig:multiple-fluxes}
@@
 \subsection{Flux distribution}
-Until this point, we have compared predictions for the population of point source in the GC to observations only through the number and flux of resolved point sources.
-We may expand this analysis by comparing the flux distribution of point source population as well.
+Until this point, we have compared predictions for the population of MSPs in the GC to observations only through the number and flux of resolved MSPs.
+We may expand this analysis by comparing the predicted flux distribution of MSPs to the observed distribution for point sources.
 
-Figure \ref{fig:flux-distro-fix-count} shows the flux distribution of the four luminosity functions with the number of resolvable point sources fixed at 47, which is the number we observed.
-The distributions are superimposed on the observed flux distribution of the 47 sources as obtained from the 4FGL catalog \cite{Fermi-LAT:2019yla}, as well as the flux distribution with the 0.53$^\circ$ cut (see section \ref{sec:observables}).
-Figure \ref{fig:flux-distro-fix-flux} requires each model to reproduce the total flux of the GCE, allowing the aggregate number of resolved point sources to vary.
-These histograms are calculated with the position-dependent sensitivity model.
+We obtained the fluxes of the 47 observed point sources from the 4FGL point source catalog \cite{Fermi-LAT:2019yla}.
+This observed flux distribution is shown as a histogram in both panels of figure \ref{fig:flux-distro}, along with the distribution when the five extra points sources are added, corresponding to those which are added when the allowed distance between a peak in the GCE template fit and a point source in the 4FGL catalog is expanded from 0.3$^\circ$ to 0.55$^\circ$ (see section \ref{sec:observables} for details).
+
+Added to figure \ref{fig:flux-distro} is the MSP flux distribution predicted the five parameterizations of the luminosity functions we study.
+Figure \ref{fig:flux-distro-fix-count} fixes the number of observed MSPs at 47 and allows the flux of the GCE to vary, and figure \ref{fig:flux-distro-fix-flux} requires each model to reproduce the flux of the GCE.
+Both figures are calculated with the position-dependent sensitivity model.
+In figure \ref{fig:flux-distro-fix-flux}, the flux distribution resulting from the step function sensitivity model is also displayed.
 
@@
     \caption{Distribution of resolved sources predicted by each luminosity function compared to observed distribution, where observed point sources are allowed to be within 0.3$^\circ$ of spatial peaks in the GCE flux (gray histogram) and 0.53$^\circ$ (black histogram).}
+    \label{fig:flux-distro}
 \end{figure}
 
-The total GCE flux yielded by the luminosity functions shown in figure \ref{fig:flux-distro-fix-count} which are forced to reproduce the number of observed sources is shown in table \ref{tab:rescaled-gce-flux}.
+For the case when the number of observed MSPs is fixed at 47, the resultant flux of the GCE is presented in table \ref{tab:rescaled-gce-flux} and compared to the observed GCE flux.
 
@@
         \hline
-        Luminosity function & $F_\text{GCE}^\text{hyp}\ (\SI{}{\erg\per\second})$ & $F^\text{hyp}_\text{GCE} / F^\text{obs}_\text{GCE}$\\ \hline \hline
+        Luminosity function & $F_\text{GCE}^{(47)}\ (\SI{}{\erg\per\second})$ & $F^{(47)}_\text{GCE} / F^\text{obs}_\text{GCE}$\\ \hline \hline
         Power law & $\num{3.49e-09}$ & $\num{2.69}$\\
@@
     \end{tabular}
-    \caption{Total GCE flux ($F_\text{GCE}^\text{hyp}$) required by each luminosity function to yield 47 observed forces, and the ratio of that flux to the observed GCE flux $F_\text{GCE}^\text{obs}$ for comparison.}
+    \caption{Total GCE flux ($F_\text{GCE}^{(47)}$) required by each luminosity function to yield 47 observed forces, and the ratio of that flux to the observed GCE flux $F_\text{GCE}^\text{obs}$ for comparison.}
     \label{tab:rescaled-gce-flux}
@@
 
+\section{Discussion}
+
+\subsection{Sensitivity models}
+Figure \ref{fig:step-and-pos} and table \ref{tab:specific-results} both demonstrate that the step function and position-dependent sensitivity models yield starkly different observables.
+The regions of allowed parameterization differ greatly, especially in the power law case, between the two models, and predictions for $N_\text{r}$ can differ by as much as a factor of ten for specific parameterizations.
+Predictions by $R_\text{r}$ differ by as much as a factor of three.
+This is in part because bright pulsars distant from Earth have lower flux, and therefore can appear unresolved in the position-dependent sensitivity model, but the step function sensitivity model always marks these pulsars as unresolved.
+The difference is also caused by the fact that lower sensitivity is correlated with MSP population density, a fact not appreciated by the step function model.
+The GCE log normal luminosity function differs most between sensitivity models, most likely due to \comment{it's thinness and low mean, but I need to think more about exactly why this is.}
+
+Finally, the step function threshold $L_\text{th}=\SI{e34}{\erg\per\second}$ used in ref.
+\cite{Zhong:2019ycb} may be unphysically low; using the conversion between flux and luminosity outlined in appendix \ref{app:lum-to-flux}, the lowest value in \textit{Fermi}'s sensitivity map corresponds to a luminosity of $\SI{1.7e34}{\erg\per\second}$.
+Ref.
+\cite{Zhong:2019ycb} also uses a threshold of $L_\text{th}=\SI{3e34}{\erg\per\second}$ sometimes, to account for the strong dependence on the value of $L_\text{th}$.
+\comment{They don't actually say why they use 3e34.
+Is it fair to put words in their mouth?
+Also, maybe I should use 3e34.
+It wouldn't actually be that hard.}
+
+In contrast, the smoothed sensitivity model does not appear to differ from the position-dependent sensitivity model by nearly as much.
+\comment{Except the power law, which may be a bug?} This is likely because the smoothed sensitivity model differs from the position dependent model only for MSPs near $F_\text{th}(\ell, b)$, which is a relatively small number of MSPs for most luminosity functions.
+Motivated by this similarity and the greater computational complexity of the smoothed sensitivity model, we will mostly use the position-dependent sensitivity model throughout the rest of this study.
+
+\subsection{Allowed luminosity function parameterizations}
+Figure \ref{fig:step-function} shows that the power law parameterization used by ref.
+\cite{Zhong:2019ycb}, which matches both $N_\text{r}=47$ and $R_\text{r}=0.2$ exactly when their GCE luminosity and the step function model is used, does not match the number constraint when di Mauro's GCE flux is used.
+When the position dependent sensitivity model is used, the constraints change so drastically that the point now produces 17.6 resolvable MSPs instead of 47 (table \ref{tab:specific-results}).
+The implicit uncertainty on this point, induced by uncertainties in the sensitivity model, the GCE luminosity, and observations, are therefore very large.
+
+Figure \ref{fig:step-and-pos} also demonstrates that the GCL and AIC parameterizations of the log normal do not match observations, regardless of which sensitivity model is used.
+However, \ref{fig:multiple-fluxes} demonstrates that this exclusion is sensitive to the flux of the GCE used; by using a small enough flux, almost all parameterizations of the log normal luminosity function fit observations.
+
+The fact that the GCL and AIC luminosity functions obey the number constraint when a different GCE flux is used does not necessarily mean that they are good candidates for an MSP population in the GC.
+The flux ratio constraint $R_\text{r}$ does not change when a different GCE flux is used, so the luminosity functions still do not match the $R_\text{r}$ constraint.
+Furthermore, the $R_\text{r}$ constraint has been shown above to be less dependent on the sensitivity model used, indicating that it is a more reliable constraint.
+The good agreement between the observed flux distribution of point sources and the predicted flux distribution of MSPs (discussed more below) also strengthens this point.
+
+The only luminosity function that reliably matches observations is the GCE luminosity function, which was expected given that that it is the only luminosity function considered in this paper which was obtained by a fit to GCE data.
+This strengthens the point made by others \cite{citation-needed} that an MSP population that explains the GCE would have to have different properties than GCL MSPs.
+Specifically, it appears they would have to have lower luminosity or form a more peaked distribution, so that they stay in the lower left triangle of the bottom row plots of figure \ref{fig:step-and-pos}.
+
+\subsection{Number of MSPs in the GCE}
+Reference \cite{Zhong:2019ycb} determined that about three million MSPs are required to reproduce the GCE.
+Using a different spectrum for the GCE, that number inflates to 8 million (table \ref{tab:specific-results}).
+However, if a different sensitivity model is used, the region of parameterizations allowed by observational constraints can produce only thousands of MSPs (figure \ref{fig:position-dependent}).
+
+The log normal case also produces a few thousand MSPs, while the GCE parameterization, which agrees with observational constraints, produces about 20,000 MSPs.The NPTF luminosity function also produces a few thousand MSPs.
+Indeed, all the specific parameterizations we studied in table \ref{tab:specific-results} result in fewer than 30,000 MSPs except for the power law luminosity function.
+\comment{In consultation with Tracy, make some final judgment about how many pulsars are likely to be in the GCE.}
+
+\subsection{Flux distribution}
+Our predictions of MSP flux distribution match the shape of the observed flux distribution of point sources well (fig.
+\ref{fig:flux-distro-fix-count}), especially for the log normal and power law luminosity functions.
+\comment{Should I make some Poissonian error bars and find a p value?}.
+However, since all luminosity functions tested match the observed flux distribution well, the flux distribution appears to be controlled by the shape of the GCE and the sensitivity model rather than the luminosity function parameterization, indicating that the observed flux distribution is unlikely to shed much light on the luminosity function of GCE MSPs.
+\comment{Is that too unsubstantiated to say?} Figure \ref{fig:flux-distro-fix-flux} shows that the flux distribution for the step function sensitivity model does not match the observed flux distribution in shape, since it predicts a sharp cutoff of point source detection at \textit{Fermi}'s luminosity threshold, which is not observed.
+
 \section{Future Sensitivity}
-We simulate an increase in sensitivity of GCE measurements by reusing the same $F_\text{th}(b, \ell)$ sensitivity map (figure \ref{fig:sensitivity}) as the one provided by the Fermi-LAT team, but with an overall multiplicative decrease.
-In particular, we study cases where the sensitivity is decreased by a factor of two, five, and ten and reproduce the analysis found earlier in the paper.
-Plots of $N_\text{r}$ for different parameterizations of the power law and log normal luminosity functions are given in figure \ref{fig:sensitivity}, and values for $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for specific parameterizations are given in table \ref{tab:sensitivity-values}.
-Of course, the number of sources in the GCE does not depend on \textit{Fermi} sensitivity and will not change.
+In this section, we determine the capability of an improved $\gamma$-ray telescope to constrain the luminosity function parameters of an MSP population in the GC.
+We simulate an increase in sensitivity of GCE measurements by reusing the same $F_\text{th}(\ell, b)$ sensitivity map (figure \ref{fig:sensitivity}) as the one provided by the Fermi-LAT team, but with an overall multiplicative decrease.
+In particular, we study cases where the sensitivity is decreased by a factor of two, five, and ten and reproduce the analysis described earlier in the paper.
+
+Plots of $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for different parameterizations of the power law and log normal luminosity functions are shown in figure \ref{fig:sensitivity-results}, and values for $N_\text{r}$ and $R_\text{r}$ for specific parameterizations are given in table \ref{tab:sensitivity-values}.
+The number of sources in the GCE does not depend on the telescope's sensitivity, so $N_\text{GCE}$ is not included in table \ref{tab:sensitivity-values} and is only included in fig.
+\ref{fig:sensitivity-results} for reference.
 \comment{That means that the backgrounds of the column plots do not change from plot to plot.
 I could put them all on the same thing.}
+
+\comment{It's difficult to draw conclusions from these plots because if you increase sensitivity, the number of observed sources will obviously change.
+Maybe I should be doing a different kind of analysis?
+Or figure out a better way to phrase things} The power law is shown to react most to changes in sensitivity level, and for both luminosity functions, the number constraint is more dependent on sensitivity than the flux ratio constraint.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{figs/power-law-sensitivity.pdf}
+        \caption{Power law luminosity function varying $L_\text{min}$, $L_\text{max}$}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{figs/power-law-alpha-sensitivity.pdf}
+        \caption{Power law luminosity function varying $\alpha$, $L_\text{max}$}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{figs/log-normal-sensitivity.pdf}
+        \caption{Log normal luminosity function }
+    \end{subfigure}
+    \caption{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for power law and log normal luminosity function parameterizations, simulating improved $\gamma$-ray telescope sensitivity, with regions allowed by the current observations of $N_\text{r}\leq 47$ and $R_\text{r} \leq 0.2$ marked with \texttt{+} symbols.
+The top row indicates \textit{Fermi}'s current sensitivity, while the lower rows are an overall decrease in threshold $F_\text{th}(\ell, b)$ by a factor of two, five, and ten respectively.
+$N_\text{GCE}$ does not depend on sensitivity but is displayed for reference.}
+    \label{fig:sensitivity-results}
+\end{figure}
 
@@
     \end{tabular}
-    \caption{Number of resolved point sources and ratio of resolved flux to total flux,predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE.
+    \caption{Number of resolved MSPs and ratio of resolved flux to total flux based on six luminosity function parameterizations and the requirement that the MSPs reproduce the entire flux of the GCE.
 The assumed sensitivity of the telescope, $F_\text{th}(\ell, b)$, has been varied by a factor of 1 (i.e., sensitivity is at its current value), 2, 5, and 10, with the factor of increase given as superscripts in the header.
@@
 \section{Conclusion}
+\comment{I thought I'd leave writing the introduction and conclusion until the rest of the paper is done, in case things change.}
+
+\comment{Effect of our research on the predictions by Fermilab}
+
+\comment{Number of pulsars in the GCE}
+
+\comment{Comparison between the GCE- and GCL-derived luminosity functions and which matches observations more accurately}
+
+\comment{The observed flux distribution matches the predicted distribution of MSPs, but is not sensitive to the luminosity function}
+
+\comment{Future sensitivity}
 
@@
 Here, $s$ represents the distance from Earth to the point of integration, and $r$ represents the distance from the GC to the point of integration.
-They are related by the law of cosines: $r^2 = s^2 + r_c^2 - 2s r_c \cos \ell$, where $\ell$ is the Galactic longitude.
+They are related by the law of cosines: $r^2 = s^2 + r_c^2 - 2s r_c \cos b\cos \ell$, where $\ell$ is the Galactic longitude.
 The numerical value reported was computed for $r_c = \SI{8.5}{\kilo\parsec}$.
@@
 \acknowledgments
-
-This is the most common positions for acknowledgments. A macro is
-available to maintain the same layout and spelling of the heading.
+\comment{We should probably acknowledge the Fermilab team for giving us their data. Anyone else?}
 

### 2021-07-01 compare-spectra/convert-rois/convert-rois.py

@@ -1,19 +1,7 @@
-'''
-Method:
-    By integrating the NFW distribution over space, I'm going to calculate
-    the number of particles present in a given ROI and divide by the
-    number of particles present in my ROI. I will use this factor to
-    convert fluxes, under the assumption that the flux goes like the
-    number of sources.
-'''
-
-'''Convert a GCE luminosity to a flux, assuming an NFW-squared distributed
-pattern of pulsars with delta function luminosity. See Jan summary for
-calculation.'''
-
 from math import pi, cos, sqrt
+import numpy as np
 
-DELTA_ANGLE = 0.001
+DELTA_ANGLE = 0.01
 DELTA_S = 0.01
 R_C=8.5
 R_S=20
@@ -22,38 +10,90 @@ INTEGRAL_LIMIT=100
 def NFWSquared(r, gamma):
     return ((r/R_S)**(-gamma) * (1 + r/R_S)**(-3+gamma))**2
 
-def calculateIntegral(maxB, minB, maxL, gamma):# Give angles in units of degrees
+def get_ring(ring, minB, gamma):
+    if ring < minB:
+        return 0
     integral = 0
-    b = -maxB * pi / 180.0
-    while b < maxB * pi / 180.0:
+
+    b = 0
+    l = ring
+    while b < ring:
         volumeElement = cos(b) * DELTA_ANGLE * DELTA_ANGLE * DELTA_S
-        l = -maxL * pi / 180.0
-        if abs(b) < minB * pi / 180.0:
+        if b < minB:
             b += DELTA_ANGLE
             continue
-        while l < maxL * pi / 180.0:
-            s=0
-            while s < INTEGRAL_LIMIT:
-                r = sqrt(R_C*R_C + s * s - 2 * R_C * s * cos(b) * cos(l))
-                integral += NFWSquared(r, gamma) * volumeElement
+        s=0
+        while s < INTEGRAL_LIMIT:
+            r = sqrt(R_C*R_C + s * s - 2 * R_C * s * cos(b) * cos(l))
+            if r == 0:
                 s += DELTA_S
-            l += DELTA_ANGLE
+                continue
+            integral += NFWSquared(r, gamma) * volumeElement
+            s += DELTA_S
[…]

### 2021-07-01 compare-spectra/display.py

@@ -6,7 +6,7 @@ import matplotlib.transforms as mtrans
 
 plt.style.use("jcap")
 
-SPECTRUM_RANGE = [0.5, 10]# GeV
+SPECTRUM_RANGE = [0.1, 100]# GeV
 NUM_PLOTS = 7
 SHAPES=['o', 's', '^', '*', 'd', '+', 'x']
 
@@ -43,7 +43,7 @@ for i in range(0, NUM_PLOTS):
     f.display_data(allax, color="C"+str(i), shape=SHAPES[i])
     f.display_data(ax)
     f.display_calore(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
-    #f.display_power_law(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
+    f.display_power_law(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     numerical_flux = f.get_numerical_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     calore_flux = f.get_calore_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     fit_flux = f.get_power_law_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
@@ -59,7 +59,7 @@ for i in range(0, NUM_PLOTS):
 
     print(f.get_name(), numerical_flux)
 
-    ax.annotate("Num: {}\nCalore: {}\nFit: {}".format(sciNot(numerical_flux), sciNot(calore_flux), sciNot(fit_flux)), (0.2, 0.1), xycoords='axes fraction')
+    ax.annotate("Num: {}\nCalore: {}\nFit: {}".format(sciNot(numerical_flux), sciNot(calore_flux), sciNot(fit_flux)), (0.2, 0.1), xycoords='axes fraction', size=8)
 
 
 axes[(NUM_PLOTS-1)%3][(NUM_PLOTS-1)//3].set_xlabel(f.get_x_label())
@@ -79,12 +79,12 @@ x = np.arange(len(fit_fluxes))
 width = 0.25
 hist_fig, hist_ax = plt.subplots()
 hist_ax.bar(x, num_fluxes, width, label="Numerical")
-hist_ax.bar(x + width, calore_fluxes, width, label="Calore", hatch='////', linewidth=0.5)
[…]

### 2021-07-01 compare-spectra/parse_spectrum.py

@@ -1,6 +1,6 @@
 import numpy as np
 from scipy.optimize import curve_fit
-import lmfit
+import lmfit, os
 
 import warnings
 warnings.filterwarnings("ignore")
@@ -13,14 +13,14 @@ FERMILAB_NFW = 4
 ABAZAJIAN = 5
 GORDON = 6
 
-BANDS_OR_BARS = 'bands'# 'bars'
-
-ROI_SIZE = 0.428821318754
+MY_ROI_SIZE = 0.428821318754
+BIG_ROI_SIZE = 0.477550208734
 LM_FIT_SCALE = 1e9
 ERGS_PER_GEV = 0.00160218
-LARGE_ROI_FACTOR = 1.8248083080193496#2.101243483243096 # Compare 40x40 degree region to 40x40 with mask
-GORDON_ROI_FACTOR = 0.7432172914343479#1.0138798168363303 # Compare 7x7 with no mask to 40x40 with mask, with gamma=1.2
-ABAZAJIAN_ROI_FACTOR = 0.2912979297594549#0.4208269993877883 # Compare 7x7 with no mask to 40x40 with mask, with gamma=1
+LARGE_ROI_FACTOR = 1.8248083080193496 # Compare 40x40 degree region to 40x40 with mask
+GORDON_ROI_FACTOR = 0.7432172914343479 # Compare 7x7 with no mask to 40x40 with mask, with gamma=1.2
+ABAZAJIAN_ROI_FACTOR = 0.2912979297594549 # Compare 7x7 with no mask to 40x40 with mask, with gamma=1.1
+AJELLO_ROI_FACTOR = 1.2 # Compare 15x15 with no mask to 40x40 with mask, with gamma=1.2
 
 CALORE_L_BREAK, CALORE_ALPHA_BELOW, CALORE_ALPHA_ABOVE = 2.06 * ERGS_PER_GEV, 1.42, 2.63
 
@@ -34,23 +34,113 @@ def power_law(x, scale, alpha_below, alpha_above, l_break):
     alpha[10**x < l_break] = alpha_below
     return (10**x)**2 * scale * (10**x / l_break)**(-alpha) * LM_FIT_SCALE
 
[…]

### 2021-07-01 compare-spectra/spectrum-data/ajello/display-power-law.py

@@ -1,0 +1,59 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+NORM = 2.7e-4
+L_MAX = 1.5#1.346
+ALPHA = 0.2
+
+def power_law(x, norm, lmax, alpha):
+    return norm * x**2 * x**(-alpha) * np.exp(-x / lmax)
+
+def load_csv(filepath):
+    # Return x and y values of the spectrum. Both are in logarithmic units. Y is E^2 dN/dE.
+    xres = []
+    yres = []
+    f = open(filepath, 'r')
+    for line in f.readlines():
+        if line == '': continue
+        x, y = line.split(",")
+        xres.append(10**float(x))
+        yres.append(10**float(y))
+    f.close()
+
+    return np.asarray(xres), np.asarray(yres)
+
+def get_point(x, datax, datay):
+    i = 0
+    if x < datax[0] or x > datax[-1]:
+        #print("{} is out of range of this function (range {} to {}).".format(logx, datax[0], datax[-1]))
+        return
+    while datax[i+1] < x:
+        i += 1
+    factor = (x - datax[i]) / (datax[i+1] - datax[i])
+    return factor * (datay[i+1] - datay[i]) + datay[i]
+
+downx, downy = load_csv("down-bands.csv")
+upx, upy = load_csv("up-bands.csv")
+ptsx = 10**np.linspace(np.log10(np.min(downx)), np.log10(np.max(downx)), 10)
+ptsy = power_law(ptsx, NORM, L_MAX, ALPHA)
+fake_ptsy = [(get_point(x, downx, downy) + get_point(x, upx, upy)) / 2 for x in ptsx]
+
+plt.plot(downx, downy, color='k')
+plt.plot(upx, upy, color='k')
+plt.plot(ptsx, ptsy, label="Fit")
+plt.plot(ptsx, fake_ptsy, label="Mid points")
+
+f = open("points.csv", 'w')
+for i in range(len(ptsx)):
+    f.write("{}, {}\n".format(np.log10(ptsx[i]), np.log10(ptsy[i])))
+f.close()
+
+plt.xscale("log")
+plt.yscale("log")
+plt.xlim(1, 100)
+plt.ylim(7e-6, 6e-4)
+plt.xlabel("E (GeV)")
+plt.ylabel("E^2 dN/dE (MeV / cm^2 / s)")
+plt.legend()
+
+plt.show()

### 2021-07-01 fit-functions/fit.py

@@ -2,6 +2,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from lmfit import Model, Parameter, report_fit
 import scipy.optimize as optimization
+from scipy import stats
 
 plt.style.use("jcap")
 
@@ -66,11 +67,12 @@ class Data:
         if self.log_normal_results is not None:
             ax.plot(self.xs, log_normal(self.xs, self.log_normal_results[0],
             self.log_normal_results[2],self.log_normal_results[4]),
-            label="Log normal fit\n$L_0$={}$\pm${}, $\\sigma$={}$\pm${}".format(
+            label="Log normal fit\n$L_0$={}$\pm${}, $\\sigma$={}$\pm${}\n$p$={}".format(
                 sci_not(self.log_normal_results[2]),
                 sci_not(self.log_normal_results[3]),
                 sci_not(self.log_normal_results[4]),
-                sci_not(self.log_normal_results[5])))
+                sci_not(self.log_normal_results[5]),
+                sci_not(self.log_normal_p)))
 
     def label_axes(self, ax):
         ax.set_xlabel("$\\log(L / $ erg s$^{-1})$")
@@ -101,6 +103,7 @@ class Data:
             result.params["c"].value, result.params["c"].stderr,
             result.params["alpha"].value, result.params["alpha"].stderr,
             result.params["lmax"].value, result.params["lmax"].stderr)
+        self.power_law_p = 1 - stats.chi2.cdf(result.chisqr, len(self.ys)-3)
 
         return self.power_law_results
 
@@ -120,6 +123,7 @@ class Data:
             result.params["c"].value, result.params["c"].stderr,
             result.params["l0"].value, result.params["l0"].stderr,
             result.params["sigma"].value, result.params["sigma"].stderr)
+        self.log_normal_p = 1 - stats.chi2.cdf(result.chisqr, len(self.ys)-3)
 
         return self.log_normal_results
 

### 2021-07-01 luminosity-models-position/calc.cpp

@@ -18,7 +18,7 @@ typedef std::vector<std::vector<double>> DoubleVector;
 
 #define INVALID -3789213.4812047 // A random number designed to encode an invalid input.
 
-#define SENSITIVITY_DIVISOR 5.0
+#define SENSITIVITY_DIVISOR 10.0
 
 #define pi 3.14159265358979323
 #define ONE_PLUS_EPSILON 1.0000000001

### 2021-07-01 luminosity-models-smoothing/calc.cpp

@@ -244,6 +244,8 @@ double sensitivity(double flux, double threshold) {
     if (threshold == INVALID) {
         return 1.0;
     }
+    //if (flux < threshold) {return 0.0;}
+    //return 1.0;
     return 0.5 * (1 + erf((log10(flux) - (log10(threshold) + K_TH)) / (sqrt(2) * SIGMA_TH)));
 }
 
@@ -915,7 +917,7 @@ int nptf() {
         + "\n\tFraction of seen luminosity: " + sciNot(fracFluxScaled) + "\n";
 
     std::cout << nptfText << std::endl; std::ofstream recordFile;
-    recordFile.open(ROOT "luminosity-models-smoothing/data-" + std::to_string((int)SENSITIVITY_DIVISOR) + "x/nptf/record.txt");
+    recordFile.open(ROOT "luminosity-models-smoothing/data-" + std::to_string((int)SENSITIVITY_DIVISOR) + "x/nptf/record-step.txt");
     recordFile << nptfText << std::endl;
 
     std::cin.get();

### 2021-07-01 plot-functions/plotter.py

@@ -48,6 +48,10 @@ def nptf(x, n1, n2, LBreak):
         return (1 - n1) * (1 - n2) / (LBreak * (n1 - n2)) * (x/LBreak)**(-n1)
     else:
         return (1 - n1) * (1 - n2) / (LBreak * (n1 - n2)) * (x/LBreak)**(-n2)
+def lum_to_flux(lum):
+    return lum * LUM_TO_FLUX
+def flux_to_lum(flux):
+    return flux / LUM_TO_FLUX
 
 fig, ax1=plt.subplots()
 
@@ -56,17 +60,6 @@ ax1.set_ylabel("$\\frac{dN}{dL}$")
 ax1.set_xscale('log')
 
 x = 10**np.linspace(PLOT_LOG_MIN, PLOT_LOG_MAX, NUM_PLOT_POINTS)
-
-ax2 = ax1.twiny()
-
-ax2.set_xlabel("Flux $F$ [erg / cm$^2$ / s]")
-
-def convert_ax2(ax1):
-    x1, x2 = ax1.get_xlim()
-    ax2.set_xlim(x1 * LUM_TO_FLUX, x2 * LUM_TO_FLUX)
-    ax2.figure.canvas.draw()
-
-ax1.callbacks.connect("xlim_changed", convert_ax2)
 
 ys = [
     powerLaw(x, L_MIN, L_MAX, ALPHA),
@@ -85,6 +78,9 @@ for i in range(len(ys)):
         c=colors[i])
 #ax1.axvline(x=L_THRESH, color='k')
 
+ax2 = ax1.secondary_xaxis('top', functions=(lum_to_flux, flux_to_lum))
+ax2.set_xlabel("Flux $F$ [erg / cm$^2$ / s]")
+
 ax1.legend(loc='upper left')
 plt.tight_layout()
 
@@ -99,18 +95,15 @@ ax1.set_xlabel("Luminosity $L$ [erg / s]")
 ax1.set_ylabel("$L\\frac{dN}{dL}$")
 ax1.set_xscale('log')
 
-ax2 = ax1.twiny()
-
-ax2.set_xlabel("Flux $F$ [erg / cm$^2$ / s]")
-
-ax1.callbacks.connect("xlim_changed", convert_ax2)
-
 ys = [x * y for y in ys]
 
 for i in range(len(ys)):
     ax1.plot(x, np.abs(ys[i]) / np.max(np.abs(ys[i])), label = names[i], linestyle=styles[i],
[…]

### 2021-07-01 sensitivity/thresholds.py

@@ -22,6 +22,7 @@ KAPPA = 0.5 # dist to center / r_s
 GAMMA = 1.2 # Shape facter of the NFW profile
 A = 1 # Something like the number of objects per cubic kiloparsec; in fact, it's the coefficient of the NFW number density
 CM_PER_KPC = 3.086e21
+FLUX_TO_LUM = 1.1093417307914119e-46
 
 DISPLAY_SIZE = 20.0
 THRESHOLD = 1e34
@@ -29,7 +30,7 @@ NUM_X_LABELS = 8
 NUM_Y_LABELS = 8
 
 def fluxToThresholdLuminosity(flux):
-    return flux * (4 * pi * (DIST_TO_CENTER * CM_PER_KPC) ** 2)
+    return flux / FLUX_TO_LUM #flux * (4 * pi * (DIST_TO_CENTER * CM_PER_KPC) ** 2)
 
 image_file = "detthresh_P8R3_source_10years_PL22.fits"
 
@@ -71,7 +72,7 @@ trimmed_lum_data = np.asarray(trimmed_lum_data)
 #mpl.rcParams["font.size"]=12
 
 # Display flux data:
-c = plt.imshow(trimmed_flux_data, 
+c = plt.imshow(trimmed_flux_data,
                    norm=colors.LogNorm(vmin=np.nanmin(trimmed_flux_data),
                    vmax=np.nanpercentile(trimmed_flux_data, 99)))
 cbar = plt.colorbar(c)
@@ -101,7 +102,7 @@ plt.savefig("flux-thresholds.pdf")
 # Display luminosity data
 
 plt.figure()
-c = plt.imshow(trimmed_lum_data, 
+c = plt.imshow(trimmed_lum_data,
                    norm=colors.LogNorm(vmin=np.nanmin(trimmed_lum_data),
                    vmax=np.nanpercentile(trimmed_lum_data, 99)))
 cbar = plt.colorbar(c)
@@ -117,9 +118,10 @@ yLabels = np.linspace(start=-DISPLAY_SIZE, stop=DISPLAY_SIZE, num=NUM_Y_LABELS+1
 np.append(yPositions, trimmed_flux_data.shape[0])
 plt.yticks(yPositions, [int(i) for i in yLabels])
 
+print(np.nanmin(trimmed_lum_data))
+
 plt.xlabel("$\\ell$ (deg)")
 plt.ylabel("$b$ (deg)")
 plt.tight_layout()
 plt.savefig("luminosity-thresholds.png")
 plt.show()
-

### 2021-07-07 paper/draft.tex
Answering questions

@@
 where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work. Other sources occasionally use $\gamma = 1$.
-\comment{The flux that comes from this NFW profile is unnormalizable.
-For most of the project, that doesn't matter because (l, b) = 0 is cut out.
-But for converting between ROIs, it means my former method was invalid.}
 
@@
 $N_\text{r}$ and $R_\text{r}$ have been studied by \comment{Some technical name for the Fermilab team.} \cite{Zhong:2019ycb}.
-The authors performed a template fit to data from Fermi-LAT to isolate spacial peaks in flux, finding 110 \comment{(I got 110; their paper says 107)} peaks within 0.3$^\circ$ of a source in the 4FGL catalog within the region of interest \cite{Abdollahi_2020}.
-Of these 110 sources, they exclude all that are listed in the 4FGL catalog as not associated with pulsars.
+The authors performed a template fit to data from Fermi-LAT to isolate spacial peaks in flux, finding 107 unique peaks within 0.3$^\circ$ of a source in the 4FGL catalog within the region of interest \cite{Abdollahi_2020}.
+Of these sources, they exclude all that are listed in the 4FGL catalog as not associated with pulsars.
 Of those that are known to be pulsars, they exclude all whose positions are known not to be within $\SI{2}{\kilo\parsec}$ of the GC via the ATNF Pulsar Catalog \cite{Hobbs04}.
@@
 The sources are scaled by luminosity in radius.
-The gray band represents the $|b| \leq 2^\circ$ cut made around the galactic disk.}
+The gray band represents the $|b| \leq 2^\circ$ cut made around the galactic disk.
+\comment{I think this disagrees with the Fermilab paper}}
     \label{fig:47-sources}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{figs/total-flux-bars.pdf}
-    \caption{Total flux of the GCE as determined by the three integration methods discussed.
-\comment{Here I would discuss why Ajello doesn't have a value for the power law case if this is still true once I have the original source}.}
+    \includegraphics[width=0.8\textwidth]{figs/total-flux-bars.pdf}
+    \caption{Total flux of the GCE as determined by the three integration methods discussed.}
     \label{fig:total-flux-bars}
@@
 They find that differences in spectrum between resolved, globular cluster MSPs in the Galactic disk and unresolved MSPs at the Galactic center are not significant.
-Their luminosity function generated for the galactic disk closely resembles a log normal luminosity function as in equation, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$ were obtained from a least-squares fit with $p$-value very close to 1\comment{Is there something wrong with the error bars here?}.
+Their luminosity function generated for the galactic disk closely resembles a log normal luminosity function as in equation, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$ were obtained from a least-squares fit with $p$-value very close to 1.
 
@@
     \label{eqn:nptf}
-\end{equation}
-where the free parameters  $n_1$, $n_2$, and $L_b$ were found via a Non-Poissonian Template Fitting model (NPTF) to be $(18.2, -0.66, \SI{8.66e+33}{\erg\per\second})$ for an NFW-squared-distributed population of MSPs named NFW PS.
-The paper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.34e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced.
-\comment{I will want to remove the unnormalizable one.
-When should I do it?} The luminosity-valued parameters were originally given as fluxes in $\SI{}{\photon \per \centi\meter\squared \per \second}$.
+\end{equation},
+where the free parameters  $n_1$, $n_2$, and $L_b$ were found via a Non-Poissonian Template Fitting model (NPTF) to be $(18.2, -0.66, \SI{9.13e+33}{\erg\per\second})$ for an NFW-squared-distributed population of MSPs named NFW PS.
+The paper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.53e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced.
+The luminosity-valued parameters were originally given as fluxes in $\SI{}{\photon \per \centi\meter\squared \per \second}$.
 The photon energy was calculated via appendix \ref{app:photon-energy} and the flux converted to luminosity via appendix \ref{app:lum-to-flux}.
@@
 \label{sec:sensitivity}
-\comment{Should I name these Model A, Model B, Model C, or keep the descriptive but vague names?
-Which is easier to follow?} The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some brighter sources to be unresolved.
+The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some brighter sources to be unresolved.
 We make use of three sensitivity models to account for these factors.
@@
 \ref{eqn:power-law} and \ref{eqn:log-normal}), with $N_\text{GCE}$ displayed as a contour map in figures \ref{fig:step-function} and \ref{fig:position-dependent}, using the step function and the position-dependent sensitivity models respectively.
+The first row of these figures varies $L_\text{min}$ and $L_\text{max}$, with $\alpha=1.94$, which is the value computed by ref.
+\cite{Zhong:2019ycb}; the second row varies $L_\text{max}$ and $\alpha$, with $L_\text{min}=\SI{1e29}{\erg\per\second}$.
 The observations $N_\text{r}=47$ and $R_\text{r}=0.2$ trace out a one-parameter family of luminosity functions that is also displayed.
@@
 Regions allowed by the $N_\text{r} \leq 47$ and $R_\text{r} \leq 0.2$ are marked with \texttt{|} and \texttt{-} respectively, while regions allowed by both constraints are marked with \texttt{+}.
-The top power law plot (blue) fixes $\alpha=1.94$ while the lower (green) fixes $L_\text{min}=\SI{1e29}{erg\per\second}$}
+The top power law plot (blue) fixes $\alpha=1.94$ while the lower (green) fixes $L_\text{min}=\SI{1e29}{erg\per\second}$.}
     \label{fig:step-and-pos}
@@
         \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
-            Power law & 5.38 & 0.0449 & $\num{5.91e6}$ \\
+            Power law & 5.35 & 0.0448 & $\num{5.91e6}$ \\
             Log normal, GCL & 79.9 & 0.683 & 473 \\
@@
 The difference is also caused by the fact that lower sensitivity is correlated with MSP population density, a fact not appreciated by the step function model.
-The GCE log normal luminosity function differs most between sensitivity models, most likely due to \comment{it's thinness and low mean, but I need to think more about exactly why this is.}
+The GCE log normal luminosity function differs most between sensitivity models, most likely due to \comment{its thinness and low mean, but I need to think more about exactly why this is.}
 
@@
 In contrast, the smoothed sensitivity model does not appear to differ from the position-dependent sensitivity model by nearly as much.
-\comment{Except the power law, which may be a bug?} This is likely because the smoothed sensitivity model differs from the position dependent model only for MSPs near $F_\text{th}(\ell, b)$, which is a relatively small number of MSPs for most luminosity functions.
+\comment{Except the power law, which may be a bug?
+I just checked; I don't think it's a bug.} This is likely because the smoothed sensitivity model differs from the position dependent model only for MSPs near $F_\text{th}(\ell, b)$, which is a relatively small number of MSPs for most luminosity functions.
 Motivated by this similarity and the greater computational complexity of the smoothed sensitivity model, we will mostly use the position-dependent sensitivity model throughout the rest of this study.
@@
 \comment{That means that the backgrounds of the column plots do not change from plot to plot.
-I could put them all on the same thing.}
+I could put them all on the same axes.}
 
@@
 
-The flux ratio as computed by equation \ref{eqn:roi-conversion} between our region and the same $40^\circ \times 40^\circ$ without the Galactic disk cutout is 2.10.
-Similarly, the ratio is 1.64, 1.27, 0.915, and 1.013 \comment{Wrong!} for a $30^\circ \times 30^\circ $, $20^\circ \times 20^\circ$, $10^\circ \times 10^\circ$, and $7^\circ \times 7^\circ$ respectively.
+The flux ratio as computed by equation \ref{eqn:roi-conversion} between our region and the same $40^\circ \times 40^\circ$ without the Galactic disk cutout is 1.90.
+Similarly, the ratio is 1.70, 1.44,1.26, 1.04, and 0.869 for a $30^\circ \times 30^\circ $, $20^\circ \times 20^\circ$, $15^\circ \times 15^\circ$, $10^\circ \times 10^\circ$, and $7^\circ \times 7^\circ$ respectively.
+We mention $15^\circ \times 15^\circ$ because it is the ROI used by ref.
+\cite{Ajello:2015kwa}, and $7^\circ \times 7^\circ$ because it is used by refs.
+\cite{Abazajian:2014fta} and \cite{Gordon13}.
 
@@
 To do this, we fit a broken power law to the GCE spectrum found by di Mauro and described in section \ref{sec:total-lum}, defining the flux observed from photons in an energy bin of energy $E_\gamma$ and width $dE_\gamma$ as $dF = E_\gamma N(E_\gamma)dE_\gamma$.
-The function $E_\gamma N(E_\gamma)$ is plotted in figure \ref{fig:di-mauro-example}.
+The function $E_\gamma^2 N(E_\gamma)$ is plotted in figure \ref{fig:di-mauro-example}.
 The average photon energy is then calculated by
 \begin{equation}
-    \langle E_\gamma \rangle =  \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} E_\gamma N(E_\gamma) dE_\gamma} \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} N(E_\gamma) dE_\gamma}^{-1} = \SI{0}{\giga\electronvolt}.
+    \langle E_\gamma \rangle =  \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} E_\gamma N(E_\gamma) dE_\gamma} \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} N(E_\gamma) dE_\gamma}^{-1} = \SI{1.58e-3}{\erg}.
     \label{eqn:photon-energy}
 \end{equation}
-\comment{I'd like to finish this. Give examples of photon energy.}
+However, for the conversion of the photon flux to energy flux for the NPTF luminosity function specifically, we use a spectrum extending from $\SI{1.893}{\giga\electronvolt}$ to $\SI{11.943}{\giga\electronvolt}$, which was used in the reference that derived the flux \cite{Lee:2015fea}.
+This yielded an energy of $\SI{5.76e-3}{\erg}$.
+
+If the broken power law fit to the GCE spectrum proposed by Calore et al.
+is used, then the energy per photon over the $\SI{0.1}{\giga\electronvolt}$ to $\SI{100}{\giga\electronvolt}$ spectrum is $\SI{1.41e-3}{\erg}$.
+If the fit to the Zhong et al.
+2020 spectrum with $\gamma=1.2$ is used, then the photon energy is $\SI{1.35e-3}{\erg}$.
+We see then that the photon energy, while highly sensitive to the range of spectrum used, is not very sensitive to the GCE spectrum used.
 
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{gce.bib}

### 2021-07-07 compare-spectra/convert-rois/convert-rois.py

@@ -1,11 +1,11 @@
 from math import pi, cos, sqrt
 import numpy as np
 
-DELTA_ANGLE = 0.01
+DELTA_ANGLE = 0.0001
 DELTA_S = 0.01
 R_C=8.5
 R_S=20
-INTEGRAL_LIMIT=100
+INTEGRAL_LIMIT=30
 
 def NFWSquared(r, gamma):
     return ((r/R_S)**(-gamma) * (1 + r/R_S)**(-3+gamma))**2
@@ -51,7 +51,7 @@ def get_ring(ring, minB, gamma):
         return integral
 
     # The edges of the quadrant are doubled. Remove them
-    volumeElement1 = cos(ring) * DELTA_ANGLE * DELTA_ANGLE * DELTA_S\
+    volumeElement = cos(ring) * DELTA_ANGLE * DELTA_ANGLE * DELTA_S\
         + DELTA_ANGLE * DELTA_ANGLE * DELTA_S
     s=0
     while s < INTEGRAL_LIMIT:
@@ -75,25 +75,23 @@ def get_roi(angle, rings, nums):
             integral += nums[i]
     return integral
 
-print("ROI 1/4")
-rings_mask, num_mask = get_rings(20, 2, 1.2)
-print(num_mask)
-print("ROI 2/4")
-rings_no_mask, num_no_mask = get_rings(20, 0, 1.2)
-print(num_no_mask)
-#print("ROI 3/4")
-#rings_mask_gamma, num_mask_gamma = get_rings(20, 2, 1.1)
-#print("ROI 4/4")
-#rings_no_mask_gamma, num_no_mask_gamma = get_rings(5, 0, 1.1)
+#print("ROI 1/4")
+#rings_mask, num_mask = get_rings(20, 2, 1.2)
+#print("ROI 2/4")
+#rings_no_mask, num_no_mask = get_rings(20, 0, 1.2)
+print("ROI 3/4")
+rings_mask_gamma, num_mask_gamma = get_rings(20, 2, 1.1)
+print("ROI 4/4")
+rings_no_mask_gamma, num_no_mask_gamma = get_rings(5, 0, 1.1)
 
-my_ROI = get_roi(20, rings_mask, num_mask)
-print("40x40 ROI factor:", get_roi(20, rings_no_mask, num_no_mask) / my_ROI)
-print("30x30 ROI factor:", get_roi(15, rings_no_mask, num_no_mask) / my_ROI)
[…]

### 2021-07-07 compare-spectra/display.py

@@ -6,13 +6,19 @@ import matplotlib.transforms as mtrans
 
 plt.style.use("jcap")
 
+
 SPECTRUM_RANGE = [0.1, 100]# GeV
-NUM_PLOTS = 7
-SHAPES=['o', 's', '^', '*', 'd', '+', 'x']
+SPECTRUM_RANGE_LOW = [0.1, 10]# GeV
+NUM_PLOTS = 9
+SHAPES = ['o', 's', '*', 'd', 'x', 'o', 's', '<', '>']
+FILL_STYLE = [None, None, 'none', None, None, 'none', 'none', 'none', 'none']
 
 fig, axes = plt.subplots(nrows=3, ncols=3, figsize=(10, 6), sharex='col', sharey='row')
 
-allfig, allax = plt.subplots()
+allfig, allax = plt.subplots(figsize=(6.8, 4.5))
+
+
+allax.set_ylim(1e-8, 6e-7)
 
 def sciNot(i):
     if i == None:
@@ -34,13 +40,22 @@ def sciNot(i):
 num_fluxes = []
 calore_fluxes = []
 fit_fluxes = []
+num_fluxes_low = []
+calore_fluxes_low = []
+fit_fluxes_low = []
 names = []
+
+calore_flux_uncs = []
+fit_flux_uncs = []
+calore_flux_low_uncs = []
+fit_flux_low_uncs = []
 
 for i in range(0, NUM_PLOTS):
     ax = axes[i%3][i//3]
     f = ps.Spectrum(i)
     names.append(f.get_name())
-    f.display_data(allax, color="C"+str(i), shape=SHAPES[i])
+    f.display_data(allax, color="C"+str(i), shape=SHAPES[i],
+        fill_color=FILL_STYLE[i])
     f.display_data(ax)
     f.display_calore(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     f.display_power_law(ax, SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
@@ -48,8 +63,10 @@ for i in range(0, NUM_PLOTS):
     calore_flux = f.get_calore_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     fit_flux = f.get_power_law_flux(SPECTRUM_RANGE[0], SPECTRUM_RANGE[1])
     num_fluxes.append(numerical_flux)
-    calore_fluxes.append(calore_flux)
-    fit_fluxes.append(fit_flux)
+    calore_fluxes.append(calore_flux[0])
[…]

### 2021-07-07 compare-spectra/make-example.py

@@ -24,6 +24,7 @@ f.label_axes(ax)
 
 ax.plot([], [], color='C1', linestyle='--', label="Calore fit")
 ax.plot([], [], color='C2', linestyle='-.', label="Power law fit")
+ax.set_ylim(2e-8, 5e-7)
 
 plt.title("")
 fig.tight_layout()

### 2021-07-07 compare-spectra/parse_spectrum.py

@@ -5,22 +5,28 @@ import lmfit, os
 import warnings
 warnings.filterwarnings("ignore")
 
-FERMILAB_GNFW = 0
+DI_MAURO = 0
 CALORE = 1
-DI_MAURO = 2
-AJELLO = 3
-FERMILAB_NFW = 4
-ABAZAJIAN = 5
-GORDON = 6
+FERMILAB_GNFW = 2
+FERMILAB_NFW = 3
+ABAZAJIAN = 4
+GORDON = 5
+AJELLO_2017 = 8
+AJELLO_BLACK = 6
+AJELLO_GREEN = 7
+ARTIFICIAL = 9
 
 MY_ROI_SIZE = 0.428821318754
 BIG_ROI_SIZE = 0.477550208734
 LM_FIT_SCALE = 1e9
 ERGS_PER_GEV = 0.00160218
-LARGE_ROI_FACTOR = 1.8248083080193496 # Compare 40x40 degree region to 40x40 with mask
-GORDON_ROI_FACTOR = 0.7432172914343479 # Compare 7x7 with no mask to 40x40 with mask, with gamma=1.2
-ABAZAJIAN_ROI_FACTOR = 0.2912979297594549 # Compare 7x7 with no mask to 40x40 with mask, with gamma=1.1
-AJELLO_ROI_FACTOR = 1.2 # Compare 15x15 with no mask to 40x40 with mask, with gamma=1.2
+LARGE_ROI_FACTOR = 1.8961920419764398 # Compare 40x40 degree region to 40x40 with mask
+GORDON_ROI_FACTOR = 0.8685899550623982 # Compare 7x7 with no mask to 40x40 with mask, with gamma=1.2
+ABAZAJIAN_ROI_FACTOR = 0.5496547377000791# Compare 7x7 with no mask to 40x40 with mask, with gamma=1.1 # UNKNOWN
+AJELLO_ROI_FACTOR = 1.2624815974139625 # Compare 15x15 with no mask to 40x40 with mask, with gamma=1.2
+
+Y_LIM = 1e-8 * ERGS_PER_GEV# lOWERMOST Y LIMIT
+ERROR_BAR_SIZE = 0.2
 
 CALORE_L_BREAK, CALORE_ALPHA_BELOW, CALORE_ALPHA_ABOVE = 2.06 * ERGS_PER_GEV, 1.42, 2.63
 
@@ -38,16 +44,20 @@ _files = {
     FERMILAB_GNFW:"fermilab-gnfw",
[…]

### 2021-07-07 compare-spectra/photon-energy.py

@@ -1,27 +1,42 @@
 DI_MAURO = 0
 FERMILAB = 1
 CALORE = 2
+TEST = 3
 ERG_PER_GEV = 0.00160218
+FLUX_TO_LUM = 1.1093417307914119e-46
+NPTF_FLUX = [1.76e-10, 6.80e-9]
 
-TYPE = FERMILAB
+TYPE = DI_MAURO
 
-if TYPE == FERMILAB or TYPE == CALORE:
+if TYPE == FERMILAB:
+    L_BREAK = 0.00516323313751923
+    ALPHA_ABOVE = 2.7922607115665783
+    ALPHA_BELOW = 1.561888668638258
+if TYPE == CALORE:
     L_BREAK = 2.06 * ERG_PER_GEV
     ALPHA_ABOVE = 2.63
     ALPHA_BELOW = 1.42
+if TYPE == DI_MAURO:
+    L_BREAK = 0.0020217250786090323
+    ALPHA_ABOVE = 2.565547079994774
+    ALPHA_BELOW = 1.0337152835197816
+if TYPE == TEST:
+    L_BREAK = 0.1
+    ALPHA_ABOVE = 1.2
+    ALPHA_BELOW = 1.4
 
 def integrate(start, stop):
     topAlpha = ALPHA_ABOVE if stop > L_BREAK else ALPHA_BELOW
     bottomAlpha = ALPHA_BELOW if start < L_BREAK else ALPHA_ABOVE
     return L_BREAK / (1 - bottomAlpha) * (1 - (start / L_BREAK)**(1 - bottomAlpha)) + \
-        L_BREAK / (1 - topAlpha) * ((stop / L_BREAK)**(1 - topAlpha) - 1)
+        L_BREAK / (1 - topAlpha) * ((stop / L_BREAK)**(1 - topAlpha) - 1) # Math confirmed 7 Jul 2021
 
 
 def lintegrate(start, stop):
     topAlpha = ALPHA_ABOVE if stop > L_BREAK else ALPHA_BELOW
     bottomAlpha = ALPHA_BELOW if start < L_BREAK else ALPHA_ABOVE
     return L_BREAK**2 / (2 - bottomAlpha) * (1 - (start / L_BREAK)**(2 - bottomAlpha)) + \
-        L_BREAK**2 / (2 - topAlpha) * ((stop / L_BREAK)**(2 - topAlpha) - 1)
[…]

### 2021-07-07 compare-spectra/spectrum-data/ajello-2017/make.py

@@ -1,0 +1,38 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+EPSILON = 1e-15
+
+def get_arrays(filename):
+    f = open(filename, 'r')
+    xs = []
+    ys = []
+    for line in f.readlines():
+        if line == '': continue
+        x, y = line.split(", ")
+        xs.append(float(x))
+        ys.append(float(y))
+    return np.asarray(xs), np.asarray(ys)
+
+px, py = get_arrays("raw-points.csv")
+_, bary = get_arrays("raw-bars.csv")
+
+plt.errorbar(px, py, yerr=bary)
+plt.xscale("log")
+plt.yscale("log")
+plt.ylim(3e-9, 2e-6)
+
+points = open("points.csv", 'w')
+up_bars = open("up-bars.csv", 'w')
+down_bars = open("down-bars.csv", 'w')
+for i in range(len(px)):
+    if (py[i] < 0): continue
+    points.write(str(np.log10(px[i]))+", "+str(np.log10(py[i]))+'\n')
+    up_bars.write(str(np.log10(px[i]))+", "+str(np.log10(py[i]+bary[i]))+'\n')
+    down_bars.write(str(np.log10(px[i]))+", "+str(np.log10(max(py[i]-bary[i], EPSILON)))+'\n')
+
+points.close()
+up_bars.close()
+down_bars.close()
+
+plt.show()

### 2021-07-08 paper/draft.tex
NPTF smoothed results

@@
             Log normal, AIC & 59.4 & 0.518 & $\num{2.99e3}$ \\
-            NFW NPTF & 0 & 0 & $\num{0}$ \\
-            DISK NPTF & 0 & 0 & $\num{0}$ \\
+            NFW NPTF & 2.31 & 0.0119 & $\num{1.97e3}$ \\
+            DISK NPTF & 34.3 & 0.521 & $\num{-47.6}$ \\
             \hline

### 2021-07-08 compare-spectra/parse_spectrum.py

@@ -341,7 +341,7 @@ class Spectrum:
              (a**(a1) * L**2 - a**2 * L**a1 - (a1 - 2)* a**2 * L**a1 * np.log(a) + (a1 -2)*a**2 * L**a1 * np.log(L))
         above_unc = c * self.fit_alpha_above_unc * b**(-a2) / (a2 - 2)**2 * \
             (-b**(a2) * L**2 + b**2 * L**a2 + (a2 - 2)* b**2 * L**a2 * np.log(b) - (a2 -2)*b**2 * L**a2 * np.log(L))
-
+        
         return (val, np.sqrt(norm_unc**2 + break_unc**2 + above_unc**2 + below_unc**2))
 
     def get_numerical_flux(self, l_min, l_max, override=False):
